---
title: "features_ttest_100iteration.rmd"
author: "Dali_Nemecio"
date: "`r Sys.Date()`"
output: html_document
---

This code executes a t-test for every data matrix in the class balanced bootstrapped training data.

## Start ---------------------------------------------------------------------

### Set up

```{r, setup}
# Set Up - Section 1 -------------------------------------------------------
#           rmd set up----------------------------------------
knitr::opts_chunk$set(echo = TRUE)


#           Load Library **SPECIFY**------------------------------------------------------------
packages_needed<-c("tidyverse",
                   "tibble", 
                   "dplyr",
                   "rstudioapi") 

for (pkg in packages_needed){
if ( !require(pkg, character.only = TRUE)){
  library(pkg, character.only = TRUE)
} 
}

#           Collect Script Info and Change To Script Directory ---------------


#Script Directory
script_path_current <- getSourceEditorContext()$path
script_path_folder<-sub("/[^/]*$", "", script_path_current)
script_name<-sub(".*/", "", script_path_current)
script_name_base<-sub("\\..*$", "", script_name)

#Change directory in all code chunks to current script location
knitr::opts_knit$set(root.dir = script_path_folder)
 

#           Collect Run Info------------------------------------------- 
run_timestamp <- format(Sys.time(), "%Y_%m_%d_%H%M")

run_sessionInfo<-sessionInfo()

#           Shortcut Custom Functions --------------------------------------------------------


v <- function(data) {
  tab_name <- deparse(substitute(data))
  View(data, title = tab_name)
}

d<-function(data){
  dim(data)
}

l<-function(data){
  length(data)
}

u<-function(data){
  unique(data)
}

h<-function(data){
  head(data)
}

t<-function(data){
  tail(data)
}


```


### Load Data and Objects Required

!!! ONLY LOAD TRAIN !!! 

```{r, load data and objects}
# Load Data - Collect .rda files ----------------------------------------

#       Find Previous Code Folder -----------------------------

# Find the last slash
last_slash <- max(gregexpr("/", script_path_folder)[[1]])

# Extract the substring
substring_after_last_slash <- substr(script_path_folder, last_slash + 1, nchar(script_path_folder))

# Extract the first number
first_number <- regmatches(substring_after_last_slash, regexpr("[0-9]+", substring_after_last_slash))

# Convert the first number to an integer and subtract 1
new_number <- as.integer(first_number) - 1

# Construct the new path
new_path <- paste0(
  substr(script_path_folder, 1, last_slash),
  new_number,
  "_*"
)

# Function to find directory matching the pattern
find_directory <- function(path_with_wildcard) {
  
  # Extract directory path without wildcard
  directory_path <- dirname(path_with_wildcard)
  
  # List files matching the pattern
  matching_files <- list.files(directory_path, pattern = basename(path_with_wildcard))
  
  # Check if any matching directory exists
  matching_directories <- matching_files[dir.exists(file.path(directory_path, matching_files))]
  
  if (length(matching_directories) > 0) {
    
    return(file.path(directory_path, matching_directories[1]))
    
  } else {
    return(NULL)
  }
}

# Find the actual directory matching the wildcard
rda_directory <- find_directory(new_path)

#       Load .rda files  ---------------------------------

# Get list of all .rda files recursively
rda_files <- list.files(path = rda_directory, 
                        pattern = "\\Train_List_Stacked.rda$",
                        recursive = TRUE,
                        full.names = TRUE)

# Load each .rda file
for (file in rda_files) {
  load(file)
}

#       Check Object Sizes by hand--------------------------

# d(MA_100_90percent)

#       Collect starting Envr.  ---------------------------------

objects_starting<-ls()

```




### Prep For Entry AND T Test execution -  gene exp x mic-gene corr. !!!!

```{r, prep for entry and t test }

boot_10_ttest_results<-list() 


#           Create TV_known Dataframe  -----------------------------------------------

for (j in 1:length(MA_100_gene_exp_multi_classbal_list_train)){
 
          print(paste0("Enter Outerloop/bootstrap dataframe :", j) ) 
  
           TV_known_ttest<-as.data.frame(MA_100_gene_exp_multi_classbal_list_train[[j]])
           
            #Filter for TV state = -1 or +1
            TV_known_ttest<- TV_known_ttest%>%
                              filter(TV_state== -1 |TV_state== 1 )%>%
                              arrange()
            

            
#           Define Entering Data and Variables --------------------------------------------------------


            gene_index_start <- which(colnames(TV_known_ttest) == "A2M")
            
            gene_index_end <- which(colnames(TV_known_ttest) == "ZZZ3")
  
            train_set<-TV_known_ttest
    
            
             
            # Define TV +1 rows 
            pos1<-train_set%>%
              filter(train_set$TV_state == 1)
            
            # Define TV -1 rows
            neg1<-train_set%>%
              filter(train_set$TV_state == -1)
            

#           Empty Dataframe For T Test Results ---------------------------------------
            results_build <- data.frame(
                                  gene = character(0),
                                  train_set=numeric(0),
                                  p_value = numeric(0),
                                  neg1_group_mean = numeric(0),
                                  pos1_group_mean = numeric(0),
                                  conf_int_low = numeric(0),
                                  conf_int_high = numeric(0),
                                  t_value = numeric(0),
                                  degrees_of_freedom = numeric(0) )
      


#           Enter T test for loop -----------------------------------------------------------------

#### Begin  Loop

  for (y in gene_index_start:gene_index_end){
    
        if (y == gene_index_start) {
          print(paste0("enter inner loop/iterate through columns "))} 
        
    pos1_col<-pos1[,y]
    neg1_col<-neg1[,y]
    
        if ( isTRUE( names(pos1)[y] == names(neg1)[y] )) {
      
      # Run T test 
      results<-t.test(pos1_col, neg1_col, alternative = c("two.sided"), var.equal = FALSE) #welch's t test
      
      # Add results to t_test results table
      results_loop<-data.frame(gene = names(pos1)[y],
                               p_value = results$p.value,
                               neg1_group_mean = mean(neg1_col),
                               pos1_group_mean = mean(pos1_col),
                               conf_int_low = results$conf.int[1],
                               conf_int_high = results$conf.int[2],
                               t_value = results$statistic,
                               degrees_of_freedom = results$parameter)
      
      results_build <- rbind(results_build,results_loop)
      
      
    } else {
      print(paste("Column Index:", y,  "---Gene names do not match, will not run t test"))
      break
    }
    
    
        if (names(train_set)[y] == gene_index_end){
      print(paste(" All colums cor. calc :)"))
    }
    
  } #end of t test looping through columns
  
#           Produced Objects --------------------------------------------------------


ttest_results<-results_build

 

    if(length(boot_10_ttest_results)==0){
    
    boot_10_ttest_results[[1]]<-ttest_results
    
  } else {
    
    boot_10_ttest_results[[(length(boot_10_ttest_results)+1)]]<-ttest_results
    
  }
  
 print(paste0("outer loop for t test completed: ", j ))
}

```

### Benjamini-Hochberg (FDR)

```{r, fdr}

resu_list<-boot_10_ttest_results



for(i in 1:length(boot_10_ttest_results)){
  
result_df<-boot_10_ttest_results[[i]]
  
  if (i == 1){
  
    print("enter i =1 ")
      # Create blank list 
      building<-list()
      
      # get adjusted values vector
      adj_p_value<-p.adjust(result_df$p_value, method = "BH")  # KEY
      
      # Add to t test results 
      joined<-cbind(adj_p_value,boot_10_ttest_results[[1]])
      
    
      
  }else{
  
    print(paste0("enter i =", i )) 
      # get adjusted values vector
      adj_p_value<-p.adjust(result_df$p_value, method = "BH")  # KEY
      
      # Add to t test results 
      joined<-cbind(adj_p_value,resu_list[[i]])
      
  }
  
  # Add to building list 
  if(length(building)==0){
    
    print(paste0("joined results to list:", i ))
    
    building[[1]]<-joined%>%
                    select("gene", "adj_p_value","p_value",
                           "neg1_group_mean", "pos1_group_mean", 
                           "conf_int_low", "conf_int_high", 
                           "t_value", "degrees_of_freedom")
    
  } else {
    
    print(paste0("joined results to list:", i ))
    
    building[[(length(building)+1)]]<-joined%>%
                    select("gene", "adj_p_value","p_value",
                           "neg1_group_mean", "pos1_group_mean", 
                           "conf_int_low", "conf_int_high", 
                           "t_value", "degrees_of_freedom")
    
  }
  
}

boot_10_ttest_results<-building


```

### Results
```{r, results}

#           Select Top 500 Genes  ---------------------------------------------------


list_arr_fxn<- function(df){
           df<-as.data.frame(df)
            newdf<-df %>%
                  arrange(adj_p_value)%>%
                  head(500)
            return(newdf)
}

boot_10_top_500_summary<-lapply(boot_10_ttest_results, list_arr_fxn)


#add index value 
for (i in 1:length(boot_10_top_500_summary)){
  
  boot_10_top_500_summary[[i]]<-as.data.frame(boot_10_top_500_summary[[i]])
  
  boot_10_top_500_summary[[i]]$boot_index<-i
}


#condense all boot top 500 in one dataframe 
boot_10_top_500_summary_stacked<-do.call(rbind, boot_10_top_500_summary)

# count genes
boot_10_top_500_count<-boot_10_top_500_summary_stacked%>%
                          count(gene)

#list of shared features
boot_10_shared_feat<-boot_10_top_500_count$gene[which(boot_10_top_500_count$n == max(boot_10_top_500_count$n)) ]  



```

### Save Object Sizes ***Specify Objects***
```{r, save objects}

# Note- rather than saving all created objects I will specify the three dataframes we need for the next code section. 

objects_created <- c( 
                      "boot_10_ttest_results",
                      "boot_10_top_500_summary",  #500 8  List with 10 df of top 500 summary 
                      "boot_10_top_500_count",  # count of genes found in top 500 of 10 dataframes
                      "boot_10_shared_feat" )

reccord_dim <- function(objects) {
  
  result <- list()
  
  for (obj_name in objects) {
    
    if (exists(obj_name)) {
      
      obj <- get(obj_name)
      
      if (is.data.frame(obj) || is.matrix(obj)) {
        
        rows <- nrow(obj)
        cols <- ncol(obj)
        result[[obj_name]] <- list(rows = rows, cols = cols)
        
      } else {
        
        warning(paste("Object labeled ", obj_name, "is not a data frame or a matrix. Skipping."))
      }
      
    } else {
      
      warning(paste("Object", obj_name, "does not exist. Skipping."))
      
    }
  }
  return(result)
}

objects_dim_list<-reccord_dim(objects_created)




#          Summary --------------------------------------------- 

print("Created Objects Summary:")
print(objects_dim_list)


```


### Exporting and Clean Up - Part 1/2
```{r, export and clean part 1}
#           Create Output File ------------------------------------------------------


current_output_folder<-paste0(script_name_base, "_", run_timestamp, ".Rmd")

dir.create(current_output_folder)

script_path_with_output_folder <- file.path(script_path_folder, 
                                            current_output_folder)

setwd(script_path_with_output_folder) # need to restate for each code chunk

#           Export Executed Code ----------------------------------------------------

copy_and_output_code <- function(script_path) {
  if (file.exists(script_path)) {
    
    rstudioapi::documentSave()
    
    script_content <- readLines(script_path)
    
    writeLines(script_content, current_output_folder)
  } else {
    message("Error: The specified script path does not exist.")
  }
}

# Call the function to copy and export the code
copy_and_output_code(script_path_current)

#           Export Run Info ---------------------------------------------------------

writeLines(capture.output(run_sessionInfo), "sessionInfo.txt")

```

### Exporting and Clean Up - Part 2/2 **Specify Objects**
```{r, export and clean part 2}

setwd(script_path_with_output_folder) # need to restate for each code chunk


#           Export Features as txt file 
writeLines(boot_10_shared_feat, "boot_10_shared_feat.txt")

#           Export Objects as .rda - **SPECIFY OBJECTS**----------------------------------------------------

objects_save<-c( objects_created, "objects_dim_list")

                            
save(list=objects_save,                   
     file = "env_obj.rda")
 
```


### Clear Env./Re-Add Generated Objects
```{r, clean env}
setwd(script_path_with_output_folder) # need to restate for each code chunk

#           Clear Environment/Re-Add Generated Objects  ------------------------------------------------------


#clear environment
rm(list = ls()) #USE VERY CAREFULLY ONLY ACTIVATE AT END OF PIPELINE
# rm(list = objects_save)

#readd the objects
load("env_obj.rda")


```
