---
title:  "8_prediction.rmd"
author: "Dali_Nemecio"
date: "`r Sys.Date()`"
output: 
  html_document:
    code_folding: hide
---

This code will predict on the mic-host-omic corr values, you must rerun this code to specify if you want, only +1 and -1 (sanity check since it was used to train/test the data) or NA (which would be prediction).

See Section "*Keystone* Select Data for Entry -1, +1, NA" to input desired predictions. 

# SET UP ------------

```{r , include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Set up

```{r}
#           Load Library **SPECIFY**------------------------------------------------------------
packages_needed<-c("knitr", "tidyverse",
                   "tibble", 
                   "dplyr",
                   "mlr","openxlsx",
                   "rstudioapi","stringr", "tidytable" , "grid", "pheatmap") 

for (pkg in packages_needed){
if ( !require(pkg, character.only = TRUE)){
  library(pkg, character.only = TRUE)
} 
}

#           Collect Script Info and Change To Script Directory ---------------


#Script Directory
script_path_current <- getSourceEditorContext()$path
script_path_folder<-sub("/[^/]*$", "", script_path_current)
script_name<-sub(".*/", "", script_path_current)
script_name_base<-sub("\\..*$", "", script_name)

#Change directory in all code chunks to current script location
knitr::opts_knit$set(root.dir = script_path_folder)
 

#           Collect Run Info------------------------------------------- 
run_timestamp <- format(Sys.time(), "%Y_%m_%d_%H%M")

run_sessionInfo<-sessionInfo()

```

### Shortcuts

```{r}
source("/Users/dalinemecio/Documents/1_Rotations/Brubaker/R/x_smaller_folders/short_cuts/short_cuts.R")
```

### Load Data and Objects Required

```{r}
# Load Data - Collect .rda files ----------------------------------------

#       Find Previous Code Folder -----------------------------

# Find the last slash
last_slash <- max(gregexpr("/", script_path_folder)[[1]])

# Extract the substring
substring_after_last_slash <- substr(script_path_folder, last_slash + 1, nchar(script_path_folder))

# Extract the first number
first_number <- regmatches(substring_after_last_slash, regexpr("[0-9]+", substring_after_last_slash))

# Convert the first number to an integer and subtract 1
new_number <- as.integer(first_number) - 1

# Construct the new path
new_path <- paste0(
  substr(script_path_folder, 1, last_slash),
  new_number,
  "_*"
)

# Function to find directory matching the pattern
find_directory <- function(path_with_wildcard) {
  
  # Extract directory path without wildcard
  directory_path <- dirname(path_with_wildcard)
  
  # List files matching the pattern
  matching_files <- list.files(directory_path, pattern = basename(path_with_wildcard))
  
  # Check if any matching directory exists
  matching_directories <- matching_files[dir.exists(file.path(directory_path, matching_files))]
  
  if (length(matching_directories) > 0) {
    
    return(file.path(directory_path, matching_directories[1]))
    
  } else {
    return(NULL)
  }
}

# Find the actual directory matching the wildcard
rda_directory <- find_directory(new_path)

#       Load .rda files  ---------------------------------

# Get list of all .rda files recursively
rda_files <- list.files(path = rda_directory, 
                        pattern = "\\.rda$",
                        recursive = TRUE,
                        full.names = TRUE)

# reccord what we had before 
objects_before<-ls()

# Load each .rda file in  folder 
for (file in rda_files) {
  load(file)
}
# reccord what we got

objects_after<-ls()   

# whats the diff 
newobjects<-setdiff(objects_after,objects_before)

# see new stuff
newobjects

#       Collect starting Envr.  ---------------------------------

objects_starting<-ls()

```

### Check Input Object Sizes

```{r}

dim_check <- list()
has_mismatch <- FALSE  # Variable to track if there's a mismatch

for (obj_name in objects_starting) {
  if (obj_name %in% names(objects_dim_list)) {
    correct_dimensions <- objects_dim_list[[obj_name]]
    actual_object <- get(obj_name)
    actual_dimensions <- list(rows = nrow(actual_object), cols = ncol(actual_object))
    
    if (identical(correct_dimensions, actual_dimensions)) {
      dim_check[[obj_name]] <- "Dimensions match"
    } else {
      # Construct the mismatch message
      mismatch_msg <- "Dimensions mismatch:"
      if (correct_dimensions$rows != actual_dimensions$rows) {
        mismatch_msg <- paste(mismatch_msg, "Expected rows is", correct_dimensions$rows,
                              "actual is", actual_dimensions$rows)
      }
      if (correct_dimensions$cols != actual_dimensions$cols) {
        mismatch_msg <- paste(mismatch_msg, "Expected columns is", correct_dimensions$cols,
                              "actual is", actual_dimensions$cols)
      }
      # Store the mismatch message in dim_check
      dim_check[[obj_name]] <- mismatch_msg
      has_mismatch <- TRUE  # Set has_mismatch to TRUE if there's a mismatch
    }
  }
}

# Print the output
print(dim_check)

# Check if there's a mismatch and stop if true
if (has_mismatch) {
  stop("There is at least one object with mismatched dimensions.")
}  else {"No mismatch in loaded object sizes, continue code execution." }

```

### Obtain Objects from Folder 1\_\*

```{r}
#       Find Object Code Folder -----------------------------------

        other_folder_number<-1

        # Construct the new path

        more_objects_path <- paste0(
          substr(script_path_folder, 1, last_slash),
          other_folder_number,
          "_*"
        )
        
        more_objects_path_defined<-find_directory(more_objects_path)
        
        
# Get objects from other folder 

rda_files<-list.files(path = more_objects_path_defined, 
                          pattern = "\\.rda$",
                          recursive = TRUE,
                          full.names = TRUE) 
   
# reccord what we had before 
objects_before<-ls()

# Load each .rda file in  folder 
for (file in rda_files) {
  load(file)
}
# reccord what we got

objects_after<-ls()   

# whats the diff 
newobjects<-setdiff(objects_after,objects_before)

# see new stuff
newobjects

#get downloaded objects 
objects_starting<-ls()

```

### Check Input Object Sizes *skip*

```{r, eval=FALSE }

dim_check <- list()
has_mismatch <- FALSE  # Variable to track if there's a mismatch

for (obj_name in objects_starting) {
  if (obj_name %in% names(objects_dim_list)) {
    correct_dimensions <- objects_dim_list[[obj_name]]
    actual_object <- get(obj_name)
    actual_dimensions <- list(rows = nrow(actual_object), cols = ncol(actual_object))
    
    if (identical(correct_dimensions, actual_dimensions)) {
      dim_check[[obj_name]] <- "Dimensions match"
    } else {
      # Construct the mismatch message
      mismatch_msg <- "Dimensions mismatch:"
      if (correct_dimensions$rows != actual_dimensions$rows) {
        mismatch_msg <- paste(mismatch_msg, "Expected rows is", correct_dimensions$rows,
                              "actual is", actual_dimensions$rows)
      }
      if (correct_dimensions$cols != actual_dimensions$cols) {
        mismatch_msg <- paste(mismatch_msg, "Expected columns is", correct_dimensions$cols,
                              "actual is", actual_dimensions$cols)
      }
      # Store the mismatch message in dim_check
      dim_check[[obj_name]] <- mismatch_msg
      has_mismatch <- TRUE  # Set has_mismatch to TRUE if there's a mismatch
    }
  }
}

# Print the output
print(dim_check)

# Check if there's a mismatch and stop if true
if (has_mismatch) {
  stop("There is at least one object with mismatched dimensions.")
}  else {"No mismatch in loaded object sizes, continue code execution." }

```

### Obtain Objects from Folder 3\_\*

```{r}
#       Find Object Code Folder -----------------------------------

        other_folder_number<-3

        # Construct the new path

        more_objects_path <- paste0(
          substr(script_path_folder, 1, last_slash),
          other_folder_number,
          "_*"
        )
        
        more_objects_path_defined<-find_directory(more_objects_path)
        
        
# Get objects from other folder 

rda_files<-list.files(path = more_objects_path_defined, 
                          pattern = "\\.rda$",
                          recursive = TRUE,
                          full.names = TRUE) 
   
# reccord what we had before 
objects_before<-ls()

# Load each .rda file in  folder 
for (file in rda_files) {
  load(file)
}
# reccord what we got

objects_after<-ls()   

# whats the diff 
newobjects<-setdiff(objects_after,objects_before)

# see new stuff
newobjects

#get downloaded objects 
objects_starting<-ls()

```

### Check Input Object Sizes

```{r}

dim_check <- list()
has_mismatch <- FALSE  # Variable to track if there's a mismatch

for (obj_name in objects_starting) {
  if (obj_name %in% names(objects_dim_list)) {
    correct_dimensions <- objects_dim_list[[obj_name]]
    actual_object <- get(obj_name)
    actual_dimensions <- list(rows = nrow(actual_object), cols = ncol(actual_object))
    
    if (identical(correct_dimensions, actual_dimensions)) {
      dim_check[[obj_name]] <- "Dimensions match"
    } else {
      # Construct the mismatch message
      mismatch_msg <- "Dimensions mismatch:"
      if (correct_dimensions$rows != actual_dimensions$rows) {
        mismatch_msg <- paste(mismatch_msg, "Expected rows is", correct_dimensions$rows,
                              "actual is", actual_dimensions$rows)
      }
      if (correct_dimensions$cols != actual_dimensions$cols) {
        mismatch_msg <- paste(mismatch_msg, "Expected columns is", correct_dimensions$cols,
                              "actual is", actual_dimensions$cols)
      }
      # Store the mismatch message in dim_check
      dim_check[[obj_name]] <- mismatch_msg
      has_mismatch <- TRUE  # Set has_mismatch to TRUE if there's a mismatch
    }
  }
}

# Print the output
print(dim_check)

# Check if there's a mismatch and stop if true
if (has_mismatch) {
  stop("There is at least one object with mismatched dimensions.")
}  else {"No mismatch in loaded object sizes, continue code execution." }

```

### Obtain Objects from Folder 5\_\*

```{r}
#       Find Object Code Folder -----------------------------------

        other_folder_number<-5

        # Construct the new path

        more_objects_path <- paste0(
          substr(script_path_folder, 1, last_slash),
          other_folder_number,
          "_*"
        )
        
        more_objects_path_defined<-find_directory(more_objects_path)
        
        
# Get objects from other folder 

rda_files<-list.files(path = more_objects_path_defined, 
                          pattern = "\\.rda$",
                          recursive = TRUE,
                          full.names = TRUE) 
   
# reccord what we had before 
objects_before<-ls()

# Load each .rda file in  folder 
for (file in rda_files) {
  load(file)
}
# reccord what we got

objects_after<-ls()   

# whats the diff 
newobjects<-setdiff(objects_after,objects_before)

# see new stuff
newobjects

#get downloaded objects 
objects_starting<-ls()

```

### Check Input Object Sizes

```{r}

dim_check <- list()
has_mismatch <- FALSE  # Variable to track if there's a mismatch

for (obj_name in objects_starting) {
  if (obj_name %in% names(objects_dim_list)) {
    correct_dimensions <- objects_dim_list[[obj_name]]
    actual_object <- get(obj_name)
    actual_dimensions <- list(rows = nrow(actual_object), cols = ncol(actual_object))
    
    if (identical(correct_dimensions, actual_dimensions)) {
      dim_check[[obj_name]] <- "Dimensions match"
    } else {
      # Construct the mismatch message
      mismatch_msg <- "Dimensions mismatch:"
      if (correct_dimensions$rows != actual_dimensions$rows) {
        mismatch_msg <- paste(mismatch_msg, "Expected rows is", correct_dimensions$rows,
                              "actual is", actual_dimensions$rows)
      }
      if (correct_dimensions$cols != actual_dimensions$cols) {
        mismatch_msg <- paste(mismatch_msg, "Expected columns is", correct_dimensions$cols,
                              "actual is", actual_dimensions$cols)
      }
      # Store the mismatch message in dim_check
      dim_check[[obj_name]] <- mismatch_msg
      has_mismatch <- TRUE  # Set has_mismatch to TRUE if there's a mismatch
    }
  }
}

# Print the output
print(dim_check)

# Check if there's a mismatch and stop if true
if (has_mismatch) {
  stop("There is at least one object with mismatched dimensions.")
}  else {"No mismatch in loaded object sizes, continue code execution." }

```

### Obtain Objects from Folder 6\_\*

```{r}
#       Find Object Code Folder -----------------------------------

        other_folder_number<-6

        # Construct the new path

        more_objects_path <- paste0(
          substr(script_path_folder, 1, last_slash),
          other_folder_number,
          "_*"
        )
        
        more_objects_path_defined<-find_directory(more_objects_path)
        
        
# Get objects from other folder 

rda_files<-list.files(path = more_objects_path_defined, 
                          pattern = "\\.rda$",
                          recursive = TRUE,
                          full.names = TRUE) 
   
# reccord what we had before 
objects_before<-ls()

# Load each .rda file in  folder 
for (file in rda_files) {
  load(file)
}
# reccord what we got

objects_after<-ls()   

# whats the diff 
newobjects<-setdiff(objects_after,objects_before)

# see new stuff
newobjects

#get downloaded objects 
objects_starting<-ls()

```

### Check Input Object Sizes

```{r}

dim_check <- list()
has_mismatch <- FALSE  # Variable to track if there's a mismatch

for (obj_name in objects_starting) {
  if (obj_name %in% names(objects_dim_list)) {
    correct_dimensions <- objects_dim_list[[obj_name]]
    actual_object <- get(obj_name)
    actual_dimensions <- list(rows = nrow(actual_object), cols = ncol(actual_object))
    
    if (identical(correct_dimensions, actual_dimensions)) {
      dim_check[[obj_name]] <- "Dimensions match"
    } else {
      # Construct the mismatch message
      mismatch_msg <- "Dimensions mismatch:"
      if (correct_dimensions$rows != actual_dimensions$rows) {
        mismatch_msg <- paste(mismatch_msg, "Expected rows is", correct_dimensions$rows,
                              "actual is", actual_dimensions$rows)
      }
      if (correct_dimensions$cols != actual_dimensions$cols) {
        mismatch_msg <- paste(mismatch_msg, "Expected columns is", correct_dimensions$cols,
                              "actual is", actual_dimensions$cols)
      }
      # Store the mismatch message in dim_check
      dim_check[[obj_name]] <- mismatch_msg
      has_mismatch <- TRUE  # Set has_mismatch to TRUE if there's a mismatch
    }
  }
}

# Print the output
print(dim_check)

# Check if there's a mismatch and stop if true
if (has_mismatch) {
  stop("There is at least one object with mismatched dimensions.")
}  else {"No mismatch in loaded object sizes, continue code execution." }

```

### Obtain Objects from Folder 7\_\*

```{r}
#       Find Object Code Folder -----------------------------------

        other_folder_number<-7

        # Construct the new path

        more_objects_path <- paste0(
          substr(script_path_folder, 1, last_slash),
          other_folder_number,
          "_*"
        )
        
        more_objects_path_defined<-find_directory(more_objects_path)
        
        
# Get objects from other folder 

rda_files<-list.files(path = more_objects_path_defined, 
                          pattern = "\\.rda$",
                          recursive = TRUE,
                          full.names = TRUE) 
   
# reccord what we had before 
objects_before<-ls()

# Load each .rda file in  folder 
for (file in rda_files) {
  load(file)
}
# reccord what we got

objects_after<-ls()   

# whats the diff 
newobjects<-setdiff(objects_after,objects_before)

# see new stuff
newobjects

#get downloaded objects 
objects_starting<-ls()

```

### Check Input Object Sizes

```{r}

dim_check <- list()
has_mismatch <- FALSE  # Variable to track if there's a mismatch

for (obj_name in objects_starting) {
  if (obj_name %in% names(objects_dim_list)) {
    correct_dimensions <- objects_dim_list[[obj_name]]
    actual_object <- get(obj_name)
    actual_dimensions <- list(rows = nrow(actual_object), cols = ncol(actual_object))
    
    if (identical(correct_dimensions, actual_dimensions)) {
      dim_check[[obj_name]] <- "Dimensions match"
    } else {
      # Construct the mismatch message
      mismatch_msg <- "Dimensions mismatch:"
      if (correct_dimensions$rows != actual_dimensions$rows) {
        mismatch_msg <- paste(mismatch_msg, "Expected rows is", correct_dimensions$rows,
                              "actual is", actual_dimensions$rows)
      }
      if (correct_dimensions$cols != actual_dimensions$cols) {
        mismatch_msg <- paste(mismatch_msg, "Expected columns is", correct_dimensions$cols,
                              "actual is", actual_dimensions$cols)
      }
      # Store the mismatch message in dim_check
      dim_check[[obj_name]] <- mismatch_msg
      has_mismatch <- TRUE  # Set has_mismatch to TRUE if there's a mismatch
    }
  }
}

# Print the output
print(dim_check)

# Check if there's a mismatch and stop if true
if (has_mismatch) {
  stop("There is at least one object with mismatched dimensions.")
}  else {"No mismatch in loaded object sizes, continue code execution." }

```

# needed objects
```{r}
dim(Master_MHG_corr_sig_NA_500)         
dim(Master_MHG_corr_sig_test_500)        
dim(Master_MHG_corr_sig_train_500)         


dim(top_500_summary)            
dim(drugFC_ordered) 
tunedSvmModel

```

# MAIN ----------------------------------------

# Define Functions

```{r}
# Prepare and strip data for MLR functions ----------

prep_mlr_pred<-function(df, featvec, statecol){
  
  
# col name consistency - gene col names in dataframe 
    names(df)<-gsub("\\-",".",names(df))
    

# col name consistency - Gene col names featvector
    featvec<-gsub("\\-",".",featvec)

    #desired col names in training data
    alongforride_colnames<-colnames(df[1:6])
    
    colnames_w_features<- c(alongforride_colnames, featvec)
   
  # Filter known classes using dynamic column name
  DF_known <- df %>%
    # dplyr::filter(.data[[statecol]] %in% c(-1, 1)) %>%
    dplyr::select(all_of(colnames_w_features))

  # Convert target to factor safely
  DF_known[[statecol]] <- factor(DF_known[[statecol]] #, levels = c( 1, -1)) 
                                    )
  
  # Strip down to target + features
  out_stripped <- DF_known %>%
    dplyr::select(all_of(c(statecol, featvec)))

  # Diagnostics
  print(paste0("Dimensions of entering df: ", dim(df)[1], " x ", dim(df)[2]))
  print(paste0("Dimensions of output df: ", dim(out_stripped)[1], " x ", dim(out_stripped)[2]))

  print("Count of drug metabolism state in out data:")
  print(table(out_stripped[[statecol]], useNA = "ifany" ))

  return(out_stripped)
  
}

```

## Assign name of model

```{r}
nameofmodel<-"MultiDrugSVM"
```

## *Keystone* Select Data for Entry -1, +1, NA

```{r}

test_train<-rbind(Master_MHG_corr_sig_test_500, Master_MHG_corr_sig_train_500) # Contains -1, +1

Master_MHG_corr_sig<-rbind(test_train, Master_MHG_corr_sig_NA_500 ) # Contains NA 

d(Master_MHG_corr_sig)  # Contains all -1, +1, and NA 


# Define Entering Data --------------
# Enter_data<-Master_MHG_corr_sig       # Contains all -1, +1, and NA 
  Enter_data<-test_train                # Contains all -1, +1
# Enter_data<-Master_MHG_corr_sig_NA_500  # Contains  NA 



# State Choice and collect info -------------------------

if (l(u(Enter_data$state)) == l(u(Master_MHG_corr_sig$state)) ){
  print("Will prediction on Data with known metbolism state -1, +1 (a sanity check). AND will predict on data with NA. ")
  
  microbestates<-"Microbes predicted on include known states (-1, +1) and NAs"
  
  
}

if (l(u(Enter_data$state)) == l(u(test_train$state)) ){
  print("Will prediction on Data with known metbolism state -1, +1 ONLY (a sanity check). No novel predictions being made on the NAs ")
  
  microbestates<-"Microbes predicted on include known states (-1, +1)."
  }
  
if (l(u(Enter_data$state)) == l(u(Master_MHG_corr_sig_NA_500$state)) ){
  print("Will predict on novel data with NA only, no known metabolism state data is being assessed. ")
  
  microbestates<-"Microbes predicted on are only NAs. "
}

```

## *Keystone* Main Prediction threshold 

```{r}

# With respect to probability of +1 call 

# Sensitivity Thresholds 
thresh_sensi_top
thresh_sensi_bot

print(paste0("Top Classification Threshold for Meta calls based on Sensi: ", thresh_sensi_top))
print(paste0("Top Classification Threshold for Meta calls based on Sensi: ",thresh_sensi_bot))

```

# Predictions on Data

### Prep Data 

Create Data to be predicted with Selected Features

```{r}

select_feats<-top_500_summary%>%pull(gene) # redundant but fxn needs it tp ru

data_prediction_stripped<-prep_mlr_pred(Enter_data, select_feats, "state")


```

### Execute 
Modify predictions based on sensitivity-determined threshold, model will auto generate predictions based on 0.5 class thresh 

Anything that is less that our Meta Thresh and higher than our Nonmeta Thresh is undetermined therefore denoted as 0. 

This means anything that is equal to our sensitivity-determined thresh is included in their respective class.

```{r}

# Make predictions on unknown microbes ------------------------
predictions<-predict(object = tunedSvmModel,
                     newdata= data_prediction_stripped) # keystone 

# Clean predictions, label groups  ------------------------

predictions_labeled<-cbind(Enter_data[["microbe"]],Enter_data[["drug"]],      as.data.frame(predictions)) 

colnames(predictions_labeled)[1]<- "Microbes"
colnames(predictions_labeled)[2]<- "Drugs"

predictions_labeled<-predictions_labeled%>%
                          mutate(group = paste(Microbes,Drugs, response, sep = "_"))%>%
                          mutate(response=as.numeric(as.character(response)))%>%  
                          mutate( #  Keystone APPLY THRESHOLD 
                                    response = case_when(
                                      prob.1 > thresh_sensi_top ~ 1,
                                      prob.1 < thresh_sensi_bot ~ -1,
                                      TRUE ~ 0
                                    ))%>%
                        arrange(desc(prob.1))
          
# Collect
predict_df_name<-deparse(substitute(predictions_labeled))


```

### Summarize 

```{r}

# Stats of Predictions and Probabilities ------------------------------
# Metabolizing probabilities for x axis order and CI calc ---------------------

predictions_sum<- predictions_labeled%>%
                        group_by(Microbes)%>%
                        summarise(prob1_ave=mean(prob.1),
                                  prob1_sd=sd(prob.1), 
                                  n=dplyr::n() ) %>%
                        arrange(desc(prob1_ave))%>%
                        mutate(
                          se_prob = prob1_sd / sqrt(n),
                          z_critical = qnorm(0.975), # Calculate z critical value for 95% confidence interval
                          ci_lower = prob1_ave - z_critical * se_prob,
                          ci_upper = prob1_ave + z_critical * se_prob
                        )

```

### Plot 

#### On Microbes

```{r}


# Data Prep ----------------------------------


#collect pos calls
pred_lab_round<-predictions_labeled%>%
                  dplyr::select(Microbes, prob.1, response)%>%
                  mutate(response=as.factor(response))
                  
                  
# collapse data
merged_data <- merge(pred_lab_round, predictions_sum, by = "Microbes")


# Define Values for Graphing ---------------------------------

level_order<-u(predictions_sum$Microbes) # NOTE - Meta average only to define x axis order 

# Specify colors 
group_colors <- c( "Nonmetabolize" = "#1e88e5",  "Metabolize"= "#d81b60","Indeterminate" = "grey")

merged_data$response <- factor(merged_data$response, 
                               levels = c(-1, 0, 1), 
                               labels = c("Nonmetabolize", "Indeterminate", "Metabolize"))

# PLOT ------------------
pred_plot<-{
  ggplot(merged_data, 
         aes(x = factor(Microbes, level = level_order), 
             y = prob.1, 
             color = response)) +
    
    theme_bw() +
    
    ylim(-0.01, 1.01) +
    geom_jitter(alpha = 0.5, width = 0.2, size = 2) +
    
    geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0.2, color = "black") +
    
    stat_summary(fun = mean, geom = "point", 
                 shape = 16, size = 2, col = "black")+
    
    geom_hline(yintercept=thresh_sensi_top, linetype="dashed", color = "darkgrey") + 
    geom_hline(yintercept=thresh_sensi_bot, linetype="dashed", color = "darkgrey") +
    
    
    
    scale_color_manual(values = group_colors,                        
                       breaks = c("Metabolize", "Indeterminate", "Nonmetabolize"), 
                       name = "Predicted Classification", 
                       ) +
    
    theme(
          plot.title = element_text(hjust =0.5, vjust = 4),
          plot.subtitle = element_text(hjust = 0.5, vjust = 2),
          
          axis.text.x = element_text(angle = 45, hjust = 1), 
          
          axis.title.x = element_text(vjust = -1), 
          axis.title.y = element_text(vjust = 5), 
          
          
          plot.margin = unit(c(1,1,1,1), "cm")) +
    
    labs(title = "Prediction Probabilities ",
         subtitle = nameofmodel
    ) +
    xlab("Microbes") +
    ylab("Probability of Metabolizing") +
    labs(
      caption = microbestates
    ) +
    theme(
      plot.caption = element_text(hjust = 1, vjust = 0)
    )
  
}


# Save 
ggplot2::ggsave("pred_plot.pdf",pred_plot,
        width = 7,
        height = 5)



```

#### On Drugs

#### Summarize Predictions on Drugs

```{r}

# Metabolizing probabilities for x axis order and CI calc ---------------------

predictions_sum_drugs<- predictions_labeled%>%
                        group_by(Drugs)%>%
                        summarise(prob1_ave=mean(prob.1),
                                  prob1_sd=sd(prob.1), 
                                  n=dplyr::n() ) %>%
                        arrange(desc(prob1_ave))%>%
                        mutate(
                          se_prob = prob1_sd / sqrt(n),
                          # Calculate z critical value for 95% confidence interval
                          z_critical = qnorm(0.975),
                          ci_lower = prob1_ave - z_critical * se_prob,
                          ci_upper = prob1_ave + z_critical * se_prob
                        )

```

#### Plot Predictions on Drugs

```{r}


# Data Prep ----------------------------------


#collect pos calls
pred_lab_round_drug<-predictions_labeled%>%
                  dplyr::select(Drugs, prob.1, response)%>%
                  mutate(response=as.factor(response))
                  
                  
# collapse data
merged_data_drug <- merge(pred_lab_round_drug, predictions_sum_drugs, by = "Drugs")


# Define Values for Graphing ---------------------------------

level_order_drug<-u(predictions_sum_drugs$Drugs) # NOTE - Meta average only to define x axis order 

# Specify colors 
group_colors <- c( "Nonmetabolize" = "#1e88e5",  "Metabolize"= "#d81b60","Indeterminate" = "grey")

merged_data_drug$response <- factor(merged_data_drug$response, 
                               levels = c(-1, 0, 1), 
                               labels = c("Nonmetabolize", "Indeterminate", "Metabolize"))

# PLOT ------------------
pred_plot_drugs<-{
  ggplot(merged_data_drug, 
         aes(x = factor(Drugs, level = level_order_drug), 
             y = prob.1, 
             color = response)) +
    
    theme_bw() +
    
    ylim(-0.01, 1.01) +
    geom_jitter(alpha = 0.5, width = 0.2, size = 2) +
    
    geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0.2, color = "black") +
    
    stat_summary(fun = mean, geom = "point", 
                 shape = 16, size = 2, col = "black")+
    
    geom_hline(yintercept=thresh_sensi_top, linetype="dashed", color = "darkgrey") + 
    geom_hline(yintercept=thresh_sensi_bot, linetype="dashed", color = "darkgrey") +
    
    
    
    scale_color_manual(values = group_colors,                        
                       breaks = c("Metabolize", "Indeterminate", "Nonmetabolize"), 
                       name = "Predicted Classification", 
                       ) +
    
    theme(
          plot.title = element_text(hjust =0.5, vjust = 4),
          plot.subtitle = element_text(hjust = 0.5, vjust = 2),
          
          axis.text.x = element_text(angle = 45, hjust = 1), 
          
          axis.title.x = element_text(vjust = -1), 
          axis.title.y = element_text(vjust = 5), 
          
          
          plot.margin = unit(c(1,1,1,1), "cm")) +
    
    labs(title = "Prediction Probabilities ",
         subtitle = nameofmodel
    ) +
    xlab("Drugs") +
    ylab("Probability of Metabolizing") +
    theme(
      plot.caption = element_text(hjust = 1, vjust = 0)
    )
  
}

# pred_plot_drug

# Normally would save at the end however for some reason it keep messing up the group order so we are saving it here. 
# Save 
ggplot2::ggsave("pred_plot_drugs.pdf", pred_plot_drugs,
        width = 7,
        height = 5)


```




## Prep - Orient Wider

```{r}

{
  
temp<-as.data.frame(predictions_labeled)%>%
                            select(Microbes, Drugs, `prob.1`)%>%
                            tidyr::pivot_wider(names_from = "Drugs", "values_from" = `prob.1`) # FYI produces NAS if combo not found 
  
temp<-as.data.frame(temp)%>%
                            dplyr::arrange(match(Microbes, ordered_bact_76_final))

predictions_labeled_wider<-as.data.frame(temp)%>% # order by reference vector
                            select(Microbes, any_of(ordered_drugs_176_final))

predictions_labeled_wider<-as.data.frame(predictions_labeled_wider)
rownames(predictions_labeled_wider)<-predictions_labeled_wider$Microbes


predictions_labeled_wider_strip<-predictions_labeled_wider%>%select(-Microbes)
}


```



# CORR ------------------------
with DrugFC

## Prep

### Clean names of DrugFC

```{r}
## Clean Microbe names 

d((drugFC_ordered)) # 76 176

# Clean the bacteria names set as rownames ----------------

  # Split DF into non-unique vs unique values 
  # Genus species that appears multi time cannot be a rowname
  # rownames must be unique 

  drugFC_ordered_t <- drugFC_ordered %>%       
    mutate(microbe = rownames(.)) %>%
    select(microbe, everything())
  
  rownames(drugFC_ordered_t)<- NULL 
  
  
  
    
  # Microbes that are non-unique 
    t_1 <- drugFC_ordered_t %>%
                          filter(str_starts(microbe, "bacteroides fragilis") |
                                   str_starts(microbe, "bacteroides thetaiotaomicron"))  
    
  # Clean Genus 
  t_1$microbe <- gsub(
                            "^bacteroides",     # pattern: starts with 'bacteroides'
                            "Bacteroides",      # replacement
                            t_1$microbe, 
                            ignore.case = FALSE
                          )
  
  # microbes that are unique therefore should have name cleaned 
    t_2 <- drugFC_ordered_t %>%  
                          filter(
                            !str_starts(microbe, "bacteroides fragilis") &
                            !str_starts(microbe, "bacteroides thetaiotaomicron")
                          )
    
    t_2_clean<-  t_2%>%mutate(
                microbe = microbe %>%
                  map_chr(~ {
                    words <- str_split(.x, " ")[[1]]   # split string by space
                    first_two <- words[1:2]            # take first two words
                    # Capitalize only the first letter of the first word
                    first_two[1] <- paste0(
                      toupper(substr(first_two[1], 1, 1)),
                      substr(first_two[1], 2, nchar(first_two[1]))
                    )
                    paste(first_two, collapse = " ")   # join back into string
                  })
              )

  # Rejoin unique and non unique microbe names 
    drugFC_ordered_clean_t<-rbind(t_1,t_2_clean)
    drugFC_ordered_clean_t<-drugFC_ordered_clean_t%>%select(microbe, everything())

    
   # produced objects 
    d(drugFC_ordered_clean_t) # 76 177 Total # 13452
    
```

There are unique microbes but there are multiples of the same genus species with unique strain associations.

### Elongate and Split Drug FC

```{r}
# Remove drugs that are not predicted on 

share1<-intersect( colnames(drugFC_ordered_clean_t)[-1], u(Enter_data$drug))


# Elongate -------------------

drugFC_long<-drugFC_ordered_clean_t%>%
                            select(microbe, all_of(share1))%>%
                            pivot_longer(cols = share1[1]:share1[l(share1)], 
                                         names_to = "Drugs", 
                                         values_to= "drugfc")

# Seperate out B. frag and B thet 

                        drugFC_split1_frag<-drugFC_long%>%
                                                                filter(str_starts(microbe, "Bacteroides fragilis")) %>%
                                                                as.data.frame(.)
                        

                        drugFC_split2_thet<-drugFC_long%>%
                                                                filter(str_starts(microbe, "Bacteroides thetaiotaomicron")) %>%
                                                                as.data.frame(.)
                      
                        
                                                                       
# Separate out the other microbes that ARE already unique 
                        drugFC_split3<-drugFC_long%>%
                                      filter(!str_starts(microbe, "Bacteroides fragilis") &
                                             !str_starts(microbe, "Bacteroides thetaiotaomicron"))  %>%
                                                                as.data.frame(.)




```

### Elongate and Split Prediction non unique out

```{r}


# Split ---------------------------------

# "Bacteroides fragilis"

        max_frag<-l(u(drugFC_split1_frag$microbe))-1

        pred_split1_frag<-predictions_labeled_wider %>%  
                                filter(
                                  str_starts(Microbes, "Bacteroides fragilis")
                                )%>%
                                bind_rows(slice(., 1)[rep(1, max_frag), ])

        # Rename to match with drugfc 
        pred_split1_frag$Microbes<-u(drugFC_split1_frag$microbe)
      
        

# "Bacteroides thetaiotaomicron"
        
        max_thet<-l(u(drugFC_split2_thet$microbe))-1
        
        pred_split2_thet<-predictions_labeled_wider %>%  
                                filter(
                                  str_starts(Microbes, "Bacteroides thetaiotaomicron")
                                )%>%
                                   bind_rows(slice(., 1)[rep(1, max_thet), ]) 
        
        # Rename to match with drugfc 
        pred_split2_thet$Microbes<-u(drugFC_split2_thet$microbe)

  
# Third slice       
  pred_split3<-predictions_labeled_wider %>%  
                          filter(
                            !str_starts(Microbes, "Bacteroides thetaiotaomicron") &
                            !str_starts(Microbes, "Bacteroides fragilis")
                          )



# Merge and pivot longer 
    pred_t<-rbind(pred_split1_frag,pred_split2_thet )
    pred_t2<-rbind(pred_t, pred_split3)

    
# collect col names 
    colnam<-n(pred_t2)[2:l(pred_t2)]
    
    
    predictions_labeled_long<-pred_t2%>%pivot_longer(cols = colnam[1]:colnam[l(colnam)],  
                                                     names_to= "Drugs", 
                                                     values_to = "prob.1")%>%
                                        filter( !is.na(prob.1 )) 


```

FYI, there are some microbe and drug combo that are not predicted on, presumably they were dropped at the correlation step.

### Merge predictions and drugFC

Inner join means it will only include values where the microbe and drug names match between the two DF 

```{r}

join<-inner_join(predictions_labeled_long, as.data.frame(drugFC_long),
                     by = c("Microbes" = "microbe", "Drugs" = "Drugs")) # bottle neck is the predictions_labeled_long



```

## Corr *Sensitivity-determined Threshold* -------------------------------
#### Functions 
```{r}

Corr_Class<-function(type, join, thresh_sensi_top, thresh_sensi_bot){
  
  # If combining Meta and Non meta groups do joint correlation
  if(type=="Combined"){
    
            # Separate out the meta and non meta predictions and DrugFCs 
          if(thresh_sensi_top == thresh_sensi_bot ){
            #The same 
            
            join<-join%>%
              filter(`prob.1`>= thresh_sensi_top | `prob.1`< thresh_sensi_bot)
            
            
          }else{
            join<-join%>%
              filter(`prob.1`>= thresh_sensi_top | `prob.1`<= thresh_sensi_bot)
          }
    
      if(nrow(join)>=2){
        
      # Do the correlation
      corr_out <-cor.test(join$prob.1, join$drugfc, method=c("spearman")) # keystone
      
      {
      # Replace NULL with NA safely
      param_val <- if (is.null(corr_out$parameter)) NA else corr_out$parameter
      pval_val  <- if (is.null(corr_out$p.value)) NA else corr_out$p.value
      cor_meta<-c(as.data.frame(corr_out$estimate)[1, 1])
      
      
      comb_out<-data.frame(
                          group       = c("Combined Meta and NonMeta"),
                          statistic   = c(as.data.frame(corr_out$statistic)[1, 1]),
                          parameter   = c(param_val),
                           p.value    = c(pval_val),
                          estimate    = c(cor_meta),
                          null.value  = c(as.data.frame(corr_out$null.value)[1, 1]),
                          alternative = c(corr_out$alternative),
                          method      = c(corr_out$method),
                          data.name   = c(corr_out$data.name)
                        )
                            
      }
      
      # Produced Correlations 
      
      print(comb_out)
      
      print(paste0("Assessing the probability of metabolozing from the combined -1 and +1 predictions with Zimm drugFC produces: ", cor_meta))
      
      }else{
        
        
      print(paste0("There are not enough Meta and NonMeta predictions (no thresh) between the drugs predicted on (thresh present) and shared with DrugFC inorder to do the combined correlation between probability and DrugFC. "))
      
              
      cor_meta <- NA_real_
      
      
      meta_1<-data.frame(
        group       = c("Combined Meta and NonMeta"),
        statistic   = c(NA_real_),
        parameter   = c(NA_real_),
        p.value     = c(NA_real_),
        estimate    = c(NA_real_),
        null.value  = c(NA_real_),
        alternative = c("Unable to Calculate"),
        method      = c(NA_real_),
        data.name   = c(NA_real_)
      )
        
      }# end of if statement
          
    
    
    
    
    
    
    
  } # end of COmbined 
  
  
  if(type=="Seperate"){ 
    
          if(thresh_sensi_top == thresh_sensi_bot ){
            #The same 
            
            pred_meta<-join%>%
              filter(`prob.1`>= thresh_sensi_top)
            
            pred_nonmeta<-join%>%
              filter(`prob.1`< thresh_sensi_bot)
            
          }else{

            pred_meta<-join%>%
              filter(`prob.1`>= thresh_sensi_top)
            
            pred_nonmeta<-join%>%
              filter(`prob.1`<= thresh_sensi_bot)
            
          }
  
  
  # Determine if both groups represented 
  n_samplecorr<-nrow(pred_nonmeta)+nrow(pred_meta)
  
  # If more than two drugs/drugFC combos do the Corr
  if(n_samplecorr >= 2){
    
    # Calculate the Meta Calls ------------------------

        if(nrow(pred_meta) != 0){
      
      corr_meta_calls <-cor.test(pred_meta$prob.1, pred_meta$drugfc, method=c("spearman")) # keystone
      
      
      # Replace NULL with NA safely
      param_val <- if (is.null(corr_meta_calls$parameter)) NA else corr_meta_calls$parameter
      pval_val  <- if (is.null(corr_meta_calls$p.value)) NA else corr_meta_calls$p.value
      cor_meta<-c(as.data.frame(corr_meta_calls$estimate)[1, 1])
      
      
      meta_1<-data.frame(
        group       = c("Meta calls"),
        statistic   = c(as.data.frame(corr_meta_calls$statistic)[1, 1]),
        parameter   = c(param_val),
        p.value    = c(pval_val),
        estimate    = c(cor_meta),
        null.value  = c(as.data.frame(corr_meta_calls$null.value)[1, 1]),
        alternative = c(corr_meta_calls$alternative),
        method      = c(corr_meta_calls$method),
        data.name   = c(corr_meta_calls$data.name)
      )
      
      
    }else{
      
      meta_1 <- data.frame(estimate = NA_real_)
      cor_meta <- NA_real_
      
      
      meta_1<-data.frame(
        group       = c("Meta calls"),
        statistic   = c(NA_real_),
        parameter   = c(NA_real_),
        p.value     = c(NA_real_),
        estimate    = c(NA_real_),
        null.value  = c(NA_real_),
        alternative = c("Unable to Calculate"),
        method      = c(NA_real_),
        data.name   = c(NA_real_)
      )
    } # end of meta if statement 
    
    # Calculate the NONMeta Calls ------------------------
    
    if(nrow(pred_nonmeta) != 0 ){
      
      corr_nonmeta_calls <-cor.test(pred_nonmeta$prob.1, pred_nonmeta$drugfc, method=c("spearman")) # keystone
      
      param_val_2 <- if (is.null(corr_nonmeta_calls$parameter)) NA else corr_nonmeta_calls$parameter
      pval_val_2  <- if (is.null(corr_nonmeta_calls$p.value)) NA else corr_nonmeta_calls$p.value
      cor_nonmeta<-c(as.data.frame(corr_nonmeta_calls$estimate)[1, 1])
      
      nonmeta_2 <- data.frame(
        group       = c("Nonmeta calls"),
        statistic   = c(as.data.frame(corr_nonmeta_calls$statistic)[1, 1]),
        parameter   = c(param_val_2),
        p.value     = c(pval_val_2),
        estimate    = c(cor_nonmeta),
        null.value  = c(as.data.frame(corr_nonmeta_calls$null.value)[1, 1]),
        alternative = c(corr_nonmeta_calls$alternative),
        method      = c(corr_nonmeta_calls$method),
        data.name   = c(corr_nonmeta_calls$data.name)
      )
      
    }else{
      nonmeta_2 <- data.frame(estimate = NA_real_)
      cor_nonmeta <- NA_real_
      
      
      nonmeta_2 <- data.frame(
        group       = c("Nonmeta calls"),
        statistic   = c(),
        parameter   = c(NA_real_),
        p.value     = c(NA_real_),
        estimate    = c(NA_real_),
        null.value  = c(NA_real_),
        alternative = c(NA_real_),
        method      = c("Unable to Calculate"),
        data.name   = c(NA_real_)
      )
      
    } # end of non meta statement 
    # Collect Correlation Output for Both --------------------
    
    
    cor_stats_pos1_neg1<-rbind(meta_1, nonmeta_2)
    

    print(paste0("The metabolizing predictions (thresh ",thresh_sensi_top,") produce a probability score that correlates to the Zimm drugFC ground truth by: ", cor_meta))
    
    print(paste0("The NONmetanolizing predictions (thresh",thresh_sensi_bot,") produce a probability score that correlates to the Zimm drugFC ground truth by: ", cor_nonmeta))

    
  }else{
    
    cor_stats_pos1_neg1<-c("There are not enough Meta and NonMeta predictions between the drugs predicted on (thresh present) and shared with DrugFC inorder to do the correlation between probability and DrugFC. ")

    
    
  } # end of enough rows  statement 
  
  print("Summary Table")
  print(cor_stats_pos1_neg1)
  
  
  
  
    
  } # End of Seperate
  
  
  
} # end of function 



Call_Sum<-function( join, thresh_sensi_top, thresh_sensi_bot) {
  
  
# Meta Predictions 
# Corr prob.1 with drugFC 
top_prob1<-join%>%filter(prob.1 >= thresh_sensi_top)%>%pull(prob.1)
top_drugfc<-join%>%filter(prob.1 >= thresh_sensi_top)%>%pull(drugfc)

meta_sum <- data.frame(
  group=c("Meta"),
  thresh_top = thresh_sensi_top,
  thresh_bottom = thresh_sensi_bot,
  
  prob1_mean   = round(mean(top_prob1, na.rm = TRUE), 2),
  prob1_median = round(median(top_prob1, na.rm = TRUE), 2),
  
  drugfc_mean   = round(mean(top_drugfc, na.rm = TRUE), 2),
  drugfc_median = round(median(top_drugfc, na.rm = TRUE), 2)
)
  
  



# NONmeta 
# Corr prob.1 with drugFC 
if(thresh_sensi_bot==thresh_sensi_top){
bot_prob1<-join%>%filter(prob.1 < thresh_sensi_bot)%>%pull(prob.1)
bot_drugfc<-join%>%filter(prob.1 < thresh_sensi_bot)%>%pull(drugfc)
}else{
  bot_prob1<-join%>%filter(prob.1 <= thresh_sensi_bot)%>%pull(prob.1)
bot_drugfc<-join%>%filter(prob.1 <= thresh_sensi_bot)%>%pull(drugfc) }


nonmeta_sum <- data.frame(
  group=c("NonMeta"),
  thresh_top = thresh_sensi_top,
  thresh_bottom = thresh_sensi_bot,
  
  prob1_mean   = round(mean(bot_prob1, na.rm = TRUE), 2),
  prob1_median = round(median(bot_prob1, na.rm = TRUE), 2),
  
  drugfc_mean   = round(mean(bot_drugfc, na.rm = TRUE), 2),
  drugfc_median = round(median(bot_drugfc, na.rm = TRUE), 2)
)
  

out<-rbind(meta_sum, nonmeta_sum)
print("Summary of Prob and DrugFC")
print(out)

} # end of call summary 



```

#### Seperate Predictions of -1 and +1

```{r}
Corr_Class("Seperate", join, thresh_sensi_top, thresh_sensi_bot)

```

#### Combined Predictions

```{r}
Corr_Class("Combined", join, thresh_sensi_top, thresh_sensi_bot)

```

#### Drop Drugs and Corr Comb

When we created DrugFC in the first section of this pipeline, there were drugs that were dropped by our code but were in the published heatmap, therefore I reintroduced them into the matrix so we could recreate the Zimm heatmap. However, note that some of these drugs may have been used to train the model (aslong as they appeared in the LINCS data).

Idea: Keep these 12 drugs dropped and run entire pipeline and see if it improves the performance.

For now, even if some of these drugs were used to train the model we will not retrain the model and instead drop them from assessing the correlation of the models prediction probability and the DrugFC.

```{r}
# Determined from rerunning first block of pipeline 

dif_t2<-c(
              "vinpocetine",
              "cyclobenzaprine",
              "fluvoxamine maleate",
              "alfuzosin",
              "diphenylpyraline",
              "lofexidine",
              "acecainide",
              "camylofine",
              "rizatriptan benzoate",
              "sulpiride",
              "trimetazidine",
              "periciazine"
            )

# Drop them from the probabilities 
join_drop<-join%>%filter(!(Drugs %in% dif_t2))

Corr_Class("Combined", join_drop, thresh_sensi_top, thresh_sensi_bot)



```



#### Mean and Median of Prob 1 and DrugFC

Run Section "Correlate Pred with DrugFC" in 8_prediction.rmd file, then return here!

This can only be calculated from microbes and drugs found in both the prediction data and that are found in the DrugFC table. There are some microbe drug combinations that are in the DrugFC table that were dropped from training and testing since they did not meet the microbe proportion metabolism threshold or the metaabolism threshold at 12 hours.

```{r}
Call_Sum(join, thresh_sensi_top, thresh_sensi_bot)
```




## Corr Thresh 0.5 ---------------------------

## *Define New Thresh*

```{r}
thresh50<-0.50
```

#### Seperate Predictions of -1 and +1

```{r}
Corr_Class("Seperate", join, thresh50, thresh50)
```

#### Combined Predictions

```{r}
Corr_Class("Combined", join, thresh50, thresh50)
```

#### Drop Drugs and Corr Comb

When we created DrugFC in the first section of this pipeline, there were drugs that were dropped by our code but were in the published heatmap, therefore I reintroduced them into the matrix so we could recreate the Zimm heatmap. However, note that some of these drugs may have been used to train the model (as long as they appeared in the LINCS data).

Idea: Keep these 12 drugs dropped and run entire pipeline and see if it improves the performance.

For now, even if some of these drugs were used to train the model we will not retrain the model and instead drop them from assessing the correlation of the models prediction probability and the DrugFC.

```{r}
# Determined from rerunning first block of pipeline 

dif_t2<-c(
              "vinpocetine",
              "cyclobenzaprine",
              "fluvoxamine maleate",
              "alfuzosin",
              "diphenylpyraline",
              "lofexidine",
              "acecainide",
              "camylofine",
              "rizatriptan benzoate",
              "sulpiride",
              "trimetazidine",
              "periciazine"
            )

# Drop them from the probabilities 
join_drop<-join%>%filter(!(Drugs %in% dif_t2))

Corr_Class("Combined", join_drop, thresh50, thresh50)



```

#### Mean and Median of Prob 1 and DrugFC

Run Section "Correlate Pred with DrugFC" in 8_prediction.rmd file, then return here!

This can only be calculated from microbes and drugs found in both the prediction data and that are found in the DrugFC table. There are some microbe drug combinations that are in the DrugFC table that were dropped from training and testing since they did not meet the microbe proportion metabolism threshold or the metaabolism threshold at 12 hours.

```{r}
# d(join) # 4294    4
Call_Sum(join, thresh50, thresh50)
```



# **CLOSING STEPS**

### Save Object Sizes ***Specify Objects***

```{r}


objects_created <- c( "tunedSvmModel", 
                      "predictions_labeled", 
                      "predictions_sum",          
                      "predictions_sum_drugs"        
            
                     
                         )

reccord_dim <- function(objects) {
  
  result <- list()
  
  for (obj_name in objects) {
    
    if (exists(obj_name)) {
      
      obj <- get(obj_name)
      
      if (is.data.frame(obj) || is.matrix(obj)) {
        
        rows <- nrow(obj)
        cols <- ncol(obj)
        result[[obj_name]] <- list(rows = rows, cols = cols)
        
      } else {
        
        warning(paste("Object labeled ", obj_name, "is not a data frame or a matrix. Skipping."))
      }
      
    } else {
      
      warning(paste("Object", obj_name, "does not exist. Skipping."))
      
    }
  }
  return(result)
}

objects_dim_list<-reccord_dim(objects_created)




#          Summary --------------------------------------------- 

print("Created Objects Summary:")
print(objects_dim_list)


```

### Exporting and Clean Up - Part 1/2

```{r}
#           Create Output File ------------------------------------------------------


current_output_folder<-paste0(script_name_base, "_", run_timestamp, ".Rmd")

dir.create(current_output_folder)

script_path_with_output_folder <- file.path(script_path_folder, 
                                            current_output_folder)

setwd(script_path_with_output_folder) # need to restate for each code chunk

#           Export Executed Code ----------------------------------------------------

copy_and_output_code <- function(script_path) {
  if (file.exists(script_path)) {
    
    rstudioapi::documentSave()
    
    script_content <- readLines(script_path)
    
    writeLines(script_content, current_output_folder)
  } else {
    message("Error: The specified script path does not exist.")
  }
}

# Call the function to copy and export the code
copy_and_output_code(script_path_current)

# Save Spreadsheet -----------

#           Export Run Info ---------------------------------------------------------

writeLines(capture.output(run_sessionInfo), "sessionInfo.txt")


#           Export Info ---------------------------------------------------------


wb <- createWorkbook()

addWorksheet(wb, "Predictions")
writeData(wb, "Predictions", predictions_labeled)

addWorksheet(wb, "Per Microbe")
writeData(wb, "Per Microbe", predictions_sum)

addWorksheet(wb, "Per Drug")
writeData(wb, "Per Drug", predictions_sum_drugs)

saveWorkbook(wb, "Predictions.xlsx", overwrite = TRUE)


```

### Exporting and Clean Up - Part 2/2 **Specify Objects**

```{r}

setwd(script_path_with_output_folder) # need to restate for each code chunk

#           Export Objects as .rda - **SPECIFY OBJECTS**----------------------------------------------------

objects_save<-c( objects_created, "objects_dim_list")

                            
save(list=objects_save,                   
     file = "env_obj.rda")
 


 
```

### Clear Env./Re-Add Generated Objects

```{r}
setwd(script_path_with_output_folder) # need to restate for each code chunk

#           Clear Environment/Re-Add Generated Objects  ------------------------------------------------------


#clear environment
rm(list = ls()) #USE VERY CAREFULLY ONLY ACTIVATE AT END OF PIPELINE
# rm(list = objects_save)

#readd the objects
load("env_obj.rda")


  ## END ---------------------------------------------------------------------


```
