---
title: "boot10_Master_analysis_parititioning_cleaning_100iterations"
author: "Dali_Nemecio"
date: "`r Sys.Date()`"
output: html_document
---

Training data is derived from 15 PTs, testing data derived from 5 PTS. Bootstrapped data is dervied from each PT set independently. 


## Start ---------------------------------------------------------------------

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Set up

```{r}
#           Load Library **SPECIFY**------------------------------------------------------------
packages_needed<-c("tidyverse",
                   "tibble", 
                   "dplyr","rsample",
                   "rstudioapi") 

for (pkg in packages_needed){
if ( !require(pkg, character.only = TRUE)){
  library(pkg, character.only = TRUE)
} 
}

#           Collect Script Info and Change To Script Directory ---------------


#Script Directory
script_path_current <- getSourceEditorContext()$path
script_path_folder<-sub("/[^/]*$", "", script_path_current)
script_name<-sub(".*/", "", script_path_current)
script_name_base<-sub("\\..*$", "", script_name)

#Change directory in all code chunks to current script location
knitr::opts_knit$set(root.dir = script_path_folder)
 

#           Collect Run Info------------------------------------------- 
run_timestamp <- format(Sys.time(), "%Y_%m_%d_%H%M")

run_sessionInfo<-sessionInfo()

#           Shortcut Custom Functions --------------------------------------------------------


v <- function(data) {
  tab_name <- deparse(substitute(data))
  View(data, title = tab_name)
}

d<-function(data){
  dim(data)
}

l<-function(data){
  length(data)
}

u<-function(data){
  unique(data)
}

h<-function(data){
  head(data)
}

t<-function(data){
  tail(data)
}


```

### Load Data and Objects Required
```{r}
# Load Data - Collect .rda files ----------------------------------------

#       Find Previous Code Folder -----------------------------

# Find the last slash
last_slash <- max(gregexpr("/", script_path_folder)[[1]])

# Extract the substring
substring_after_last_slash <- substr(script_path_folder, last_slash + 1, nchar(script_path_folder))

# Extract the first number
first_number <- regmatches(substring_after_last_slash, regexpr("[0-9]+", substring_after_last_slash))

# Convert the first number to an integer and subtract 1
new_number <- as.integer(first_number) - 1

# Construct the new path
new_path <- paste0(
  substr(script_path_folder, 1, last_slash),
  new_number,
  "_*"
)

# Function to find directory matching the pattern
find_directory <- function(path_with_wildcard) {
  
  # Extract directory path without wildcard
  directory_path <- dirname(path_with_wildcard)
  
  # List files matching the pattern
  matching_files <- list.files(directory_path, pattern = basename(path_with_wildcard))
  
  # Check if any matching directory exists
  matching_directories <- matching_files[dir.exists(file.path(directory_path, matching_files))]
  
  if (length(matching_directories) > 0) {
    
    return(file.path(directory_path, matching_directories[1]))
    
  } else {
    return(NULL)
  }
}

# Find the actual directory matching the wildcard
rda_directory <- find_directory(new_path)

#       Load .rda files  ---------------------------------

# Get list of all .rda files recursively
rda_files <- list.files(path = rda_directory, 
                        pattern = "\\.rda$",
                        recursive = TRUE,
                        full.names = TRUE)

# Load each .rda file
for (file in rda_files) {
  load(file)
}


#       Collect starting Envr.  ---------------------------------

objects_starting<-ls()

```


### Check Input Object Sizes

```{r}

dim_check <- list()
has_mismatch <- FALSE  # Variable to track if there's a mismatch

for (obj_name in objects_starting) {
  if (obj_name %in% names(objects_dim_list)) {
    correct_dimensions <- objects_dim_list[[obj_name]]
    actual_object <- get(obj_name)
    actual_dimensions <- list(rows = nrow(actual_object), cols = ncol(actual_object))
    
    if (identical(correct_dimensions, actual_dimensions)) {
      dim_check[[obj_name]] <- "Dimensions match"
    } else {
      # Construct the mismatch message
      mismatch_msg <- "Dimensions mismatch:"
      if (correct_dimensions$rows != actual_dimensions$rows) {
        mismatch_msg <- paste(mismatch_msg, "Expected rows is", correct_dimensions$rows,
                              "actual is", actual_dimensions$rows)
      }
      if (correct_dimensions$cols != actual_dimensions$cols) {
        mismatch_msg <- paste(mismatch_msg, "Expected columns is", correct_dimensions$cols,
                              "actual is", actual_dimensions$cols)
      }
      # Store the mismatch message in dim_check
      dim_check[[obj_name]] <- mismatch_msg
      has_mismatch <- TRUE  # Set has_mismatch to TRUE if there's a mismatch
    }
  }
}

# Print the output
print(dim_check)

# Check if there's a mismatch and stop if true
if (has_mismatch) {
  stop("There is at least one object with mismatched dimensions.")
}  else {"No mismatch in loaded object sizes, continue code execution." }

```


### Obtain Objects from Folder 1_*
 
```{r}
#       Find Object Code Folder 1_* -----------------------------------

        other_folder_number<-1

        # Construct the new path

        more_objects_path <- paste0(
          substr(script_path_folder, 1, last_slash),
          other_folder_number,
          "_*"
        )
        
        more_objects_path_defined<-find_directory(more_objects_path)
        
        
# Get objects from other 3_* folder 

rda_files<-list.files(path = more_objects_path_defined, 
                          pattern = "\\.rda$",
                          recursive = TRUE,
                          full.names = TRUE) 
   


# Load each .rda file in 3_* folder 
for (file in rda_files) {
  load(file)
}
        

#get downloaded objects 
objects_starting<-ls()

```

### Check Input Object Sizes 

```{r}

dim_check <- list()
has_mismatch <- FALSE  # Variable to track if there's a mismatch

for (obj_name in objects_starting) {
  if (obj_name %in% names(objects_dim_list)) {
    correct_dimensions <- objects_dim_list[[obj_name]]
    actual_object <- get(obj_name)
    actual_dimensions <- list(rows = nrow(actual_object), cols = ncol(actual_object))
    
    if (identical(correct_dimensions, actual_dimensions)) {
      dim_check[[obj_name]] <- "Dimensions match"
    } else {
      # Construct the mismatch message
      mismatch_msg <- "Dimensions mismatch:"
      if (correct_dimensions$rows != actual_dimensions$rows) {
        mismatch_msg <- paste(mismatch_msg, "Expected rows is", correct_dimensions$rows,
                              "actual is", actual_dimensions$rows)
      }
      if (correct_dimensions$cols != actual_dimensions$cols) {
        mismatch_msg <- paste(mismatch_msg, "Expected columns is", correct_dimensions$cols,
                              "actual is", actual_dimensions$cols)
      }
      # Store the mismatch message in dim_check
      dim_check[[obj_name]] <- mismatch_msg
      has_mismatch <- TRUE  # Set has_mismatch to TRUE if there's a mismatch
    }
  }
}

# Print the output
print(dim_check)

# Check if there's a mismatch and stop if true
if (has_mismatch) {
  stop("There is at least one object with mismatched dimensions.")
}  else {"No mismatch in loaded object sizes, continue code execution." }

```

### Fxn 
```{r}


reccord_dim <- function(objects) {
  
  result <- list()
  
  for (obj_name in objects) {
    
    if (exists(obj_name)) {
      
      obj <- get(obj_name)
      
      if (is.data.frame(obj) || is.matrix(obj)) {
        
        rows <- nrow(obj)
        cols <- ncol(obj)
        result[[obj_name]] <- list(rows = rows, cols = cols)
        
      } else {
        
        warning(paste("Object labeled ", obj_name, "is not a data frame or a matrix. Skipping."))
      }
      
    } else {
      
      warning(paste("Object", obj_name, "does not exist. Skipping."))
      
    }
  }
  return(result)
}
```

# MAIN ----------------------

# Set Seed
```{r}
set.seed(2026)
```

### Data Prep/Partition Fxn and Execute 

```{r}

# DEFINE FUNCTION ----------------------

dataprep<-function(boot10_Master_analysis){
  
      
    #           Remove NA ---------------------------------------------------------------
    
    
    #Confirm NA in boot10_Master_analysis
    sum(is.na(boot10_Master_analysis)) # 15,940,672          
    
    
    
    #Remove Rows with NA values and filter for 100 iterations in Gene correlation section 
    
    boot10_MA_100<-list()
    
    for(i in 1:length(boot10_Master_analysis)){
    
                current<-as.data.frame(boot10_Master_analysis[[i]])
      
                gene_index_start <- which(colnames(current) == "A2M")
    
                build<-current[complete.cases(current[,gene_index_start:ncol(current)]),]
                
    #           Filter for 100 iterations  -----------------------
    
                build<-build%>%
                            filter(MvG_iteration <= 100) 
                
      if(length(boot10_MA_100)==0){
        
        boot10_MA_100[[1]]<-build
        
      } else {
        
        boot10_MA_100[[(length(boot10_MA_100)+1)]]<-build
        
      }
                
    }
    
    str(boot10_MA_100) # 3714 9456
    
    
    return(boot10_MA_100)
    

  
  
} # END dataprep fxn 


# EXECUTE ----------------------------------------- 

train_boot10_MA_100<-dataprep(train_boot10_Master_analysis)

test_boot10_MA_100<-dataprep(test_boot10_Master_analysis)



```

### Clean up
```{r}
rm(df_hp1_rna_dat_select_tran, df_mbiocomp_dat_pres_pop_trans, mbio_taxo_clean,lincs_selectdrugs_share,  test_boot10_Master_analysis, train_boot10_Master_analysis, train_boot10_pt_ID_per_iteration, test_boot10_pt_ID_per_iteration, trans_data_share, zimm_metabolism_state)
```



### Generate Input Data Matrix: 10x Bootstrapped :: LINCS  **Gene expression** X Gene-Mic Corr (aka Microbe-Host) ------------------------------------------------------------- 

```{r}
 # Define Function ------------------------------------------------- 
lincs_x_gene_mbiocorr<-function(boot10_MA_100, df_lincs_gene_tv_sharedgenes){
     
      
      #objects needed 
      
                  # Make matrix 
                  df_lincs_gene_tv_sharedgenes<-as.matrix(df_lincs_gene_tv_sharedgenes)
                  
      #Prep empty list
      
      MA_100_gene_exp_multi_genesonly_list<-list()
      
      # select each bootstrapped matrix
      for(i in 1:length(boot10_MA_100)){
        
                  current<-as.data.frame(boot10_MA_100[[i]])
        
                  # define columns with genes
                  gene_col_index_start <- which(colnames(current) == "A2M")
        
                  gene_col_index_end <- which(colnames(current) == "ZZZ3")
                  
                  # Select columns with genes and transpose
                  MA_100_gene<-current[,gene_col_index_start:gene_col_index_end]
                  MA_100_gene<-as.matrix(MA_100_gene)
                  MA_100_gene_trans<-base::t(MA_100_gene)
      
                  
                  #multiply the gene expression LINCS sig to the microbe-gene corr (microbe-Host)
      MA_100_gene_exp_multi_genesonly<-df_lincs_gene_tv_sharedgenes[,1] * MA_100_gene_trans  # KEYSTONE 
      
                  #transpose back to normal orientation
                  MA_100_gene_exp_multi_genesonly<-base::t(MA_100_gene_exp_multi_genesonly)
            
                  
                  # Create Dataframe with new gene exp x microbe-gene corr                    
                  build<-cbind(current[,1:gene_col_index_start-1], MA_100_gene_exp_multi_genesonly) 
      
      
        if(length(MA_100_gene_exp_multi_genesonly_list)==0){
          
          MA_100_gene_exp_multi_genesonly_list[[1]]<-build
          
        } else {
          
          MA_100_gene_exp_multi_genesonly_list[[(length(MA_100_gene_exp_multi_genesonly_list)+1)]]<-build
          
        }
        
      }
      
      
      #add index value 
      for (i in 1:length(MA_100_gene_exp_multi_genesonly_list)){
        
        MA_100_gene_exp_multi_genesonly_list[[i]]<-as.data.frame(MA_100_gene_exp_multi_genesonly_list[[i]])
        
        MA_100_gene_exp_multi_genesonly_list[[i]]$boot_index<-i
        
        #reorder 
        gene_index_start <- which(colnames( MA_100_gene_exp_multi_genesonly_list[[i]]) == "A2M")
                  
        gene_index_end <- which(colnames( MA_100_gene_exp_multi_genesonly_list[[i]]) == "ZZZ3")
        
        info_cols<-names(MA_100_gene_exp_multi_genesonly_list[[i]][1:(gene_index_start-1)] )
        gene_cols<-names(MA_100_gene_exp_multi_genesonly_list[[i]][gene_index_start:gene_index_end])
        boot_index_col<-c("boot_index")
        
      MA_100_gene_exp_multi_genesonly_list[[i]]<-MA_100_gene_exp_multi_genesonly_list[[i]]%>%
                                      select(all_of(c(info_cols, boot_index_col,gene_cols)))
      }  
      
      # Produced object 
      str(MA_100_gene_exp_multi_genesonly_list)
      
      return(MA_100_gene_exp_multi_genesonly_list)
      

} # end of lincs_x_gene_mbiocorr fxn  


# Execute  FUNCTION ---------------------------


train_MA_100_gene_exp_multi_genesonly_list<-lincs_x_gene_mbiocorr(train_boot10_MA_100, df_lincs_gene_tv_sharedgenes)
test_MA_100_gene_exp_multi_genesonly_list<-lincs_x_gene_mbiocorr(test_boot10_MA_100, df_lincs_gene_tv_sharedgenes)


```

### Mid-Code Export Objects boot10_MA_100
```{r}

objects_created <- c("test_boot10_MA_100", 
                     "train_boot10_MA_100" 
                     
  )
                            

objects_dim_list_1<-reccord_dim(objects_created)


print("CREATED OBJECT DIMENSIONS AS FOLLOWS :")
print(objects_dim_list_1)



# Create Output File ------------------------------------------------------


current_output_folder<-paste0(script_name_base, "_", run_timestamp, ".Rmd")

dir.create(current_output_folder)

script_path_with_output_folder <- file.path(script_path_folder, 
                                            current_output_folder)

setwd(script_path_with_output_folder) # need to restate for each code chunk


# SAVE ------------------------------

objects_save<-c( objects_created, "objects_dim_list_1")



save(list=objects_save,                   
     file = "env_obj_boot10_MA_100.rda")

# Remove 
rm(test_boot10_MA_100, train_boot10_MA_100 )
 



```


# SPLIT INTO NA, TESTING, TRAINING 

## Filter for NA

```{r}

# Extract those with NA meta state
MA_100_gene_exp_multi_classbal_list_NA_PT15<-lapply(train_MA_100_gene_exp_multi_genesonly_list,  # class bal is irrelevant 
                                               function(x) x %>% filter(is.na(TV_state)))


# Extract those with NA meta state 
MA_100_gene_exp_multi_classbal_list_NA_PT5<-lapply(test_MA_100_gene_exp_multi_genesonly_list,             # class balanced on +1 and -1 only, carries NA 
                                               function(x) x %>% filter(is.na(TV_state)))


# Stack/ condense all boot top 500 in one dataframe ------------------

# Will merge NA from Training and Testing Patient population pools 

MA_100_gene_exp_multi_classbal_stacked_NA <-
    do.call(
        rbind,
        c(
            MA_100_gene_exp_multi_classbal_list_NA_PT15,
            MA_100_gene_exp_multi_classbal_list_NA_PT5
        )
    )


# Produced Objects ------------------------

paste0("Prediction data (NA from Train) dim: ", class(MA_100_gene_exp_multi_classbal_list_NA_PT15)," of length ", length(MA_100_gene_exp_multi_classbal_list_NA_PT15))

paste0("Prediction data (NA from Test) dim: ", class(MA_100_gene_exp_multi_classbal_list_NA_PT5)," of length ", length(MA_100_gene_exp_multi_classbal_list_NA_PT5))

paste0("Total NAs from Training and Testing data dim: ", class(MA_100_gene_exp_multi_classbal_stacked_NA)," of length ", length(MA_100_gene_exp_multi_classbal_stacked_NA))

dim(MA_100_gene_exp_multi_classbal_list_NA_PT15)
dim(MA_100_gene_exp_multi_classbal_list_NA_PT5)


```


## Mid-Code Export Objects NA List and Stacked 
```{r}

objects_created <- c("MA_100_gene_exp_multi_classbal_list_NA_PT15", 
                     "MA_100_gene_exp_multi_classbal_list_NA_PT5", 
                     "MA_100_gene_exp_multi_classbal_stacked_NA")
                     
                            

objects_dim_list_2<-reccord_dim(objects_created)


print("CREATED OBJECT DIMENSIONS AS FOLLOWS :")
print(objects_dim_list_2)


# reset wd 

setwd(script_path_with_output_folder) # need to restate for each code chunk



# SAVE ------------------------------

objects_save<-c( objects_created, "objects_dim_list_2")



# SAVE ------------------------------

save(list=objects_save,                   
     file = "env_obj_NA_list_stacked.rda")

# Remove 
rm(MA_100_gene_exp_multi_classbal_list_NA_PT15, MA_100_gene_exp_multi_classbal_list_NA_PT5, MA_100_gene_exp_multi_classbal_stacked_NA )
 



```


## Class Balancing Metabolism - for Training ONLY 

```{r}



# Define Proportion Functions ----------------------------------
  find_prop<- function(data){
    
  temp<-data

  temp$tally<-rep(1, nrow(temp))
  
 df<- xtabs(tally ~ Microbes + TV_state,  temp)
 
  prop<-proportions(df, "TV_state")
  
  prop<-as.data.frame(prop)
  
  prop<-prop%>%
        dplyr::arrange(Microbes)%>%
        mutate(Freq = round(Freq, digits = 1))

  return(prop)
  
  }

# assume all DF will have the same microbes, therefore the structure of the tables should contain the same microbes and be in alphabetical order. This code does not account for microbes being in different places within each respective table, nor if the data frames have different microbes. 
  
  
comp_prob_table<- function(df1,df2){ 
  
  
  df1_prob<-find_prop(df1)
  
  df2_prob<-find_prop(df2)
  
  if (any( df1_prob != df2_prob ) ){
    
    print("DF DO NOT share all values")
    return(FALSE) 
    
  } else { 
            return (TRUE) }
  
}

# Define Class Balance Function ----------------------------- 



execute_classbal<-function(boot_df){
  
# Split Bootstrap and Count Sample Size per Group ---------------------
  
  
  boot_df_pos1<- boot_df%>%
                        filter(TV_state == 1)
  
  boot_df_neg1<- boot_df%>%
                        filter(TV_state == -1)
  
  boot_df_NA<-boot_df%>%
                        filter(is.na(TV_state) )
  
  # Compare Sizes of Groups -----------------------
  
  if ( nrow(boot_df_neg1) != nrow(boot_df_pos1) ) {
    

    if ( nrow(boot_df_neg1) > nrow(boot_df_pos1) ){
      
            large_sample_size<- boot_df_neg1
    
            small_sample_size<- boot_df_pos1

            }
  
    if ( nrow(boot_df_neg1) < nrow(boot_df_pos1) ){
    
            large_sample_size<- boot_df_pos1
    
            small_sample_size<- boot_df_neg1
            
            print("FYI the LARGER group is TV_state POSITIVE 1 ")
    }
    
    
  # Prep for DF building ----------------------
    
    
    
  # Make Building Table Blank 
    
     building_table<-large_sample_size[FALSE,]
     
  # Define smaller group size to shrink larger
     
     small_group_size<- nrow(small_sample_size) 
     
  # Record ratio of larger group, determine counts needed to maintain proportions
           # We are assuming there are enough samples in the largest group to provide enough rows per microbe to condense to the smaller size 
     
    large_prob<-find_prop(large_sample_size)
     
     large_prob<-large_prob%>% 
                  mutate(require_count = ceiling( Freq * small_group_size ))
     
     
     # Fill building table with specified counts 
    
     for( i in 1:nrow(large_prob)){
      
    # Define microbe and count 
    large_prob_row<-large_prob[i,]
    
    mic<-large_prob_row$Microbes
    
    count<-large_prob_row$require_count
    
    
    # Sort DF with select microbe only 
    large_sample_size_microbe<-large_sample_size%>%
                                     filter(Microbes == mic)
  
    # Select required amount of rows 
    selected_count<-dplyr::sample_n(large_sample_size_microbe, count)
    
    
    # Merge with building table 
    building_table<-rbind(selected_count, building_table)
    
     }
     
    
     if( comp_prob_table(building_table, large_sample_size) == TRUE &    
         nrow(small_sample_size) <= nrow(building_table) & 
         nrow(building_table) <= nrow(small_sample_size)+2
         ) {
       
       print(paste0("Created equal group size between -1 and 1, size per (+/-1): ", nrow(building_table)) )
            

             classbal_boot<-rbind(small_sample_size, building_table, boot_df_NA)
       
       
     }
     
     
     
  } else {
  
  print(paste0("Existing equal group size between -1 and 1, size per: ", nrow(boot_df[which(boot_df$TV_state==-1),]) + nrow(boot_df[which(boot_df$TV_state== 1),]) ))
    
  classbal_boot<-boot_df
    
  }
  
  
return(classbal_boot)
  
  
} # End of function

# Apply to list of bootstrapped dataframes ----------------------------------- 
  
train_MA_100_gene_exp_multi_classbal_list<-lapply(train_MA_100_gene_exp_multi_genesonly_list, execute_classbal)



  
```





## Filter for -1 and +1 
```{r}

# Extract those with -1 or +1 meta state ------------------------

# Training 
MA_100_gene_exp_multi_classbal_list_train<-lapply(train_MA_100_gene_exp_multi_classbal_list, # does not need to be class balanced 
                                                  function(x) x %>% filter(!is.na(TV_state)))

# Test 
MA_100_gene_exp_multi_list_test<-lapply(test_MA_100_gene_exp_multi_genesonly_list, 
                                               function(x) x %>% filter(!is.na(TV_state)))


# Stacked ----------------------------

#condense all boot top 500 in one dataframe 

MA_100_gene_exp_multi_classbal_stacked_train<-do.call(rbind, MA_100_gene_exp_multi_classbal_list_train)

MA_100_gene_exp_multi_stacked_test<-do.call(rbind, MA_100_gene_exp_multi_list_test)






paste0("Training data dim: ", class(MA_100_gene_exp_multi_classbal_list_train)," of length ", length(MA_100_gene_exp_multi_classbal_list_train))

paste0("Testing data dim: ", class(MA_100_gene_exp_multi_list_test)," of length ", length(MA_100_gene_exp_multi_list_test))


```


## Mid-Code Export Objects Train and Test, List and Stacked 
```{r}

objects_created_train <- c("MA_100_gene_exp_multi_classbal_list_train", 
                     "MA_100_gene_exp_multi_classbal_stacked_train") 
                     


objects_created_test <- c("MA_100_gene_exp_multi_list_test", 
                     "MA_100_gene_exp_multi_stacked_test") 


objects_dim_list_3<-reccord_dim(objects_created_train)
objects_dim_list_4<-reccord_dim(objects_created_test)


print("CREATED OBJECT DIMENSIONS AS FOLLOWS :")
print(objects_dim_list_3)


print("CREATED OBJECT DIMENSIONS AS FOLLOWS :")
print(objects_dim_list_4)




# reset wd 

setwd(script_path_with_output_folder) # need to restate for each code chunk



# SAVE and remove ------------------------------

objects_save_train<-c( objects_created_train, "objects_dim_list_3")
objects_save_test<-c( objects_created_test, "objects_dim_list_4")



save(list=objects_save_train,                   
     file = "env_obj_Train_List_Stacked.rda")

rm(MA_100_gene_exp_multi_classbal_list_train, MA_100_gene_exp_multi_classbal_stacked_train )

save(list=objects_save_test,                   
     file = "env_obj_Test_List_Stacked.rda")

rm(MA_100_gene_exp_multi_list_test, MA_100_gene_exp_multi_stacked_test )
 



```
### Save Object Sizes ***Specify Objects***
```{r}
      
    
objects_dim_list<-c(objects_dim_list_1, objects_dim_list_2, objects_dim_list_3, objects_dim_list_4)





```


### Exporting and Clean Up - Part 1/2
```{r}

setwd(script_path_with_output_folder) # need to restate for each code chunk

#           Export Executed Code ----------------------------------------------------

copy_and_output_code <- function(script_path) {
  if (file.exists(script_path)) {
    
    rstudioapi::documentSave()
    
    script_content <- readLines(script_path)
    
    writeLines(script_content, current_output_folder)
  } else {
    message("Error: The specified script path does not exist.")
  }
}

# Call the function to copy and export the code
copy_and_output_code(script_path_current)

#           Export Run Info ---------------------------------------------------------

writeLines(capture.output(run_sessionInfo), "sessionInfo.txt")

```

### Exporting and Clean Up - Part 2/2 **Specify Objects**
```{r}
 
                            
save(objects_dim_list,                   
     file = "objects_dim_list.rda")


```
