---
title: "Zimm_clustogram"
author: "Dali_Nemecio"
date: "`r Sys.Date()`"
output: html_document
---

# START
# Set up 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Set WD
```{r}
wd <- "/Users/dalinemecio/Documents/1_Rotations/Brubaker/R/SVM_Multi_Drug"
setwd(wd)
```

## Library
```{r}
# List of required packages
packages <- c(
  "data.table",
  "readxl",
  "stringr",
  "readr",
  "rstudioapi",
  "tidyverse",
  "dplyr",
  "circlize", "pheatmap")



# Install missing packages
missing_pkgs <- packages[!packages %in% rownames(installed.packages())]
if(length(missing_pkgs)) install.packages(missing_pkgs)

lapply(packages, library, character.only = TRUE)
installed <- packages %in% rownames(installed.packages())


if (any(!installed)) {
  install.packages(packages[!installed])
}


```

## Get Script Info 
```{r}
#           Collect Script Info and Change To Script Directory ---------------


#Script Directory
script_path_current <- getSourceEditorContext()$path
script_path_folder<-sub("/[^/]*$", "", script_path_current)
script_name<-sub(".*/", "", script_path_current)
script_name_base<-sub("\\..*$", "", script_name)

#Change directory in all code chunks to current script location
knitr::opts_knit$set(root.dir = script_path_folder)
 

#           Collect Run Info------------------------------------------- 
run_timestamp <- format(Sys.time(), "%Y_%m_%d_%H%M")

run_sessionInfo<-sessionInfo()    
```



## Shortcuts 
```{r}
source("/Users/dalinemecio/Documents/1_Rotations/Brubaker/R/x_smaller_folders/short_cuts/short_cuts.R")
```

## Load Data 
```{r}

# Paths 
path_libr<-"/Users/dalinemecio/Documents/1_Rotations/Brubaker/7_Raw_Files_Library/"
path_data_local<-"/Users/dalinemecio/Documents/1_Rotations/Brubaker/R/SVM_Multi_Drug/z_data/"
path_explore<-"/Users/dalinemecio/Documents/1_Rotations/Brubaker/R/SVM_Multi_Drug/code_explore_data/zimm/"
# Objects 

# Zimmerman Supplemental 3 table 
zimm<-read_excel(paste0(path_data_local,"zimmerman_sup_table3.xlsx"), skip = 4) # cannot read in raw, format is screwy with first 4 rows 
zimm<-as.data.frame(zimm)
colnames(zimm)[1]<-c("drug") 


# Bacteria Order Found on publishd clustogram
ordered_bact_76 <- read.table(paste0(path_data_local,"publication_adaptations/ordered_76_bacteria_clustogram.txt"), 
                 header = FALSE,        
                 sep = "\t",          
                 stringsAsFactors = FALSE)

# Drug order found on published clustogram 
ordered_drugs_176 <- read.table(paste0(path_data_local,"publication_adaptations/ordered_176_meta_drugs_clustogram.txt"), 
                 header = FALSE,       
                 sep = "\t",           
                 stringsAsFactors = FALSE)


```


# MAIN -----------------------------------------------------------

# Clean Zimm
```{r}

# Make all character columns lowercase
zimm <- zimm %>% mutate(drug = tolower(drug))

```


# Reconstruct Values from Zimm Figure 1 
## Extract Values from Zimm Raw
```{r}
# 1. Enter -----------

df <- zimm
 
# 2. Identify column groups ----------------

fc_t      <- grep("^FC ", colnames(df), value = TRUE) # Will Capture FC and FC STD
fcstd_cols   <- grep("^FC STD", fc_t, value = TRUE)
fc_cols<-setdiff(fc_t, fcstd_cols)

pfdr_cols    <- grep("^p\\(FDR\\)", colnames(df), value = TRUE)
drug_col     <- "drug"
adaptive_col <- "Drug adaptive FC threshold %"

# 3. Extract matrices of specified values --------------

drugFC       <- as.matrix(df[, fc_cols])
drugFCstd    <- as.matrix(df[, fcstd_cols])
drugP        <- as.matrix(df[, pfdr_cols])
drugNames    <- df[[drug_col]]
drugAdaptive <- df[[adaptive_col]]
      
      # Confirm TRUE
      nrow(drugFC) == nrow(drugFCstd) && nrow(drugFCstd) == nrow(drugP)

# 4. Extract species names from FC columns ------------

species_names <- str_replace(fc_cols, "^FC ", "")
species_names <- str_squish(species_names)

# 5. Remove any 'Control' species -------------------

control_idx <- grepl("Control", species_names)
drugFC      <- drugFC[, !control_idx, drop = FALSE]
drugP       <- drugP[, !control_idx, drop = FALSE]
species_names <- species_names[!control_idx]

```

## Convert and Clean FC
```{r}

# Step 1: Convert adaptive FC to log2 scale -----------------

    drugAdaptive <- abs(log2((100 - drugAdaptive) / 100))  

# Step 2: Define thresholds ----------------------------------
    # This step filters drugs where NO SPECIES meet the adaptive FC and p value criteria for the drug. 
    # P value taken from MatLab code. 

    pThreshold  <- 0.05

# Step 3: Check the drugAdaptive threshold  ---------------------------------

    adaptive_pass <- drugFC <= -matrix(drugAdaptive, 
                                   nrow = nrow(drugFC), 
                                   ncol = ncol(drugFC),
                                   byrow = TRUE)

    # FC for that species +drug combo is less than of equal to the -drug adaptive value 
    # if FALSE that species does not meet the adaptive threshold 
    # if TRUE that species DOES meet the adaptive threshold 
    # A drug is removed only if all species fail,

    any(adaptive_pass) # TRUE


# Step 4: Check the p-value threshold ---------------------------------
    
    p_pass <- drugP <= pThreshold

    # if TRUE that species and drug pass the p value threshold
    # if false that species and drug do not pass the p value threhsold 

   any(p_pass) # TRUE 

# Step 5: Combine both conditions ---------------------------------
   
    combined_pass <- adaptive_pass & p_pass
   
    # if TRUE then  both the adaptive threhsold and p value threshold are passed 
        any(combined_pass) # TRUE 
    


# Step 6: Identify drugs to remove (columns where no rows pass) --------------
    
    remove_drugs <- rowSums(combined_pass) == 0 # counts per species how many drugs its passes both thresholds for 

    any(rowSums(combined_pass) == 0 ) # TRUE removed 91 drugs 


# Step 7: Filter out drugs failing thresholds ---------------------------------
    
    drugFC <- drugFC[!remove_drugs, , drop = FALSE]  # rows = drugs, columns = species
    drugP  <- drugP[!remove_drugs, , drop = FALSE]
    drugNames <- drugNames[!remove_drugs]
    drugAdaptive <- drugAdaptive[!remove_drugs]


# Step 8: Replace NaNs (as in MATLAB) ---------------------------------
    
    drugP[is.na(drugP)]     <- 1
    drugFC[is.na(drugFC)]   <- 0
    
# Step 9: Apply thresholds to FC and p-values, then convert to percent consumed ------
    # This step Masks the non-sig values for plotting, "visually blanked"
    
    drugFC <- drugFC * (drugP <= pThreshold) * 
              (drugFC <= -matrix(drugAdaptive, nrow = nrow(drugFC), 
                                 ncol = ncol(drugFC), byrow = TRUE))
    
    drugFC <- 1 - 2^drugFC   # convert to % consumed like MATLAB
    

```



# Prep for Heatmap 

## Forced clustering order

```{r}
# Execute --------------

# Transpose 
drugFC_df<-as.data.frame(base::t(drugFC))

# Assign Names and Clean  
colnames(drugFC_df)<-drugNames
rownames(drugFC_df)<-tolower(species_names)

# Clean Names from published clustogram 
ordered_bact_76<-tolower(ordered_bact_76$V1)
ordered_bact_76<-trimws(ordered_bact_76)
ordered_bact_76_final<-rev(ordered_bact_76)

ordered_drugs_176<-tolower(ordered_drugs_176$V1)
ordered_drugs_176_final<-trimws(ordered_drugs_176)


```



## Find Diff
```{r}
# ID which Drugs to drop - Compare Drug Composition -------------------------------------

# returns elements in first vec that is not in the second 
dif_t1<-setdiff(drugNames, ordered_drugs_176_final) # 

      l(dif_t1) # 16 
      # there are 16 drugs in our clustogram that are NOT in the published heatmap 
      # we have 16 additional drugs in ours

 
 
dif_t2<-setdiff(ordered_drugs_176_final, drugNames ) 
      l(dif_t2) # 12 
      # there are 12 drugs in their clustogram that are not in ours 
      # Adding the drugs that are dropped will be time consuming, we will accept the L and move on. 

  
      
      
```

FYI 
This code (like earlier in the pipeline) pulls the bacteria names for our regenerated clustogram from the names of the columns in the csv file, some of these names are either incorrectly formatted or spelled incorrectly(!). For ease sake, we will edit the .txt that contains the names copied from fig 3 of the publication so that it matches the names in the csv file we are using to derive the values for the clustogram. Note though that there are misspellings both unintentionally in the raw csv file and intentionally in the .txt file. The purpose of the intentional misspelling is so that our forced order clustogram will actually work with the mislabeled csv-inherited names. 

Here are the manual edits I made to the .txt file:  

t <- c(
  "escherichia coli k-12",                          # manually changes in .txt
  "bifidobacterium adolescentis atcc15703",         # edited number
  "enterobacter cancerogenus atcc35316",            # edit numb
  "pretovella copri dsm18205",                      # spelled incorrectly in “Raw csv” prob b/c of how the string was extracted. For ease sake I will change the .txt file to also be incorrect
  "bifidobacterium longum subsp. infantis ccug52486", # manually changed in .txt
  "lactobacillus reuteri cf48-3a bei hm-102",       # manually change in .txt I think they shortened some of the names in the clustogram figure
  "bifidobacterium ruminatum",                      # spelled incorrectly in , manually changed
  "akkermansia muciniphila atccbaa-835",            # edit numb
  "odoribacter splanchnius",                        # edit .txt name
  "bacteroides wh2 wh2",                            # edit name
  "bryantia formatexigens dsm14469",                # edit name
  "alistipes indistinctus dsm 22520",               # edit name
  "victivallis vadensis atcc baa-548"               # edit name
)



## Modify to Mimic Fig 1 
```{r}

# 1. Drop drugs that are not in published fig 1
    # We are removing the 16 drugs that remained in our drugFC but are not found in the published clustogram. 
    drugFC_ordered<-drugFC_df%>%select(-all_of(dif_t1))

# 2. Recreate/add drug for missing/dropped drugs
    # These are the 12 drugs that are in their published clustogram that were dropped while generating our drugFC. 
    # Since they were dropped we will readd then but with zero FC values. 

    mat <- matrix(0, nrow = nrow(drugFC_ordered), ncol = l(dif_t2)) 
    ord_t<-as.data.frame(mat)
    colnames(ord_t)<-dif_t2
    
# 3. Merge the df
    
    drugFC_ordered<- cbind(drugFC_ordered, ord_t)
    
# 4. Order cols as in Fig 1 
    
    drugFC_ordered<-drugFC_ordered%>%
                                select(all_of(ordered_drugs_176_final))
    
# 5. Reorder rows to match Fig 1
    
    pos <- match(ordered_bact_76_final, rownames(drugFC_ordered))
    drugFC_ordered <- drugFC_ordered[pos[!is.na(pos)], , drop = FALSE]


```

# CLOSING --------------------------------------------------
### Save Object Sizes ***Specify Objects***
```{r}

# Note- rather than saving all created objects I will specify the three dataframes we need for the next code section. 

objects_created <- c("drugFC_ordered",
                     "ordered_drugs_176_final",
                     "ordered_bact_76_final"
                     )

reccord_dim <- function(objects) {
  
  result <- list()
  
  for (obj_name in objects) {
    
    if (exists(obj_name)) {
      
      obj <- get(obj_name)
      
      if (is.data.frame(obj) || is.matrix(obj)) {
        
        rows <- nrow(obj)
        cols <- ncol(obj)
        result[[obj_name]] <- list(rows = rows, cols = cols)
        
      } else if(is.vector(obj)){
        
        length <- length(obj)
      
        result[[obj_name]] <- list(rows = length, cols = NA)
      
      } else {
        
        warning(paste("Object labeled ", obj_name, "is not a data frame or a matrix, or a vector. Skipping."))
      }
      
    } else {
      
      warning(paste("Object", obj_name, "does not exist. Skipping."))
      
    }
  }
  return(result)
}

objects_dim_list<-reccord_dim(objects_created)

```

### Exporting and Clean Up - Part 1/2
```{r}
#           Create Output File ------------------------------------------------------


current_output_folder<-paste0(script_name_base, "_", run_timestamp, ".Rmd")

dir.create(current_output_folder)

script_path_with_output_folder <- file.path(script_path_folder, 
                                            current_output_folder)

setwd(script_path_with_output_folder) # need to restate for each code chunk

#           Export Executed Code ----------------------------------------------------

copy_and_output_code <- function(script_path) {
  if (file.exists(script_path)) {
    
    rstudioapi::documentSave()
    
    script_content <- readLines(script_path)
    
    writeLines(script_content, current_output_folder)
  } else {
    message("Error: The specified script path does not exist.")
  }
}

# Call the function to copy and export the code
copy_and_output_code(script_path_current)

#           Export Run Info ---------------------------------------------------------

writeLines(capture.output(run_sessionInfo), "sessionInfo.txt")


```

### Exporting and Clean Up - Part 2/2 **Specify Objects**
```{r}

setwd(script_path_with_output_folder) # need to restate for each code chunk

#           Export Objects as .rda - **SPECIFY OBJECTS**----------------------------------------------------

objects_save<-c( objects_created, "objects_dim_list")

                            
save(list=objects_save,                   
     file = "env_obj.rda")



# Export as CSV 

write.csv(drugFC_ordered, file = paste0(script_path_with_output_folder, "/drugFC_ordered.csv"), row.names = TRUE)

# Export Plot 

pdf(file.path(script_path_with_output_folder, "clust_forcedorder.pdf"), width = 11, height = 6)

grid::grid.newpage()
grid::grid.draw(hm$gtable)
dev.off()

 
```

