---
title: "MLR_Training_V7.Rmd"
author: "Dali_Nemecio"
date: "`r Sys.Date()`"
output: 
  html_document:
    code_folding: hide
---

This code uses MA_100_gene_exp_multi_classbal_list_train[[1]] as an input.

FYI - code loads objects that are not used - just by product of how the code was written.



# START ------------------------
### Set up

```{r, setup}
# Set Up - Section 1 -------------------------------------------------------
#           rmd set up----------------------------------------
knitr::opts_chunk$set(echo = TRUE)


#           Load Library **SPECIFY**------------------------------------------------------------
packages_needed<-c("knitr","readr",
                   "tidyverse",
                   "tibble", 
                   "dplyr",
                   "rstudioapi","caret",
                   "kernlab", "measures", "PRROC", "mlr", 
                   "tidyverse") #


for (pkg in packages_needed){
if ( !require(pkg, character.only = TRUE)){
  library(pkg, character.only = TRUE)
} 
     
}



#           Collect Script Info and Change To Script Directory ---------------


#Script Directory
script_path_current <- getSourceEditorContext()$path
script_path_folder<-sub("/[^/]*$", "", script_path_current)
script_name<-sub(".*/", "", script_path_current)
script_name_base<-sub("\\..*$", "", script_name)
#Change directory in all code chunks to current script location

knitr::opts_knit$set(root.dir = script_path_folder)
 

#           Collect Run Info------------------------------------------- 
run_timestamp <- format(Sys.time(), "%Y_%m_%d_%H%M")

run_sessionInfo<-sessionInfo()


#           Shortcut Custom functions --------------------------------------------------------


v <- function(data) {
  tab_name <- deparse(substitute(data))
  View(data, title = tab_name)
}

d<-function(data){
  dim(data)
}

l<-function(data){
  length(data)
}

u<-function(data){
  unique(data)
}

h<-function(data){
  head(data)
}

t<-function(data){
  tail(data)
}


# End Set up

```

### Load Data and Objects Required 
```{r, Load Data and Objects Required}
# Load Data - Collect .rda files ----------------------------------------

#       Find Previous Code Folder -----------------------------

# Find the last slash
last_slash <- max(gregexpr("/", script_path_folder)[[1]])

# Extract the substring
substring_after_last_slash <- substr(script_path_folder, last_slash + 1, nchar(script_path_folder))

# Extract the first number
first_number <- regmatches(substring_after_last_slash, regexpr("[0-9]+", substring_after_last_slash))

# Convert the first number to an integer and subtract 1
new_number <- as.integer(first_number) - 1

# Construct the new path
new_path <- paste0(
  substr(script_path_folder, 1, last_slash),
  new_number,
  "_*"
)

# Function to find directory matching the pattern
find_directory <- function(path_with_wildcard) {
  
  # Extract directory path without wildcard
  directory_path <- dirname(path_with_wildcard)
  
  # List files matching the pattern
  matching_files <- list.files(directory_path, pattern = basename(path_with_wildcard))
  
  # Check if any matching directory exists
  matching_directories <- matching_files[dir.exists(file.path(directory_path, matching_files))]
  
  if (length(matching_directories) > 0) {
    
    return(file.path(directory_path, matching_directories[1]))
    
  } else {
    return(NULL)
  }
}

# Find the actual directory matching the wildcard
rda_directory <- find_directory(new_path)



#       Load .rda files  ---------------------------------
         

# Get list of all .rda files recursively
rda_files <- list.files(path = rda_directory, 
                        pattern = "\\.rda$",
                        recursive = TRUE,
                        full.names = TRUE)

# Load each .rda file
for (file in rda_files) {
  load(file)
}


#       Collect starting Envr.  ---------------------------------

objects_starting<-ls()


```

### Check Input Object Sizes 

```{r, Check Input Object Sizes - Previous File}

dim_check <- list()
has_mismatch <- FALSE  # Variable to track if there's a mismatch

for (obj_name in objects_starting) {
  if (obj_name %in% names(objects_dim_list)) {
    correct_dimensions <- objects_dim_list[[obj_name]]
    actual_object <- get(obj_name)
    actual_dimensions <- list(rows = nrow(actual_object), cols = ncol(actual_object))
    
    if (identical(correct_dimensions, actual_dimensions)) {
      dim_check[[obj_name]] <- "Dimensions match"
    } else {
      # Construct the mismatch message
      mismatch_msg <- "Dimensions mismatch:"
      if (correct_dimensions$rows != actual_dimensions$rows) {
        mismatch_msg <- paste(mismatch_msg, "Expected rows is", correct_dimensions$rows,
                              "actual is", actual_dimensions$rows)
      }
      if (correct_dimensions$cols != actual_dimensions$cols) {
        mismatch_msg <- paste(mismatch_msg, "Expected columns is", correct_dimensions$cols,
                              "actual is", actual_dimensions$cols)
      }
      # Store the mismatch message in dim_check
      dim_check[[obj_name]] <- mismatch_msg
      has_mismatch <- TRUE  # Set has_mismatch to TRUE if there's a mismatch
    }
  }
}

# Print the output
print(dim_check)

# Check if there's a mismatch and stop if true
if (has_mismatch) {
  stop("There is at least one object with mismatched dimensions.")
}  else {"No mismatch in loaded object sizes, continue code execution." }

```

### Clean up 
```{r}
rm(boot_10_top_500_count , boot_10_top_500_summary ,  boot_10_ttest_results, objects_dim_list_1)
```


### Obtain Objects from folder 3_*
```{r, Obtain Objects from folder 3_*}
#       Find Object Code Folder 3_* -----------------------------------

        other_folder_number<-3

        # Construct the new path

        more_objects_path <- paste0(
          substr(script_path_folder, 1, last_slash),
          other_folder_number,
          "_*"
        )
        
        more_objects_path_defined<-find_directory(more_objects_path)
        
        
# Get objects from other 3_* folder 

rda_files<-list.files(path = more_objects_path_defined, 
                          pattern = "\\Train_List_Stacked.rda$",
                          recursive = TRUE,
                          full.names = TRUE) 
   
# Load each .rda file in 3_* folder 
for (file in rda_files) {
  load(file)
}
        
rda_files<-list.files(path = more_objects_path_defined, 
                          pattern = "\\Test_List_Stacked.rda$",
                          recursive = TRUE,
                          full.names = TRUE) 
   

# Load each .rda file in 3_* folder 
for (file in rda_files) {
  load(file)
}
        


#get downloaded objects 
objects_starting<-ls()


print(more_objects_path_defined) # path that defines files retrieved 
```


### Clean up 
```{r}
rm(objects_dim_list_3, objects_dim_list_4, MA_100_gene_exp_multi_classbal_stacked_train, MA_100_gene_exp_multi_stacked_test 
   , test_boot10_MA_100, train_boot10_MA_100)
```


# MAIN ------------------------------
# Define and Set Required Objects -------------
# Set Seed
```{r}
set.seed(2026)
```
 
# Define Functions 
```{r}
# Prepare and strip data for MLR functions ----------

prep_mlr<-function(df, featvec, statecol){
  
  
# col name consistency - gene col names in dataframe 
    names(df)<-gsub("\\-",".",names(df))
    

# col name consistency - Gene col names featvector
    featvec<-gsub("\\-",".",featvec)

    #desired col names in training data
    alongforride_colnames<-colnames(df[1:6])
    
    colnames_w_features<- c(alongforride_colnames, featvec)
   
  # Filter known classes using dynamic column name
  DF_known <- df %>%
    dplyr::filter(.data[[statecol]] %in% c(-1, 1)) %>%
    dplyr::select(all_of(colnames_w_features))

  # Convert target to factor safely
  DF_known[[statecol]] <- factor(DF_known[[statecol]], levels = c( 1, -1))

  # Strip down to target + features
  out_stripped <- DF_known %>%
    dplyr::select(all_of(c(statecol, featvec)))

  # Diagnostics
  print(paste0("Dimensions of entering df: ", dim(df)[1], " x ", dim(df)[2]))
  print(paste0("Dimensions of output df: ", dim(out_stripped)[1], " x ", dim(out_stripped)[2]))

  print("Count of drug metabolism state in out data:")
  print(table(out_stripped[[statecol]]))

  return(out_stripped)
  
}

# Generate Conf Matr ----------

conf_mat<-function(df, thresh = NULL ){
  
  
# Comment on Threshold  
if(!is.null(thresh)){
  
df<-df%>%mutate(response = ifelse( prob.1 >= thresh, 1, -1))

print(paste0("Adjusted Threshold, positive class defined by :", thresh))

}else{
  
  check_pos_thresh(df)
  
}   
  
# Prep for Confusion Matrix ---------------
  
  df<-df%>%
      mutate(
        truth    = factor(truth, levels = c(1, -1)),
        response = factor(response, levels = c(1, -1))
      )
        
# Make Confusion Matrix -------------------
  
conf_ob<-confusionMatrix(data = df$response, reference = df$truth)


# Confusion Matrix as DF --------------
cm_df<-as.data.frame(conf_ob$table)


cm_df<-as.data.frame(cm_df)%>%
            rename(`response`=Prediction, 
                               `truth`=Reference, 
                               `n`=Freq)%>%
            select(truth, response, n)%>%
            mutate(order = case_when(         # Arrange rows in the order: TN, FP, FN, TP
              truth == -1 & response == -1 ~ 1,  # TN
              truth == -1 & response == 1  ~ 2,  # FP
              truth == 1  & response == -1 ~ 3,  # FN
              truth == 1  & response == 1  ~ 4   # TP
            )) %>%
            arrange(order) %>%
            select(-order)  # remove helper column

return(cm_df)

}


# Calculate the Performance Metrics  ------------ 

calc_perf<-function(df, col_label){

# Prep for Confusion Matrix ---------------
  
  df<-df%>%
      mutate(
        truth    = factor(truth, levels = c(1, -1)),
        response = factor(response, levels = c(1, -1))
      )
        
# Make Confusion Matrix -------------------
  
conf_ob<-confusionMatrix(data = df$response, reference = df$truth)

# Extract Default Calculated Metrics ---------------
conf_perf<-as.data.frame(conf_ob$byClass)
colnames(conf_perf)[1]<-col_label  

temp<-as.data.frame(conf_ob$overall)
colnames(temp)[1]<-col_label  

met_1<-rbind(conf_perf, temp )

  
# Determine Hand Calculated Metrics ----------------------

TPR  <- conf_ob$byClass["Sensitivity"]
TNR  <- conf_ob$byClass["Specificity"]
FPR  <- 1 - TNR
FNR  <- 1 - TPR
MMCE <- 1 - conf_ob$overall["Accuracy"]

met_2 <- base::t(data.frame(mmce = MMCE, fpr = FPR, fnr = FNR, tpr = TPR, tnr = TNR))
colnames(met_2)[1]<-col_label



# Determine Alternative Function Calculated Metrics ----------------------
    
# Measure AUC 
AUC_ROC<-measureAUC(probabilities = df$prob.1, 
                   truth = df$truth,
                   negative = as.character(-1), 
                   positive = as.character(1)) # MLR Fxn 


# Measure Area Under Precision Recall Curve 
interest_scores<-df$prob.1[df$truth == 1]
other_scores<-df$`prob.1`[df$truth == -1]
au_pr_out <- PRROC::pr.curve(scores.class0 = as.numeric(interest_scores), # class of interest aka positive class aka +1 
                       scores.class1 = as.numeric(other_scores),
                       curve = TRUE)

AUC_PR<-au_pr_out$auc.integral


temp<-data.frame(AUC_ROC=AUC_ROC, AUC_PR=AUC_PR )
met_3<-base::t(temp)
colnames(met_3)[1]<-col_label


# Clean and Return -------------------------
metric_order <- c(
  
  "Precision",
  "Accuracy",
  "Recall",
  "Specificity",
  
  "AUC_ROC", 
  "AUC_PR", 

  "mmce", 
  "fpr", 
  "fnr", 
  "tpr", 
  "tnr",
  
  
  "F1",
  "Pos Pred Value",
  "Neg Pred Value",
  "Sensitivity",
  "Prevalence",
  "Detection Rate",
  "Detection Prevalence",
  
  "Kappa",
  "Balanced Accuracy", 
  "AccuracyLower",
  "AccuracyUpper",
  "AccuracyNull",
  "AccuracyPValue",
  "McnemarPValue"
)


# Collapse all Metircs into DF 
out<-rbind(met_1, met_2, met_3)
out <- out[metric_order, , drop = FALSE]


# Convert NAN and NA to Zero and Round
out<-out%>%
  mutate(across(everything(), ~ ifelse(is.na(.) | is.nan(.), 0, .))) %>%
  mutate(across(everything(), ~ round(., 2)))


return(out)  
    
  
  
}

# Calculate the Performance Metrics Looped ------------------------------

calc_perf_multithresh<-function(df, vec){
  
  
for (i in 1:l(vec)){
  
  cur_thresh<-vec[i]
  col_label<-paste0("ProbThresh_", cur_thresh)
  
  # Adjust predictions on threshold --------------------
  
  df<-df%>%mutate(response = ifelse( prob.1 >= cur_thresh, 1, -1)) # predictions adjusted for threshold 
  

  # Confusion Matrix --------------
  
  cur_conf<-conf_mat(df, cur_thresh) # confusion matrix adjusted for threshold 
  
  
  # Make list if i == 1
  
  if (i == 1){ list_mat<-list() }

  # Collect 
  
  list_mat[[i]] <-cur_conf
  names(list_mat)[i] <- col_label
  
# Performance Metrics -------------
  
  cur_perf_calc<-calc_perf(df, col_label )
  
  
  # Make list if i == 1
  if (i == 1){ build_perf<-cur_perf_calc }else{  
  # Collect 
  build_perf<-cbind(build_perf, cur_perf_calc) 
  }
  
}
  
  
  # Package to Close 
  out<-list( build_perf, list_mat) 
  names(out)<-c("Performance", "ConfusionMat")
  
  
  return(out)
  
  
  
  
  
}


# Collect the performance and confusion matrix looped per iteration on desired threshold ----------------------------

calc_perf_multiiter<-function(df, thresh){

          
        for(i in 1:max(df$iter)){
          
        # sanity check 
        if (l(u(df$iter)) != max(df$iter)){error("Number of iterations does not equal maximum iteration found")}
        
        # FIlter for iteration   
        curr_df<-df%>%filter(iter == i)
        
        temp<-calc_perf_multithresh(curr_df, thresh) # the desired threshold 
        
        
            
          # Build column name
          col_label <- paste0("iter", i, "_ProbThresh_", thresh)
        
          # Rename performance column
          colnames(temp$Performance)[1] <- col_label
        
          # Rename confusion matrix list entry
          names(temp$ConfusionMat)[1] <- col_label
        
          # Collect 
          if(i == 1){
            
            build_conf <- temp
          
            } else {
              
            # collect performance 
            build_conf$Performance <- cbind(
              build_conf$Performance,
              temp$Performance)
              
                
            # Collect Matrix 
            
            build_conf$ConfusionMat[[col_label]] <- temp$ConfusionMat[[1]]
                
                
        
        
        
          }

        }
  
  return(build_conf)
  }


# Check threshold associated with lowest probability of positive classification -----------

check_pos_thresh<-function(df){
    
    temp<-df%>% 
  filter(response == 1) %>%
  arrange(desc(prob.1)) %>%
  tail(1)

 print(paste0(" Threshold lowest prob for positive class is:", temp$prob.1))
        
      

      }


```

# Desired Pred Thresh 
```{r}

desired_prob_thresh<-0.50

```

 
# Data Prep ------------------------------

## Create Training Data with Selected Features

Will use first bootstrapped data set for training 

```{r, Create Training Data with Selected Features}

# Select top 500 features -----------------------------------------
    
# Use First dataframe in bootstrapped for training 
boot10_MA_100_multi_mat_INDEXONE<-MA_100_gene_exp_multi_classbal_list_train[[1]]

TV_known_training_stripped<-prep_mlr(boot10_MA_100_multi_mat_INDEXONE,
                                     boot_10_shared_feat , 
                                     "TV_state")



```



# CV ---------------------------------


### Define Task, Learner, hyperparameter search, crossvalidation strategy 
```{r, Define Task, Learner, hyperparameter search, crossvalidation strategy }

# Define task and learner -------------------------------------------------
#supervised 
    
    #Task
    geneTask<-makeClassifTask(data = TV_known_training_stripped, 
                              target="TV_state", 
                              positive = "1")                  # name of target variable 
    #learner 
    svm_gene<-makeLearner("classif.svm",                          # use SVM algorithm for classification
                           predict.type="prob", 
                          predict.threshold = desired_prob_thresh
                          )              
    
    

# Define hyper parameter search space -------------------------------------
    
# tuning the model 
    

    kernels_choice<-c("polynomial", "radial", "sigmoid")          
    
    svm_gene_ParamSpace<-makeParamSet(
                            makeDiscreteParam("kernel", values = kernels_choice),
                            makeIntegerParam("degree", lower = 1, upper = 3), # flexibility with hyper plane
                            makeNumericParam("cost", lower = 5, upper = 20),  # how much SVM should bend data to make smooth decision surface 
                            makeNumericParam("gamma", lower = 0, upper = 2) ) # distance of influence a training point has 
                            
    


# Define search procedure -------------------------------------------------
    #randomly select parameters to tune and identify optimal parameters for our SVM 
    
    #random sampling 
    randSearch_extended<-makeTuneControlRandom(maxit=60)         
    
    
    
# Define nested cross validation strategy ---------------------------------
                                                                  
    
      inner_cv<-makeResampleDesc("Holdout",                        
                                 split = 2/3,                      #inner cross validation loop is split 2/3, where 1/3 is reserved for validation
                                 stratify.cols = "TV_state", 
                                 predict = "both")                
                                                                  
                                                                  
      outer_cv<-makeResampleDesc("CV", iters = 10, 
                                 stratify.cols = "TV_state")                 #K fold cross validation 


```


### Define wrapper (learning SVM and tuning) 
```{r, Define wrapper (learning SVM and tuning) }
# Wrap together svm with tuning -------------------------------------------

    svm_gene_Wrapper<-makeTuneWrapper(
                            learner= svm_gene,
                            resampling = inner_cv,                
                            par.set=svm_gene_ParamSpace,               # hyperparameter search space 
                            control = randSearch_extended              
                              )
      
    

```

### Run CV with parameter tuning

The resample() fxn evaluates a learner (makeLearner()) on a given machine learning Task() using the selected resampling stretegy (makeResampleDesc())

```{r, Run CV with parameter tuning}
# Run CV with tuning and reccord tested params ----------------------------------------------------------
    svm_gene_cvWithTuning<-resample(
                              learner = svm_gene_Wrapper, 
                              task = geneTask,
                              resampling = outer_cv,               #outer 3 fold cross val defined 
                              models = TRUE, 
                              extract = getTuneResult,    
                              measures = list(mmce,fpr, fnr, tpr, tnr, mlr::auc, timetrain))    

```

## Method Validation Summary

```{r}


print("Optimal hyperparameters from all iterations: ") 
cv_hyperparam_fold_table<-getNestedTuneResultsX(svm_gene_cvWithTuning) 

cv_hyperparam_fold_table                             

cv_hyperparam_fold_list<-svm_gene_cvWithTuning$extract   

```

# CV Performance ---------------------------

svm_gene_cvWithTuning does not retain the threshold set in makeLearner(), not sure why but this is corrected in the next section, prior to the metrics calculations. 

## Adjust Threshold for Metrics 
```{r}

# Set threshold to adjust predictions 
svm_gene_cvWithTuning$pred <- setThreshold(svm_gene_cvWithTuning$pred, desired_prob_thresh) # KEYSTONE



```

svm_gene_cvWithTuning will now reflect prediction using the desired thresh as the threshold !!!!  


## Aggregate 

### *Sensitivity Point* - Calc Conf Matrix & Perf Met - Multi Thresh

```{r}
# Extract the Data -----------------------------

 all_call_CV<- as.data.frame(svm_gene_cvWithTuning$pred[["data"]])


# Execute --------------------------------


prob_thresh_vec<-c(seq(0, 1, by = 0.05))

cv_perf_confmat_allthresh<-calc_perf_multithresh(all_call_CV, prob_thresh_vec)


# Produced objects 
cv_perf_confmat_allthresh



```
### *Sensitivity Point* - Perf Across Prob Threshs

- On aggregated/ All training data

Plotting the performance metrics across difference probability thresholds to define the positive class. 

```{r}

### Elongate --------------------------------------

# Extract the performance measures 
cv_perf_mat_allthresh<-cv_perf_confmat_allthresh$Performance

# Pivot and Filter for desired metrics 
cv_perf_mat_allthresh$Metric<-rownames(cv_perf_mat_allthresh)
cv_perf_mat_allthresh<-cv_perf_mat_allthresh%>%select(Metric, everything())

desired_metrics<-c("Precision", "Accuracy", "Recall", "Specificity")

enter<-tidyr::pivot_longer(cv_perf_mat_allthresh,
               cols=  ProbThresh_0:ProbThresh_1, 
               names_to = "ProbThresh", 
               values_to="value")%>%
  
        mutate(ProbThresh = gsub("ProbThresh_", "", ProbThresh))%>%
        mutate(Metric = factor(Metric, 
                           levels = desired_metrics))%>% 
        filter(Metric %in% desired_metrics)%>%
        mutate(value = as.numeric(value))  


### Plot ----------------------------------------------
# Selections --------------------------

# Desired Thresholds for Prob Assessment 
selected_points<-seq(0,1, by = 0.1)

# Desired Performance Metrics to show 
select_metric<- c("Precision", 
                  #"Accuracy", 
                  "Recall" #, 
                  #"Specificity"
                  )

# colors 
gp_colors<- c( Precision= "#FFB000", 
               Accuracy = "#FE6100", 
               Recall =  "#785EF0", 
               Specificity = "#DC267F" )

# shapes 
gp_shapes <- c(
  Precision   = 21,
  Accuracy    = 22,
  Recall      = 23,
  Specificity = 24
)


# Plot CV Aggg -----------------------------

# Selected Performance Metrics 
plot_cv_agg_sensi<-enter%>%
        filter(Metric %in% all_of(select_metric), 
               ProbThresh %in% all_of(selected_points))  %>%
  ggplot(aes(x = ProbThresh, y = value, group = Metric, color = Metric, fill = Metric, shape=Metric)) +
  geom_line(size = 1) +                      
  geom_point( size = 3) +                     
  scale_color_manual(values = gp_colors) +      
  scale_fill_manual(values = gp_colors) +       
  scale_shape_manual(values = gp_shapes) + 
  scale_y_continuous(limits= c(0,1), breaks = c(0.00, 0.20 ,0.40 ,0.60, 0.80 ,1.00) ) +             
  ggtitle("Sensitivity Analysis on Prediction Threshold") +
  ylab("Performance")+
  xlab("Probability Threshold for Metabolism")+
    labs(caption = "CV aggregated all folds")+
  theme(
    legend.title = element_blank(),
    plot.title = element_text(hjust = 0.5, size = 16)
  )




# All Performance Metrics 
plot_cv_agg_sensi_all<-enter%>%
        filter( 
               ProbThresh %in% all_of(selected_points))  %>%
  ggplot(aes(x = ProbThresh, y = value, group = Metric, color = Metric, fill = Metric, shape=Metric)) +
  geom_line(size = 1) +                      
  geom_point( size = 3) +    
  scale_color_manual(values = gp_colors) +      
  scale_fill_manual(values = gp_colors) +       
  scale_shape_manual(values = gp_shapes) + 
  scale_y_continuous(limits= c(0,1), breaks = c(0.00, 0.20 ,0.40 ,0.60, 0.80 ,1.00) ) +             
  ggtitle("Sensitivity Analysis on Prediction Threshold") +
  ylab("Performance")+
  xlab("Probability Threshold for Metabolism")+
  labs(caption = "CV aggregated all folds")+
  theme(
    legend.title = element_blank(),
    plot.title = element_text(hjust = 0.5, size = 16)
  )


```

### *Sensitivity Point* - Extract Threshold based on F1 and Neg Pred. Value 


```{r}

temp<-base::t(cv_perf_confmat_allthresh$Performance)%>%
  as.data.frame(.)%>%
  dplyr::select("F1", "Recall", "Neg Pred Value", "Specificity", "fnr", "Balanced Accuracy", "Kappa")



 # Highest Meta Threshold ---------------------------------------------

# Select Highest F1 value and associated threshold 

{ 
  
F1_high<-sort(u(temp$F1), decreasing=TRUE)[1]

# Start Group Code Block 
temp2<-temp%>%
  dplyr::filter(F1 == F1_high)

# If one threshold with highest F1 choose that threshold 
if(nrow(temp2)==1){
  
  thresh_sensi_top<-rownames(temp2)%>%sub(".*_", "", .)%>%as.numeric(.)
  
}else{
  
# If multiple thresholds with highest F1, Tie breaker is Highest Recall 
  
  # Collect highest recall 
  Recall_high<-sort(u(temp2$Recall), decreasing=TRUE)[1]

  #Filter for highest recall 
  temp3<-temp2%>%dplyr::filter(Recall == Recall_high)
    
# If Only only thresh with highest recall select it   
  if(nrow(temp3) ==1){
    
  thresh_sensi_top<-rownames(temp3)%>%sub(".*_", "", .)%>%as.numeric(.)

  
  }else{
    
    # pull the lowest threshold if ties between two perf metrics 
    thresh_sensi_top<-rownames(temp3)%>%
        sub(".*_", "", .)%>%
        as.numeric(.)%>%
        sort(., decreasing=FALSE)%>%
        .[1]%>%as.numeric(.)
    
    print("Tie Breaker enacted for Metabolizing Threshold")
  } 
  
  
} # end of nested if statements 
} # end of Grouped code block 



 # Bottom Nonmeta Threshold ---------------------------------------------


{
  
NPV_high<-sort(u(temp$`Neg Pred Value`), decreasing=TRUE)[1]  # Start Group Code Block 

temp2<-temp%>%
  dplyr::filter(`Neg Pred Value` == NPV_high)

# If one threshold with highest F1 choose that threshold 
if(nrow(temp2)==1){
  
  thresh_sensi_bot<-rownames(temp2)%>%sub(".*_", "", .)%>%as.numeric(.)

  
}else{
  
# If multiple thresholds with highest F1, Tie breaker is Highest Recall 
  
  # Collect highest recall 
 Spec_high<-sort(u(temp2$Specificity), decreasing=TRUE)[1]

  
  
  #Filter for highest recall 
  temp3<-temp2%>%dplyr::filter(Specificity == Spec_high)
    
# If Only only thresh with highest recall select it   
  if(nrow(temp3) ==1){
    
  thresh_sensi_bot<-rownames(temp3)%>%sub(".*_", "", .)%>%as.numeric(.)

  
  
  }else{
    
    # pull the highest threshold if ties between two perf metrics 
    thresh_sensi_bot<-rownames(temp3)%>%
        sub(".*_", "", .)%>%
        as.numeric(.)%>%
        sort(., decreasing=TRUE)%>%
        .[1]%>%as.numeric(.)
    
    print("Tie Breaker enacted for Nonmetabolizing Threshold")
  
  } 
  
  
} # end of nested if statements 
} # end of Grouped code block 




# Printed Summary 

print(paste0("Sensitivity Analysis on Classification threshold found top Meta. thresh: ", thresh_sensi_top))
print(paste0("Sensitivity Analysis on Classification threshold found botton non Meta. thresh: ", thresh_sensi_bot))
```

### Extract Perf. and ConfMat on Desired Thresh 

Choose matrix with prob threshold defined at the start labeled as desired_prob_thresh

```{r}

# name of Col with desired threshold
namedcol<-paste0("ProbThresh_", desired_prob_thresh)

# Performance from Aggregated Folds with desired threshold
cv_perf_agg<-cv_perf_confmat_allthresh$Performance%>%select(all_of(namedcol))

# Confusion Matrix from Aggregated Folds with desired Threshold 

cv_confmat_agg<- cv_perf_confmat_allthresh$ConfusionMat[[namedcol]]

# Obtained Objects 
print(paste0("Aggregated Crossvalidation Performance (Threshold of ", desired_prob_thresh, ")"))

cv_perf_agg

print(paste0("Aggregated Crossvalidation Confusion Matrix (Threshold of ", desired_prob_thresh, ")"))

cv_confmat_agg
```




### Performance curves

```{r}

# Collect Number of Cases per State for Plot 

n_pos_cv<-sum(TV_known_training_stripped$TV_state == 1 )
n_neg_cv<-sum(TV_known_training_stripped$TV_state == -1 )


samplecount_cv<-paste0("n: (+1) ", n_pos_cv,", (-1) ", n_neg_cv)


# Performance Curves - Aggregated ----------------------------------

thresh_vs_perf_agg<-generateThreshVsPerfData(obj = svm_gene_cvWithTuning$pred, # Already modified for desired threshold 
                                             measures = list(mmce,fpr, fnr, tpr, tnr, ppv),
                                             gridsize = 100L,
                                             aggregate = TRUE # plot performance of all iterations aggregated
                                             )

# False Negative Rate vs True Negative Rate 

ft_neg_agg_cv<-plotROCCurves(obj = thresh_vs_perf_agg,
              measures = list(fnr, tnr) )+    
              ggtitle(paste0("False Negative Rate vs True Negative Rate, CV Performance, ",samplecount_cv)) +
              theme(plot.title = element_text(size = 10))

# ROC - Sensitivity and Specificity curve 

ft_pos_agg_cv<-plotROCCurves(obj = thresh_vs_perf_agg,
              measures = list(fpr, tpr) )+    
               ggtitle(paste0("ROC - Sensitivity-Specifificty Curve, CV Performance, ",samplecount_cv))+
                 theme(plot.title = element_text(size = 10))
# Precision/Recall

prec_recall_agg_cv<-plotROCCurves(thresh_vs_perf_agg, measures = list(tpr, ppv), diagonal = FALSE)+    
                    ggtitle(paste0("Precision-Recall Curve, CV Performance, ",samplecount_cv))+
                    theme(plot.title = element_text(size = 10))


```

## Per Iteration
### Sanity Check 
```{r}

  temp<-all_call_CV%>% 
  filter(response == 1) %>%
  arrange(desc(prob.1)) %>%
  tail(1)
  
print(paste0("No Threshold Adjustment, lowest prob for positive class is:", temp$prob.1))
        
```

### Generate Per iteration conf mat at desired thresh 

Using Desired threshold calculate the performance per iteration 

```{r}

# Per iteration Confusion Matrix -------------

cv_iter_result_desirethresh<-calc_perf_multiiter(all_call_CV, desired_prob_thresh)

cv_iter_result_desirethresh

```



### Extract Perf. and ConfMat on Desired Thresh  

Choose matrix with prob threshold defined at the start labeled as desired_prob_thresh

```{r}

# name of Col with desired threshold
namedcol<-paste0("ProbThresh_", desired_prob_thresh)

# Performance per iteration with desired threshold
cv_perf_per_iter<-cv_iter_result_desirethresh$Performance

# Confusion Matrix fper iteration with desired Threshold 
cv_confmat_per_iter<- cv_iter_result_desirethresh$ConfusionMat


# Obtained Objects 
print(paste0("Per iteration Performance (Threshold of ", desired_prob_thresh, ")"))

cv_perf_per_iter

print(paste0("Per iteration Confusion Matrix (Threshold of ", desired_prob_thresh, ")"))

cv_confmat_per_iter

```



### Performance curves
```{r}


# ROC curve from predictions - Per iteration ----------------------------------

thresh_vs_perf<-generateThreshVsPerfData( obj = svm_gene_cvWithTuning$pred, 
                                              measures = list(mmce,fpr, fnr, tpr, tnr, ppv), 
                                              gridsize = 100L, 
                                              aggregate = FALSE # plot performance of individual iterations 
                                          )

# False Negative Rate vs True Negative Rate 


ft_neg_cv<-plotROCCurves(obj = thresh_vs_perf,
                          measures = list(fnr, tnr) )+    
  ggtitle(paste0("False Negative Rate vs True Negative Rate, CV Performance, ",samplecount_cv) )+
  theme(plot.title = element_text(size = 10))



# ROC - Sensitivity and Specificity 

ft_pos_cv<-plotROCCurves(obj = thresh_vs_perf,
                          measures = list(fpr, tpr) )+    
  ggtitle(paste0("ROC - Sensitivity-Specifificty Curve, Trained on:\n, CV Performance, ", samplecount_cv) )+
  theme(plot.title = element_text(size = 10))


# Precision/Recall

prec_recall_cv<-plotROCCurves(thresh_vs_perf, measures = list(tpr, ppv), diagonal = FALSE)+    
                    ggtitle(paste0("Precision-Recall Curve, Trained on:\n, CV Performance, ", samplecount_cv) )+
                    theme(plot.title = element_text(size = 10))

# Plot - Performance vs Threshold

ThreshvsPerf_plots_iter_cv<-plotThreshVsPerf(thresh_vs_perf)


```

## Results Agg and Iter Plots
```{r}

# Aggregated ---------

# Sensitivity Analysis - Performance across multiple thresholds 
plot_cv_agg_sensi

plot_cv_agg_sensi_all


# Aggregated performance plots (on desired thresh)
ft_neg_agg_cv

ft_pos_agg_cv

prec_recall_agg_cv


# Per Iteration ---------

# Aggregated performance plots (on desired thresh)

ft_neg_cv

ft_pos_cv

prec_recall_cv

ThreshvsPerf_plots_iter_cv

```

## Results Summary
```{r}

print(paste0("Sensivity point performance across multi thresholds on aggregated training data"))

cv_perf_confmat_allthresh$Performance


print(paste0("Confusion Matrix across multi thresholds on aggregated training data"))

cv_perf_confmat_allthresh$ConfusionMat

```

```{r}


# Obtained Objects 
print(paste0("Aggregated Crossvalidation Performance (Threshold of ", desired_prob_thresh, ")"))

cv_perf_agg

print(paste0("Aggregated Crossvalidation Confusion Matrix (Threshold of ", desired_prob_thresh, ")"))

cv_confmat_agg


```

```{r}


# Obtained Objects 
print(paste0("Per iteration Performance (Threshold of ", desired_prob_thresh, ")"))

cv_perf_per_iter

print(paste0("Per iteration Confusion Matrix (Threshold of ", desired_prob_thresh, ")"))

cv_confmat_per_iter
```





# Model Training ------------------------------



## Train Model
```{r, Train Model}
# Train model on  data -------------------------------------------------

tunedSvmPars_gene<-tuneParams(learner= svm_gene,                   # to get best performing set of parameters 
                              task= geneTask,
                              resampling = inner_cv,
                              par.set=svm_gene_ParamSpace,
                              control = randSearch_extended
                                )
 print("Determined Hyperparameters for Model Training: " ) # list of determined hyperparameters
tunedSvmPars_gene$x

  
# Apply the hyperparameters       
tunedSvm_gene<-setHyperPars(svm_gene, 
                            par.vals = tunedSvmPars_gene$x)   

# THE TRAINED MODEL
tunedSvmModel_gene<-mlr::train(tunedSvm_gene, geneTask) # KEYSTONE 


# The Trained Model Performance Metrics
    
as.data.frame(tunedSvmPars_gene$opt.path)

```

## Results 
```{r, Results}

# Hyperparameters
print( paste0("Determined Hyperparameters for Model Training: ") ) # 
print(tunedSvmPars_gene$x)


# Model 
print( paste0("Trained Model: " ) ) # 
model_overview<-capture.output({tunedSvmModel_gene})
print(model_overview)


```

# Learning Curves ----------------------
## Define Model and Learner 
```{r}
# Used and defined in the CV ------------------ 

# Define outer CV for Learning Curve 
    
          outer_cv_lc <- makeResampleDesc("CV", iters = 10, 
                                              stratify.cols = "TV_state", predict = "both")
# Learner
    
          svm_learner_opthyper<-makeLearner("classif.svm",                         
                                              predict.type="prob", 
                                            predict.threshold = desired_prob_thresh, 
                                              par.vals = tunedSvmPars_gene$x)   # OPTIMAL HYPERPARAMTERS for model training                
 
          
```

## Generate 

```{r}

                                            
# Performance metrics Aggregated 
    
    # ACCURACY DF -----------------------------------------------

acc_agg<- generateLearningCurveData(
                            learners = svm_learner_opthyper,  
                            task = geneTask,
                            percs = seq(0.1, 1, by = 0.1), # 
                            measures = list(acc, setAggregation(acc, train.mean)),
                            
                            resampling = outer_cv_lc,
                            show.info = FALSE)




    # MEAN MISCLASSIFICATION DF -----------------------------------------------


mmce_agg<- generateLearningCurveData(
                            learners = svm_learner_opthyper, 
                            task = geneTask,
                            percs = seq(0.1, 1, by = 0.1), # 
                            measures = list(mmce, setAggregation(mmce, train.mean)),
                            
                            resampling = outer_cv_lc,
                            show.info = FALSE)


    # FALSE POSITTIVE RATE DF -----------------------------------------------


fpr_agg<- generateLearningCurveData(
                            learners = svm_learner_opthyper, 
                            task = geneTask,
                            percs = seq(0.1, 1, by = 0.1), # 
                            measures = list(fpr, setAggregation(fpr, train.mean)),
                            
                            resampling = outer_cv_lc,
                            show.info = FALSE)


    # TRUE POSITTIVE RATE DF -----------------------------------------------


tpr_agg<- generateLearningCurveData(
                            learners = svm_learner_opthyper, 
                            task = geneTask,
                            percs = seq(0.1, 1, by = 0.1), # 
                            measures = list(tpr, setAggregation(tpr, train.mean)),
                            
                            resampling = outer_cv_lc,
                            show.info = FALSE)


    # False negative RATE DF -----------------------------------------------


fnr_agg<- generateLearningCurveData(
                            learners = svm_learner_opthyper, 
                            task = geneTask,
                            percs = seq(0.1, 1, by = 0.1), # 
                            measures = list(fnr, setAggregation(fnr, train.mean)),
                            
                            resampling = outer_cv_lc,
                            show.info = FALSE)




    # True negative RATE DF -----------------------------------------------


tnr_agg<- generateLearningCurveData(
                            learners = svm_learner_opthyper, 
                            task = geneTask,
                            percs = seq(0.1, 1, by = 0.1), #
                            measures = list(tnr, setAggregation(tnr, train.mean)),
                            
                            resampling = outer_cv_lc,
                            show.info = FALSE)

tnr_agg



```

## Graphs
```{r}
acc_agg_plot_withlegend<-plotLearningCurve(acc_agg, 
                  facet = "learner"  
                  ) 

mmce_agg_plot_withlegend<-plotLearningCurve(mmce_agg, 
                  facet = "learner"  
                  ) 


acc_agg_plot<-plotLearningCurve(acc_agg, 
                  facet = "learner"  
                  ) + theme(legend.position = "none")

mmce_agg_plot<-plotLearningCurve(mmce_agg, 
                  facet = "learner"  
                  ) + theme(legend.position = "none")

tpr_agg_plot<-plotLearningCurve(tpr_agg, 
                  facet = "learner"  
                  ) + theme(legend.position = "none")

fpr_agg_plot<-plotLearningCurve(fpr_agg, 
                  facet = "learner"  
                  ) + theme(legend.position = "none")

tnr_agg_plot<-plotLearningCurve(tnr_agg, 
                  facet = "learner"  
                  ) + theme(legend.position = "none")

fnr_agg_plot<-plotLearningCurve(fnr_agg, 
                  facet = "learner"  
                  ) + theme(legend.position = "none")




```

## Replot 
```{r}


# Function to apply consistent labels and limits
standardize_plot <- function(plot_obj) {
    
  # Convert to long format
  df <- plot_obj$data%>%
    select(-learner)
  
  leadcol<-names(df)[2] # Measure name
  endcol<-names(df)[3] # Performance value 

  
   long<-df %>%
          rename(Performance=performance, 
                 Group=measure
                 )
          
  # Define consistent axis labels
  x_label <- "Percentage of Training Data"
  y_label <- "Performance"
  
  # Define consistent y-axis range
  y_limits <- c(0, 1)  
  x_limits<- c(0,1)

  out<-ggplot(long, aes( x= percentage, y= Performance, color = Group))+
    geom_line(size=1)+
    geom_point(size=2)+ 
    theme_minimal() + theme(legend.position = "none")+
    labs(x = x_label, y = y_label) +
    coord_cartesian(ylim = y_limits, xlim = x_limits) 
}

# Apply
acc_agg_plot <- standardize_plot(acc_agg_plot)
mmce_agg_plot <- standardize_plot(mmce_agg_plot)
tpr_agg_plot <- standardize_plot(tpr_agg_plot)
fpr_agg_plot <- standardize_plot(fpr_agg_plot)
tnr_agg_plot <- standardize_plot(tnr_agg_plot)
fnr_agg_plot <- standardize_plot(fnr_agg_plot)


```


# Test Model -----------------------------------

 ## Prep Training Data 
```{r}

# Use First dataframe in bootstrapped for training 
drugstate_known_test<-MA_100_gene_exp_multi_list_test[[1]] 

# Select features and strip
TV_known_test_stripped<-prep_mlr(drugstate_known_test, boot_10_shared_feat, "TV_state" )
  
  
    
```


# Execute Test 
```{r}

testoutput <-predict(tunedSvmModel_gene, newdata = TV_known_test_stripped) 


check_pos_thresh(testoutput$data)

```


# Test Performance ------------------------------------------

### *Sensitivity Point* - Calc Conf Matrix & Perf Met - Multi Thresh

```{r}
# Extract the Data -----------------------------

 all_call_test<- as.data.frame(testoutput$data)


# Execute --------------------------------


prob_thresh_vec<-c(seq(0, 1, by = 0.05))

test_perf_confmat_allthresh<-calc_perf_multithresh(all_call_test, prob_thresh_vec)



```
### *Sensitivity Point* - Perf Across Prob Threshs

- On aggregated/ all training data

Plotting the performance metrics across difference probability thresholds to define the positive class. 

```{r}

### Elongate --------------------------------------

# Extract the performance measures 
test_perf_mat_allthresh<-test_perf_confmat_allthresh$Performance

# Pivot and Filter for desired metrics 
test_perf_mat_allthresh$Metric<-rownames(test_perf_mat_allthresh)
test_perf_mat_allthresh<-test_perf_mat_allthresh%>%select(Metric, everything())

desired_metrics<-c("Precision", "Accuracy", "Recall", "Specificity")

enter<-tidyr::pivot_longer(test_perf_mat_allthresh,
               cols=  ProbThresh_0:ProbThresh_1, 
               names_to = "ProbThresh", 
               values_to="value")%>%
  
        mutate(ProbThresh = gsub("ProbThresh_", "", ProbThresh))%>%
        mutate(Metric = factor(Metric, 
                           levels = desired_metrics))%>% 
        filter(Metric %in% desired_metrics)%>%
        mutate(value = as.numeric(value))   


### Plot ----------------------------------------------
# Selections --------------------------

# Desired Thresholds for Prob Assessment 
selected_points<-seq(0,1, by = 0.1)

# Desired Performance Metrics to show 
select_metric<- c("Precision", 
                  #"Accuracy", 
                  "Recall" #, 
                  #"Specificity"
                  )

# colors 
gp_colors<- c( Precision= "#FFB000", 
               Accuracy = "#FE6100", 
               Recall =  "#785EF0", 
               Specificity = "#DC267F" )

# shapes 
gp_shapes <- c(
  Precision   = 21,
  Accuracy    = 22,
  Recall      = 23,
  Specificity = 24
)


# Plot CV Aggg -----------------------------

# Selected Performance Metrics 
plot_test_sensi<-enter%>%
        filter(Metric %in% all_of(select_metric), 
               ProbThresh %in% all_of(selected_points))  %>%
  ggplot(aes(x = ProbThresh, y = value, group = Metric, color = Metric, fill = Metric, shape=Metric)) +
  geom_line(size = 1) +                    
  geom_point( size = 3) +    
  scale_color_manual(values = gp_colors) +    
  scale_fill_manual(values = gp_colors) +       
  scale_shape_manual(values = gp_shapes) + 
  scale_y_continuous(limits= c(0,1), breaks = c(0.00, 0.20 ,0.40 ,0.60, 0.80 ,1.00) ) +             
  ggtitle("Sensitivity Analysis on Prediction Threshold") +
  ylab("Performance")+
  xlab("Probability Threshold for Metabolism")+
    labs(caption = "Test data")+
  theme(
    legend.title = element_blank(),
    plot.title = element_text(hjust = 0.5, size = 16)
  )




# All Performance Metrics 
plot_test_sensi_all<-enter%>%
        filter( 
               ProbThresh %in% all_of(selected_points))  %>%
  ggplot(aes(x = ProbThresh, y = value, group = Metric, color = Metric, fill = Metric, shape=Metric)) +
  geom_line(size = 1) +                      
  geom_point( size = 3) +  
  scale_color_manual(values = gp_colors) +      
  scale_fill_manual(values = gp_colors) +     
  scale_shape_manual(values = gp_shapes) + 
  scale_y_continuous(limits= c(0,1), breaks = c(0.00, 0.20 ,0.40 ,0.60, 0.80 ,1.00) ) +             
  ggtitle("Sensitivity Analysis on Prediction Threshold") +
  ylab("Performance")+
  xlab("Probability Threshold for Metabolism")+
  labs(caption = "Test Data")+
  theme(
    legend.title = element_blank(),
    plot.title = element_text(hjust = 0.5, size = 16)
  )



```


### Extract Perf. and ConfMat on Desired Thresh  

Choose matrix with prob threshold defined at the start labeled as desired_prob_thresh

```{r}

# name of Col with desired threshold
namedcol<-paste0("ProbThresh_", desired_prob_thresh)

# Performance from  with desired threshold
test_perf<-test_perf_confmat_allthresh$Performance%>%select(all_of(namedcol))

# Confusion Matrix from with desired Threshold 
test_confmat<- test_perf_confmat_allthresh$ConfusionMat[[namedcol]]






# Obtained Objects 
print(paste0("Test Performance (Threshold of ", desired_prob_thresh, ")"))

test_perf

print(paste0("Test Confusion Matrix (Threshold of ", desired_prob_thresh, ")"))

test_confmat



```





## MLR Plot method

```{r}


# Collect --------------------------------------------------------


n_pos_test<-sum(TV_known_test_stripped$TV_state == 1 )
n_neg_test<-sum(TV_known_test_stripped$TV_state == -1 )


samplecount_test<-paste0("n: (+1) ", n_pos_test,", (-1) ", n_neg_test)



# Performance Curves - Aggregated ----------------------------------


thresh_vs_perf_test<-generateThreshVsPerfData(obj = testoutput,
                                             measures = list(mlr::mmce, mlr::acc, mlr::fpr, mlr::fnr, mlr::tpr, mlr::tnr, mlr::auc, mlr::ppv),
                                             gridsize = 100L,
                                             aggregate = TRUE # plot performance of all iterations aggregated
                                             )

# Plot -------------------------------------------------------------


# False Negative Rate vs True Negative Rate 

ft_neg_test<-plotROCCurves(obj = thresh_vs_perf_test,
              measures = list(fnr, tnr) )+    
              ggtitle(paste0("False Negative Rate vs True Negative Rate, Test Performance, ", samplecount_test))+
              theme(plot.title = element_text(size = 10))

# ROC - Sensitivity and Specificity curve 

ft_pos_test<-plotROCCurves(obj = thresh_vs_perf_test,
              measures = list(fpr, tpr) )+    
               ggtitle(paste0("ROC - Sensitivity-Specifificty Curve, Test Performance, ", samplecount_test))+
                 theme(plot.title = element_text(size = 10))
# Precision/Recall

prec_recall_test<-plotROCCurves(thresh_vs_perf_test, measures = list(tpr, ppv), diagonal = FALSE)+    
                    ggtitle(paste0("Precision-Recall Curve, Test Performance, ", samplecount_test))+
                    theme(plot.title = element_text(size = 10))


# Plots - Perf vs thresh --------------
ThreshvsPerf_plots_test<-plotThreshVsPerf(thresh_vs_perf_test)



```


## Results PLots 
```{r}

# sensitivity 

plot_test_sensi
plot_test_sensi_all


# plots 
ft_neg_test
ft_pos_test


prec_recall_test
ThreshvsPerf_plots_test

```

## Results Summary 
```{r}
    
print(paste0("Sensivity point performance across multi thresholds on aggregated training data"))

test_perf_confmat_allthresh$Performance


print(paste0("Confusion Matrix across multi thresholds on aggregated training data"))

test_perf_confmat_allthresh$ConfusionMat



# Obtained Objects 
print(paste0("Test Performance (Threshold of ", desired_prob_thresh, ")"))

test_perf

print(paste0("Test Confusion Matrix (Threshold of ", desired_prob_thresh, ")"))

test_confmat


```

# Joint Summary 
```{r}


temp<-test_perf
colnames(temp)[1]<-paste0("Test_", colnames(test_perf)[1])


temp2<-cv_perf_agg
colnames(temp2)[1]<-paste0("CV_agg_", colnames(cv_perf_agg)[1])


temp3<-test_confmat
colnames(temp3)[3]<-paste0("Test_", colnames(test_perf)[1])

temp4<-cv_confmat_agg
colnames(temp4)[3]<-paste0("CV_agg_", colnames(cv_perf_agg)[1])



# Merge test and training performance metrics and desired threshold 
performance_summary_desiredthresh<-cbind(temp, temp2)


# Merge test and training performance metrics and desired threshold 
confmat_summary_desiredthresh<-full_join(temp3, temp4)




```


# CLOSE -------------------------------
# Save Object Sizes ***Specify Objects*** 
```{r, Save Object Sizes ***Specify Objects***}

# Note- rather than saving all created objects I will specify the three dataframes we need for the next code section. 


objects_created <- c( "tunedSvmPars_gene", 
                               "tunedSvmModel_gene", 
                               "svm_gene_cvWithTuning", 
                               "thresh_sensi_top", # Based on F1 and/or Recall From Class. Seni. Analysis 
                               "thresh_sensi_bot")# Based on Negative Predictive Value and/or Specificity from Class seni analysis 


reccord_dim <- function(objects) {
  
  result <- list()
  
  for (obj_name in objects) {
    
    if (exists(obj_name)) {
      
      obj <- get(obj_name)
      
      if (is.data.frame(obj) || is.matrix(obj)) {
        
        rows <- nrow(obj)
        cols <- ncol(obj)
        result[[obj_name]] <- list(rows = rows, cols = cols)
        
      } else {
        
        warning(paste("Object labeled ", obj_name, "is not a data frame or a matrix. Skipping."))
      }
      
    } else {
      
      warning(paste("Object", obj_name, "does not exist. Skipping."))
      
    }
  }
  return(result)
}

objects_dim_list<-reccord_dim(objects_created)




#          Summary --------------------------------------------- 

print("Created Objects Summary:")
print(objects_dim_list)


```





### Exporting and Clean Up - Part 1/2
```{r, Exporting and Clean Up - Part 1/2}
#           Create Output File ------------------------------------------------------


current_output_folder<-paste0(script_name_base, "_", run_timestamp, ".Rmd")

dir.create(current_output_folder)

script_path_with_output_folder <- file.path(script_path_folder, 
                                            current_output_folder)

setwd(script_path_with_output_folder) # need to restate for each code chunk

#           Export Executed Code ----------------------------------------------------

copy_and_output_code <- function(script_path) {
  if (file.exists(script_path)) {
    
    rstudioapi::documentSave()
    
    script_content <- readLines(script_path)
    
    writeLines(script_content, current_output_folder)
  } else {
    message("Error: The specified script path does not exist.")
  }
}

# Call the function to copy and export the code
copy_and_output_code(script_path_current)

#           Export Run Info ---------------------------------------------------------

writeLines(capture.output(run_sessionInfo), "sessionInfo.txt")

```

### Exporting and Clean Up - Part 2/2 **Specify Objects**
```{r, Exporting and Clean Up - Part 2/2 **Specify Objects**}

setwd(script_path_with_output_folder) # need to restate for each code chunk

#           Export Objects as .rda - **SPECIFY OBJECTS**----------------------------------------------------

objects_save<-c( objects_created, "objects_dim_list")

                            
save(list=objects_save,                   
     file = "env_obj.rda")
 

#           Export Tables/Genes Individually- **SPECIFY OBJECTS** ----------------------------------------

write_lines(tunedSvmPars_gene, "tunedSvmPars_gene.txt" )
write_lines(tunedSvmModel_gene, "tunedSvmModel_gene.txt")


# Sensitivity Analysis 

sensi_plot_names<-c("plot_cv_agg_sensi", 
                    "plot_cv_agg_sensi_all",
                    "plot_test_sensi",
                    "plot_test_sensi_all")

        dir.create("Results_Sensitivity", recursive = TRUE, showWarnings = FALSE)
        
        for (nm in sensi_plot_names) {
          ggsave(
            filename = file.path("Results_Sensitivity", paste0(nm, ".pdf")),
            plot = get(nm)
          )
        }

# CV Performance Curves
        
       cv_plot_names <- c( # Aggregated performance plots (on desired thresh)

                          "ft_neg_agg_cv",
                          "ft_pos_agg_cv",
                          "prec_recall_agg_cv",
                          
                          # Per Iteration performance plots (on desired thresh)
                          "ft_neg_cv",
                          "ft_pos_cv",
                          "prec_recall_cv"
                        )

        dir.create("Results_CV/Plots", recursive = TRUE, showWarnings = FALSE)
        
            
        ggsave(
            filename = file.path("Results_CV/Plots", "ThreshvsPerf_plots_iter_cv.pdf"),
            plot = ThreshvsPerf_plots_iter_cv, units = "in", width = 10, height = 8
          )
            
        for (nm in cv_plot_names) {
          ggsave(
            filename = file.path("Results_CV/Plots", paste0(nm, ".pdf")),
            plot = get(nm)
          )
        }

# Testing Performance Curves
        
                        
      test_plot_names<-c(
                        "ft_neg_test",
                        "ft_pos_test",
                        
                        
                        "prec_recall_test")

          dir.create("Results_Test/Plots", showWarnings = FALSE, recursive = TRUE)
        
            
        ggsave(
            filename = file.path("Results_Test/Plots", "ThreshvsPerf_plots_test.pdf"),
            plot = ThreshvsPerf_plots_test, units = "in", width = 10, height = 8
          )
        
        
        for (nm in test_plot_names) {
          ggsave(
            filename = file.path("Results_Test/Plots", paste0(nm, ".pdf")),
            plot = get(nm)
          )
        }
          
      

# Learning Curves
          
    learn_plot_names <- c("acc_agg_plot_withlegend", "mmce_agg_plot_withlegend",
                              "acc_agg_plot",
                              "mmce_agg_plot",
                              "tpr_agg_plot",
                              "fpr_agg_plot",
                              "tnr_agg_plot",
                              "fnr_agg_plot"
                            )

          dir.create("Results_Learning", showWarnings = FALSE, recursive = TRUE)
          
                  for (nm in learn_plot_names) {
                    ggsave(
                      filename = file.path("Results_Learning", paste0(nm, ".pdf")),
                      plot = get(nm), units = "in", width =3, height = 3
                    )
                  }

    
# Export CSV
  

      
# Sensitivity Performance 
write.csv(cv_perf_confmat_allthresh$Performance, 
          file = file.path("Results_Sensitivity","cv_perf_confmat_allthresh_Performance.csv"), 
          row.names = TRUE)

write.csv(cv_perf_confmat_allthresh$ConfusionMat, 
          file = file.path("Results_Sensitivity","cv_perf_confmat_allthresh_ConfusionMat.csv"), 
          row.names = TRUE)


write.csv(test_perf_confmat_allthresh$Performance, 
          file = file.path("Results_Sensitivity", "test_perf_confmat_allthresh_Performance.csv"), 
          row.names = TRUE)

write.csv(test_perf_confmat_allthresh$ConfusionMat, 
          file = file.path("Results_Sensitivity","test_perf_confmat_allthresh_ConfusionMat.csv"), 
          row.names = TRUE)





# CV Performance Aggregated
write.csv(cv_perf_agg, 
          file = file.path("Results_CV", "cv_perf_agg.csv"),
          row.names = TRUE)
    
write.csv(cv_confmat_agg, 
          file = file.path("Results_CV", "cv_confmat_agg.csv"),
          row.names = TRUE)
    

# CV Performance Per Iteration
write.csv(cv_perf_per_iter, 
          file = file.path("Results_CV", "cv_perf_per_iter.csv"),
          row.names = TRUE)
    
write.csv(cv_confmat_per_iter, 
          file = file.path("Results_CV", "cv_confmat_per_iter.csv"),
          row.names = TRUE)
    


# Test Performance

write.csv(test_perf, 
          file = file.path("Results_Test", "test_perf.csv"), 
          row.names = TRUE)  

write.csv(test_confmat, 
          file = file.path("Results_Test", "test_confmat.csv"), 
          row.names = TRUE)    




# Joint SUmmary 

write.csv(performance_summary_desiredthresh, 
          file = "performance_summary_desiredthresh.csv", 
          row.names = TRUE)    

write.csv(confmat_summary_desiredthresh, 
          file =  "confmat_summary_desiredthresh.csv", 
          row.names = TRUE)    


# Read CSV files in folder
CSV_Files <- list.files(path = script_path_with_output_folder, pattern = ".csv$")

# Zip the files
zip::zip(zipfile = "exported_objects.zip", files = CSV_Files)

#Remove CSV files
file.remove(CSV_Files)


 
```


### Clear Env./Re-Add Generated Objects

```{r, Clear Env./Re-Add Generated Objects}
setwd(script_path_with_output_folder) # need to restate for each code chunk

#           Clear Environment/Re-Add Generated Objects  ------------------------------------------------------


#clear environment
rm(list = ls()) #USE VERY CAREFULLY ONLY ACTIVATE AT END OF PIPELINE


  ## END ---------------------------------------------------------------------


```


