---
title: "lincs_multi"
author: "Dali_Nemecio"
date: "`r Sys.Date()`"
output: 
  html_document:
    code_folding: hide
---

Multiply the LINCS CD by the microbe-transcriptomics correlations. The data is then partitioned into testing/training based on the drug identity and are class balanced. Drugs that are Zimmerman restricted (and passed the microbe proportion check) are used for testing and training, all other drugs will be predicted on. 

Cannot execute with slurm script need to run in interactive session.  

Note that the host omic corr matrix (tranx vs mic) contains microbes with NAs across all genes, those are dropped. A summary output states the identities of these microbes. Since they are dropped they cannot be predicted on as their correlation is NA. 

## Start ---------------------------------------------------------------------
# SET UP MAC ---------------------------------------------------------------------
## Library 
```{r, eval=TRUE}
packages_needed <- c("rsample",  
                   "rstudioapi", 
                   "tidyverse")

for (pkg in packages_needed){
  if ( !require(pkg, character.only = TRUE)){
    library(pkg, character.only = TRUE)
  } 
}

```

## Script Info and Dir
```{r, eval=TRUE}

# Script Directory
script_path_current <- getSourceEditorContext()$path
script_path_folder <- sub("/[^/]*$", "", script_path_current)
script_name <- sub(".*/", "", script_path_current)
script_name_base <- sub("\\..*$", "", script_name)

# Change directory in all code chunks to current script location
knitr::opts_knit$set(root.dir = script_path_folder)

# Collect Run Info
run_timestamp <- format(Sys.time(), "%Y_%m_%d_%H%M")

run_sessionInfo <- sessionInfo()

```

## Shortcuts
```{r, eval=TRUE}
source("/Users/dalinemecio/Documents/1_Rotations/Brubaker/R/x_smaller_folders/short_cuts/short_cuts.R")
```

## Load Data and Objects Required 
### Data Prev Folder 
```{r, eval=TRUE}
# Load Data - Collect .rda files ----------------------------------------

# Find Previous Code Folder -----------------------------

# Find the last slash
last_slash <- max(gregexpr("/", script_path_folder)[[1]])

# Extract the substring
substring_after_last_slash <- substr(script_path_folder, last_slash + 1, nchar(script_path_folder))

# Extract the first number
first_number <- regmatches(substring_after_last_slash, regexpr("[0-9]+", substring_after_last_slash))

# Convert the first number to an integer and subtract 1
new_number <- as.integer(first_number) - 1

# Construct the new path
new_path <- paste0(
  substr(script_path_folder, 1, last_slash),
  new_number,
  "_*"
)

# Function to find directory matching the pattern
find_directory <- function(path_with_wildcard) {
   
  # Extract directory path without wildcard
  directory_path <- dirname(path_with_wildcard)
   
  # List files matching the pattern
  matching_files <- list.files(directory_path, pattern = basename(path_with_wildcard))
   
  # Check if any matching directory exists
  matching_directories <- matching_files[dir.exists(file.path(directory_path, matching_files))]
   
  if (length(matching_directories) > 0) {
     
    return(file.path(directory_path, matching_directories[1]))
     
  } else {
    return(NULL)
  }
}

# Find the actual directory matching the wildcard
rda_directory <- find_directory(new_path)

# Load .rda files  ---------------------------------

# Get list of all .rda files recursively
rda_files <- list.files(path = rda_directory, 
                        pattern = "\\.rda$",
                        recursive = TRUE,
                        full.names = TRUE)

# *NEW* objects before loading .rda from previous folder
objects_beforeload <- ls()

# Load each .rda file
for (file in rda_files) {
  load(file)
}

# NEW* objects obtains from load 

objects_afterload <- ls()

# Check Object dim by hand  ---------------------------------
# A little redundant 
loaded_obj <- setdiff(objects_afterload, objects_beforeload)
loaded_obj <- loaded_obj[!loaded_obj %in% c("file", "objects_beforeload")]

print("OBJECTS LOADED AND DIMENSIONS ")
for (obj_name in loaded_obj) {
  obj <- get(obj_name)  # get the actual object from its name
  dims <- if (!is.null(dim(obj))) dim(obj) else length(obj)
  print(paste0(obj_name, " Dim: ", paste(dims, collapse = " x ")))
}

# Collect starting Envr.  ---------------------------------

objects_starting <- ls()

```

### Check Input Object Sizes 
```{r, Check Input Object Sizes - Previous File, eval=TRUE}

dim_check <- list()
has_mismatch <- FALSE  # Variable to track if there's a mismatch

for (obj_name in objects_starting) {
  if (obj_name %in% names(objects_dim_list)) {
    correct_dimensions <- objects_dim_list[[obj_name]]
    actual_object <- get(obj_name)
    actual_dimensions <- list(rows = nrow(actual_object), cols = ncol(actual_object))
    
    if (identical(correct_dimensions, actual_dimensions)) {
      dim_check[[obj_name]] <- "Dimensions match"
    } else {
      # Construct the mismatch message
      mismatch_msg <- "Dimensions mismatch:"
      if (correct_dimensions$rows != actual_dimensions$rows) {
        mismatch_msg <- paste(mismatch_msg, "Expected rows is", correct_dimensions$rows,
                              "actual is", actual_dimensions$rows)
      }
      if (correct_dimensions$cols != actual_dimensions$cols) {
        mismatch_msg <- paste(mismatch_msg, "Expected columns is", correct_dimensions$cols,
                              "actual is", actual_dimensions$cols)
      }
      # Store the mismatch message in dim_check
      dim_check[[obj_name]] <- mismatch_msg
      has_mismatch <- TRUE  # Set has_mismatch to TRUE if there's a mismatch
    }
  }
}

# Print the output
print(dim_check)

# Check if there's a mismatch and stop if true
if (has_mismatch) {
  stop("There is at least one object with mismatched dimensions.")
} else {
  "No mismatch in loaded object sizes, continue code execution."
}

```


### Obtain Objects from folder 3_*
```{r, Obtain Objects from folder 3_*}
#       Find Object Code Folder 3_* -----------------------------------

        other_folder_number<-3

        # Construct the new path

        more_objects_path <- paste0(
          substr(script_path_folder, 1, last_slash),
          other_folder_number,
          "_*"
        )
        
        more_objects_path_defined<-find_directory(more_objects_path)
        
        
# Get objects from other 3_* folder 

rda_files<-list.files(path = more_objects_path_defined, 
                          pattern = "\\.rda$",
                          recursive = TRUE,
                          full.names = TRUE) 
   


# Load each .rda file in 3_* folder 
for (file in rda_files) {
  load(file)
}
        

#get downloaded objects 
objects_starting<-ls()

```

### Check Input Object Sizes 

```{r, Check Input Object Sizes - Folder 3_*}

dim_check <- list()
has_mismatch <- FALSE  # Variable to track if there's a mismatch

for (obj_name in objects_starting) {
  if (obj_name %in% names(objects_dim_list)) {
    correct_dimensions <- objects_dim_list[[obj_name]]
    actual_object <- get(obj_name)
    actual_dimensions <- list(rows = nrow(actual_object), cols = ncol(actual_object))
    
    if (identical(correct_dimensions, actual_dimensions)) {
      dim_check[[obj_name]] <- "Dimensions match"
    } else {
      # Construct the mismatch message
      mismatch_msg <- "Dimensions mismatch:"
      if (correct_dimensions$rows != actual_dimensions$rows) {
        mismatch_msg <- paste(mismatch_msg, "Expected rows is", correct_dimensions$rows,
                              "actual is", actual_dimensions$rows)
      }
      if (correct_dimensions$cols != actual_dimensions$cols) {
        mismatch_msg <- paste(mismatch_msg, "Expected columns is", correct_dimensions$cols,
                              "actual is", actual_dimensions$cols)
      }
      # Store the mismatch message in dim_check
      dim_check[[obj_name]] <- mismatch_msg
      has_mismatch <- TRUE  # Set has_mismatch to TRUE if there's a mismatch
    }
  }
}

# Print the output
print(dim_check)

# Check if there's a mismatch and stop if true
if (has_mismatch) {
  stop("There is at least one object with mismatched dimensions.")
}  else {"No mismatch in loaded object sizes, continue code execution." }

```


# Required Objects
```{r required_ojects}
d(microbes_vs_genes_corr_loop) #  33 11780
d(lincs_selectdrugs_share)     # 130 11781
d(zimm_metabolism_state)       #  5330    3

```

# MAIN -------------
# Set Seed 
```{r}
set.seed(2026)
```

# Clean microbe-omic corr 
```{r clean_corr}

# Remove Rows with NA values 
  
  mbio_corr_gene_clean<-microbes_vs_genes_corr_loop%>%
                             filter(!if_all(everything(), is.na))


# Summary -------

paste0( "Dropped microbes due to NA in host (tranX vs mic) corr matrix :")
print(setdiff(rn(microbes_vs_genes_corr_loop), rn(mbio_corr_gene_clean)) )
  
# Produced Objects --------------------
paste0("Dimension of cleaned microbe-omic corr matrix: ", dim(mbio_corr_gene_clean)[1], " x ",dim(mbio_corr_gene_clean)[2])  # 181 x 11780 


```

### Generate LINCS  **Gene expression CD ** X Gene-Mic Corr (aka Microbe-Host Sig) -------------------------- 

```{r generate_lincs_keystone}

# ----Generate Input Data Matrix----------------------

# Objects Needed 

            # Make LINCS matrix 
            lincs_selectdrugs_share_mat<-lincs_selectdrugs_share%>%
                                          column_to_rownames("DRUG") %>%
                                          as.matrix()

           lincs_selectdrugs_share_mat_t<-base::t(lincs_selectdrugs_share_mat)

# Execute 
for(i in 1:ncol(lincs_selectdrugs_share_mat_t)){
  
          print(paste0("ENTER col index: ", i))
  
            # Record drug name 
            drug_name<-colnames(lincs_selectdrugs_share_mat_t)[i]
            
            # Select the current drug CD 
            current_lincs_drug<-as.data.frame(lincs_selectdrugs_share_mat_t[,i])
            current_lincs_drug<-current_lincs_drug[[1]]
          
            
            # Multiply the gene expression LINCS sig to the microbe-omic corr
            
            build_curr<-sweep(mbio_corr_gene_clean, MARGIN=2, current_lincs_drug, `*`) # KEYSTONE  2 = across cols 

      # Collect and aggregate info 
            
      build_curr<-build_curr%>% mutate(
                                  microbe = rownames(build_curr), 
                                  drug = rep(drug_name, nrow(build_curr)))%>%
                                  select(microbe, drug, everything(.))
      
      # Renaame the df if its the first one         
      
      if(i == 1){
        building<- build_curr
      } else { 
        
      # Add to main building DF 
      
        building<-rbind(building, build_curr)        
      }
      

        
      # If last col rename 
        if(i == ncol(lincs_selectdrugs_share_mat_t) ){
          
          MHG_corr_sig<-building
          
        }
}



```


# Assign Metabolism State 


## Designate Microbes 
```{r desig_mic}

# Rename the B. thet and B. frag strains to pick one to represent the metabolism state. 
# Note they are all similar in -1 +1 metabolism state so it really does not matter which one. 



# Separate out B. frag and B thet 

                        split1<-zimm_metabolism_state%>%
                                                                filter(str_starts(microbe, "Bacteroides fragilis") |
                                                                       str_starts(microbe, "Bacteroides thetaiotaomicron")) %>%  
                                                                pivot_wider(names_from="drug", 
                                                                            values_from="state")
                        
                        # Rename B frag 
                        split1$microbe <- str_replace(
                                                                            split1$microbe,
                                                                            "^Bacteroides fragilis.*",
                                                                            "Bacteroides fragilis"
                                                                          )
                        # Rename B Thet
                        split1$microbe <- str_replace(
                                                                            split1$microbe,
                                                                            "^Bacteroides thetaiotaomicron.*",
                                                                            "Bacteroides thetaiotaomicron"
                                                                          )
                        # Keep one of each                                                                        
                        split1<-split1%>%
                                       distinct(microbe, .keep_all = TRUE)%>%
                                        pivot_longer(cols = acecainide:zaleplon, 
                                                     names_to="drug", 
                                                     values_to="state")

# Separate out the other microbes that ARE already unique 
                        split2<-zimm_metabolism_state%>%
                                      filter(!str_starts(microbe, "Bacteroides fragilis") &
                                             !str_starts(microbe, "Bacteroides thetaiotaomicron"))  

                        
                        
# Remerge and make alphabetically 
zimm_metabolism_state_mod<-rbind(split1, split2) %>%
                                    arrange(microbe, drug )


# Add Meta state, if no state found NA is provided
 Master_MHG_corr_sig_temp<-MHG_corr_sig%>%
                              inner_join(zimm_metabolism_state_mod, by=c("drug", "microbe"))%>%
                              select(microbe, drug, state, everything(.))
                     
                    
 
```

#  Class Balancing Metabolism - for Training  
### Define Fxn
```{r, }

# data<-large_sample_size
# Define Proportion Functions ----------------------------------
find_prop<- function(data){
  
  temp<-data
  
  temp$tally<-rep(1, nrow(temp))
  
  df<- xtabs(tally ~ microbe + state,  temp)
  
  prop<-proportions(df, "state")
  
  prop<-as.data.frame(prop)
  
  prop<-prop%>%
    dplyr::arrange(microbe)%>%
    mutate(Freq = round(Freq, digits = 2)) 
  
  return(prop)
  
}

# assume all DF will have the same microbe, therefore the structure of the tables should contain the same microbe and be in alphabetical order. This code does not account for microbe being in different places within each respective table, nor if the dataframes have different microbe. 


comp_prob_table<- function(df1,df2){ 
  
  
  df1_prob<-find_prop(df1)
  
  df2_prob<-find_prop(df2)
  
  if (any( df1_prob != df2_prob ) ){
    
    print("DF DO NOT share all values")
    return(FALSE) 
    
  } else { 
    return (TRUE) }
  
}

# Define Class Balance Function ----------------------------- 

# boot_df<-Master_MHG_corr_sig_temp

execute_classbal<-function(boot_df){
  
  # Split Bootstrap and Count Sample Size per Group ---------------------
  
  
  boot_df_pos1<- boot_df%>%
    filter(state == 1)
  
  boot_df_neg1<- boot_df%>%
    filter(state == -1)
  
  boot_df_NA<-boot_df%>%
    filter(is.na(state) )
  
  # Compare Sizes of Groups -----------------------
  
  if ( nrow(boot_df_neg1) != nrow(boot_df_pos1) ) {
    
    
    if ( nrow(boot_df_neg1) > nrow(boot_df_pos1) ){
      
      large_sample_size<- boot_df_neg1
      
      small_sample_size<- boot_df_pos1
      
    }
    
    if ( nrow(boot_df_neg1) < nrow(boot_df_pos1) ){
      
      large_sample_size<- boot_df_pos1
      
      small_sample_size<- boot_df_neg1
      
      print("FYI the LARGER group is state POSITIVE 1 ")
    }
    
    
    # Prep for DF building ----------------------
    
    
    
    # Make Building Table Blank 
    
    building_table<-large_sample_size[FALSE,]
    
    # Define smaller group size to shrink larger
    
    small_group_size<- nrow(small_sample_size) 
    
    # Record ratio of larger group, determine counts needed to maintain proportions as we shrink
    # We are assuming there are enough samples in the largest group to provide enough rows per microbe to condense to the smaller size 
    
    large_prob<-find_prop(large_sample_size)
    
    large_prob<-large_prob%>% 
      mutate(require_count = ceiling( Freq * small_group_size ))
    
    
    # Fill building table with specified counts 
    for( i in 1:nrow(large_prob)){
      
      # Define microbe and count 
      large_prob_row<-large_prob[i,]
      
      mic<-large_prob_row$microbe
      
      count<-large_prob_row$require_count
      
      
      # Sort DF with select microbe only 
      large_sample_size_microbe<-large_sample_size%>%
        filter(microbe == mic)
      
      # Select required amount of rows 
      selected_count<-dplyr::sample_n(large_sample_size_microbe, count)
      
      
      # Merge with building table 
      building_table<-rbind(selected_count, building_table)
      
    }
    
    
    if( comp_prob_table(building_table, large_sample_size) == TRUE &    
        nrow(small_sample_size) <= nrow(building_table) & 
        nrow(building_table) <= nrow(small_sample_size)+nrow(large_prob) # wont be exactly equal, will max maxim largest difference if say there was one extra per microbe b/c of the rounding in the fxn 
    ) {
      
      print(paste0("Created equal group size between -1 and 1, size per (+/-1): ", nrow(building_table)) )
      
      classbal_boot<-rbind(small_sample_size, building_table, boot_df_NA)
      
      
    }
    
    
    
  } else {
    
    print(paste0("Existing equal group size between -1 and 1, size per: ", nrow(boot_df[which(boot_df$state==-1),]) + nrow(boot_df[which(boot_df$state== 1),]) ))
    
    classbal_boot<-boot_df
    
  }
  
  
  return(classbal_boot)
  
  
} # End of function



```

### Execute 
```{r, }

# Apply to list of bootstrapped dataframes ----------------------------------- 
  
Master_MHG_corr_sig<-execute_classbal(Master_MHG_corr_sig_temp)

```


# Produced Objects --------------------
```{r}

# Extract those with NA meta state -----------------------------
Master_MHG_corr_sig_NA<- Master_MHG_corr_sig%>%
                                        filter(is.na(state))

# Extract those with -1 or +1 meta state ------------------------
Master_MHG_corr_sig_temp2 <-Master_MHG_corr_sig%>%
                                        filter(!is.na(state))

# Create stratified split ---------------------------------------
split <- initial_split(Master_MHG_corr_sig_temp2, prop = 0.8, strata = state)

Master_MHG_corr_sig_train <- training(split)
Master_MHG_corr_sig_test  <- testing(split)



# Produced Objects ------------------------
paste0("Prediction data dim: ", d(Master_MHG_corr_sig_NA)[1]," X " ,d(Master_MHG_corr_sig_NA)[2])
paste0("Training data dim: ", d(Master_MHG_corr_sig_train)[1]," X " ,d(Master_MHG_corr_sig_train)[2])
paste0("Testing data dim: ", d(Master_MHG_corr_sig_test)[1]," X " ,d(Master_MHG_corr_sig_test)[2])

```

# CLOSING ------------------
### Save Object Sizes ***Specify Objects***
```{r saveojb_size}

# Note- rather than saving all created objects I will specify the three dataframes we need for the next code section. 

objects_created <- c("Master_MHG_corr_sig_train", "Master_MHG_corr_sig_test", "Master_MHG_corr_sig_NA")

reccord_dim <- function(objects) {
  
  result <- list()
  
  for (obj_name in objects) {
    
    if (exists(obj_name)) {
      
      obj <- get(obj_name)
      
      if (is.data.frame(obj) || is.matrix(obj)) {
        
        rows <- nrow(obj)
        cols <- ncol(obj)
        result[[obj_name]] <- list(rows = rows, cols = cols)
        
      } else {
        
        warning(paste("Object labeled ", obj_name, "is not a data frame or a matrix. Skipping."))
      }
      
    } else {
      
      warning(paste("Object", obj_name, "does not exist. Skipping."))
      
    }
  }
  return(result)
}

objects_dim_list<-reccord_dim(objects_created)




#          Summary --------------------------------------------- 

print("Created Objects Summary:")
print(objects_dim_list)

```

# Partition Testing, Training, and to Predict 
```{r partition, eval= FALSE}

# Extract those with NA meta state ------------------------

Master_MHG_corr_sig_NA<- Master_MHG_corr_sig_temp%>%
                                        filter(is.na(state))

# Partition Testing and Training with Class Bal ---------- 

Master_MHG_corr_sig_temp2<- Master_MHG_corr_sig_temp%>%
                                   filter(!is.na(state))

# Seperate -1 and +1 

pos<-Master_MHG_corr_sig_temp2%>%filter(state == 1)
neg<-Master_MHG_corr_sig_temp2%>%filter(state == -1)


split <- initial_split(Master_MHG_corr_sig_temp2, prop = 0.8, strata = state)

Master_MHG_corr_sig_train <- training(split)
Master_MHG_corr_sig_test  <- testing(split)

# Produced Objects --------------------
paste0("Prediction data dim: ", d(Master_MHG_corr_sig_NA)[1]," X " ,d(Master_MHG_corr_sig_NA)[2])

paste0("Training data dim: ", d(Master_MHG_corr_sig_train)[1]," X " ,d(Master_MHG_corr_sig_train)[2])

paste0("Testing data dim: ", d(Master_MHG_corr_sig_test)[1]," X " ,d(Master_MHG_corr_sig_test)[2])


```



### Exporting and Clean Up - Part 1/2
```{r export_1}
#           Create Output File ------------------------------------------------------


current_output_folder<-paste0(script_name_base, "_", run_timestamp, ".Rmd")

dir.create(current_output_folder)

script_path_with_output_folder <- file.path(script_path_folder, 
                                          current_output_folder)


#           Export Run Info ---------------------------------------------------------

writeLines(capture.output(run_sessionInfo), file.path(script_path_with_output_folder, "sessionInfo.txt"))
```

### Exporting and Clean Up - Part 2/2 **Specify Objects**
```{r export2}

setwd(script_path_with_output_folder) # need to restate for each code chunk

#           Export Objects as .rda - **SPECIFY OBJECTS**----------------------------------------------------

objects_save<-c( objects_created, "objects_dim_list")

                            
save(list=objects_save,                   
     file = "env_obj.rda")
 
```

