---
title: "multi_drug_svm"
author: "Dali_Nemecio"
date: "`r Sys.Date()`"
output: 
  html_document:
    code_folding: hide
---

FYI: main code takes about <1hr to run!!! 

## Start ---------------------------------------------------------------------
# MAC SET UP ------------
```{r , include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Set up
```{r}
#           Load Library **SPECIFY**------------------------------------------------------------
packages_needed<-c("knitr","readr",
                   "tidyverse",
                   "tibble", 
                   "dplyr",
                   "rstudioapi","caret",
                   "kernlab", "measures", "PRROC", "mlr", 
                   "tidyverse") 

for (pkg in packages_needed){
if ( !require(pkg, character.only = TRUE)){
  library(pkg, character.only = TRUE)
} 
}

#           Collect Script Info and Change To Script Directory ---------------


#Script Directory
script_path_current <- getSourceEditorContext()$path
script_path_folder<-sub("/[^/]*$", "", script_path_current)
script_name<-sub(".*/", "", script_path_current)
script_name_base<-sub("\\..*$", "", script_name)

#Change directory in all code chunks to current script location
knitr::opts_knit$set(root.dir = script_path_folder)
 

#           Collect Run Info------------------------------------------- 
run_timestamp <- format(Sys.time(), "%Y_%m_%d_%H%M")

run_sessionInfo<-sessionInfo()

```

## Shortcuts
```{r}
source("/Users/dalinemecio/Documents/1_Rotations/Brubaker/R/x_smaller_folders/short_cuts/short_cuts.R")
```

## Load Data and Objects Required
```{r}
# Load Data - Collect .rda files ----------------------------------------

#       Find Previous Code Folder -----------------------------

# Find the last slash
last_slash <- max(gregexpr("/", script_path_folder)[[1]])

# Extract the substring
substring_after_last_slash <- substr(script_path_folder, last_slash + 1, nchar(script_path_folder))

# Extract the first number
first_number <- regmatches(substring_after_last_slash, regexpr("[0-9]+", substring_after_last_slash))

# Convert the first number to an integer and subtract 1
new_number <- as.integer(first_number) - 1

# Construct the new path
new_path <- paste0(
  substr(script_path_folder, 1, last_slash),
  new_number,
  "_*"
)

# Function to find directory matching the pattern
find_directory <- function(path_with_wildcard) {
  
  # Extract directory path without wildcard
  directory_path <- dirname(path_with_wildcard)
  
  # List files matching the pattern
  matching_files <- list.files(directory_path, pattern = basename(path_with_wildcard))
  
  # Check if any matching directory exists
  matching_directories <- matching_files[dir.exists(file.path(directory_path, matching_files))]
  
  if (length(matching_directories) > 0) {
    
    return(file.path(directory_path, matching_directories[1]))
    
  } else {
    return(NULL)
  }
}

# Find the actual directory matching the wildcard
rda_directory <- find_directory(new_path)

#       Load .rda files  ---------------------------------

# Get list of all .rda files recursively
rda_files <- list.files(path = rda_directory, 
                        pattern = "\\.rda$",
                        recursive = TRUE,
                        full.names = TRUE)

# Load each .rda file
for (file in rda_files) {
  load(file)
}

#       Check Object Sizes by hand--------------------------

# d(boot10_Master_analysis) 5400 9456

#       Collect starting Envr.  ---------------------------------

objects_starting<-ls()

```


## Check Input Object Sizes
```{r}

dim_check <- list()
has_mismatch <- FALSE  # Variable to track if there's a mismatch

for (obj_name in objects_starting) {
  if (obj_name %in% names(objects_dim_list)) {
    correct_dimensions <- objects_dim_list[[obj_name]]
    actual_object <- get(obj_name)
    actual_dimensions <- list(rows = nrow(actual_object), cols = ncol(actual_object))
    
    if (identical(correct_dimensions, actual_dimensions)) {
      dim_check[[obj_name]] <- "Dimensions match"
    } else {
      # Construct the mismatch message
      mismatch_msg <- "Dimensions mismatch:"
      if (correct_dimensions$rows != actual_dimensions$rows) {
        mismatch_msg <- paste(mismatch_msg, "Expected rows is", correct_dimensions$rows,
                              "actual is", actual_dimensions$rows)
      }
      if (correct_dimensions$cols != actual_dimensions$cols) {
        mismatch_msg <- paste(mismatch_msg, "Expected columns is", correct_dimensions$cols,
                              "actual is", actual_dimensions$cols)
      }
      # Store the mismatch message in dim_check
      dim_check[[obj_name]] <- mismatch_msg
      has_mismatch <- TRUE  # Set has_mismatch to TRUE if there's a mismatch
    }
  }
}

# Print the output
print(dim_check)

# Check if there's a mismatch and stop if true
if (has_mismatch) {
  stop("There is at least one object with mismatched dimensions.")
}  else {"No mismatch in loaded object sizes, continue code execution." }

```



# MAIN ------------------------------------------------------
# Set Seed
```{r}
set.seed(2026)
```
# Define Functions 
```{r}
# Prepare and strip data for MLR functions ----------

prep_mlr<-function(df, featvec, statecol){
  
  
# col name consistency - gene col names in dataframe 
    names(df)<-gsub("\\-",".",names(df))
    

# col name consistency - Gene col names featvector
    featvec<-gsub("\\-",".",featvec)

    #desired col names in training data
    alongforride_colnames<-colnames(df[1:6])
    
    colnames_w_features<- c(alongforride_colnames, featvec)
   
  # Filter known classes using dynamic column name
  DF_known <- df %>%
    dplyr::filter(.data[[statecol]] %in% c(-1, 1)) %>%
    dplyr::select(all_of(colnames_w_features))

  # Convert target to factor safely
  DF_known[[statecol]] <- factor(DF_known[[statecol]], levels = c( 1, -1))

  # Strip down to target + features
  out_stripped <- DF_known %>%
    dplyr::select(all_of(c(statecol, featvec)))

  # Diagnostics
  print(paste0("Dimensions of entering df: ", dim(df)[1], " x ", dim(df)[2]))
  print(paste0("Dimensions of output df: ", dim(out_stripped)[1], " x ", dim(out_stripped)[2]))

  print("Count of drug metabolism state in out data:")
  print(table(out_stripped[[statecol]]))

  return(out_stripped)
  
}

# Generate Conf Matr ----------

conf_mat<-function(df, thresh = NULL ){
  
  
# Comment on Threshold  
if(!is.null(thresh)){
  
df<-df%>%mutate(response = ifelse( prob.1 >= thresh, 1, -1))

print(paste0("Adjusted Threshold, positive class defined by :", thresh))

}else{
  
  check_pos_thresh(df)
  
}   
  
# Prep for Confusion Matrix ---------------
  
  df<-df%>%
      mutate(
        truth    = factor(truth, levels = c(1, -1)),
        response = factor(response, levels = c(1, -1))
      )
        
# Make Confusion Matrix -------------------
  
conf_ob<-confusionMatrix(data = df$response, reference = df$truth)


# Confusion Matrix as DF --------------
cm_df<-as.data.frame(conf_ob$table)


cm_df<-as.data.frame(cm_df)%>%
            rename(`response`=Prediction, 
                               `truth`=Reference, 
                               `n`=Freq)%>%
            select(truth, response, n)%>%
            mutate(order = case_when(         # Arrange rows in the order: TN, FP, FN, TP
              truth == -1 & response == -1 ~ 1,  # TN
              truth == -1 & response == 1  ~ 2,  # FP
              truth == 1  & response == -1 ~ 3,  # FN
              truth == 1  & response == 1  ~ 4   # TP
            )) %>%
            arrange(order) %>%
            select(-order)  # remove helper column if you like

return(cm_df)

}


# Calculate the Performance Metrics  ------------ 

calc_perf<-function(df, col_label){

# Prep for Confusion Matrix ---------------
  
  df<-df%>%
      mutate(
        truth    = factor(truth, levels = c(1, -1)),
        response = factor(response, levels = c(1, -1))
      )
        
# Make Confusion Matrix -------------------
  
conf_ob<-confusionMatrix(data = df$response, reference = df$truth)

# Extract Default Calculated Metrics ---------------
conf_perf<-as.data.frame(conf_ob$byClass)
colnames(conf_perf)[1]<-col_label  

temp<-as.data.frame(conf_ob$overall)
colnames(temp)[1]<-col_label  

met_1<-rbind(conf_perf, temp )

  
# Determine Hand Calculated Metrics ----------------------

TPR  <- conf_ob$byClass["Sensitivity"]
TNR  <- conf_ob$byClass["Specificity"]
FPR  <- 1 - TNR
FNR  <- 1 - TPR
MMCE <- 1 - conf_ob$overall["Accuracy"]

met_2 <- base::t(data.frame(mmce = MMCE, fpr = FPR, fnr = FNR, tpr = TPR, tnr = TNR))
colnames(met_2)[1]<-col_label



# Determine Alternative Function Calculated Metrics ----------------------
    
# Measure AUC 
AUC_ROC<-measureAUC(probabilities = df$prob.1, 
                   truth = df$truth,
                   negative = as.character(-1), 
                   positive = as.character(1)) # MLR Fxn 


# Measure Area Under Precision Recall Curve 
interest_scores<-df$prob.1[df$truth == 1]
other_scores<-df$`prob.1`[df$truth == -1]
au_pr_out <- PRROC::pr.curve(scores.class0 = as.numeric(interest_scores), # class of interest aka positive class aka +1 
                       scores.class1 = as.numeric(other_scores),
                       curve = TRUE)

AUC_PR<-au_pr_out$auc.integral


temp<-data.frame(AUC_ROC=AUC_ROC, AUC_PR=AUC_PR )
met_3<-base::t(temp)
colnames(met_3)[1]<-col_label


# Clean and Return -------------------------
metric_order <- c(
  
  "Precision",
  "Accuracy",
  "Recall",
  "Specificity",
  
  "AUC_ROC", 
  "AUC_PR", 

  "mmce", 
  "fpr", 
  "fnr", 
  "tpr", 
  "tnr",
  
  
  "F1",
  "Pos Pred Value",
  "Neg Pred Value",
  "Sensitivity",
  "Prevalence",
  "Detection Rate",
  "Detection Prevalence",
  
  "Kappa",
  "Balanced Accuracy", 
  "AccuracyLower",
  "AccuracyUpper",
  "AccuracyNull",
  "AccuracyPValue",
  "McnemarPValue"
)


# Collapse all Metircs into DF 
out<-rbind(met_1, met_2, met_3)
out <- out[metric_order, , drop = FALSE]


# Convert NAN and NA to Zero and Round
out<-out%>%
  mutate(across(everything(), ~ ifelse(is.na(.) | is.nan(.), 0, .))) %>%
  mutate(across(everything(), ~ round(., 2)))


return(out)  
    
  
  
}

# Calculate the Performance Metrics Looped ------------------------------

calc_perf_multithresh<-function(df, vec){
  
  
for (i in 1:l(vec)){
  
  cur_thresh<-vec[i]
  col_label<-paste0("ProbThresh_", cur_thresh)
  
  # Adjust predictions on threshold --------------------
  
  df<-df%>%mutate(response = ifelse( prob.1 >= cur_thresh, 1, -1)) # predictions adjusted for threshold 
  

  # Confusion Matrix --------------
  
  cur_conf<-conf_mat(df, cur_thresh) # confusion matrix adjusted for threshold 
  
  
  # Make list if i == 1
  
  if (i == 1){ list_mat<-list() }

  # Collect 
  
  list_mat[[i]] <-cur_conf
  names(list_mat)[i] <- col_label
  
# Performance Metrics -------------
  
  cur_perf_calc<-calc_perf(df, col_label )
  
  
  # Make list if i == 1
  if (i == 1){ build_perf<-cur_perf_calc }else{  
  # Collect 
  build_perf<-cbind(build_perf, cur_perf_calc) 
  }
  
}
  
  
  # Package to Close 
  out<-list( build_perf, list_mat) 
  names(out)<-c("Performance", "ConfusionMat")
  
  
  return(out)
  
  
  
  
  
}


# Collect the performance and confusion matrix looped per iteration on desired threshold ----------------------------

calc_perf_multiiter<-function(df, thresh){

          
        for(i in 1:max(df$iter)){
          
        # sanity check 
        if (l(u(df$iter)) != max(df$iter)){error("Number of iterations does not equal maximum iteration found")}
        
        # FIlter for iteration   
        curr_df<-df%>%filter(iter == i)
        
        temp<-calc_perf_multithresh(curr_df, thresh) # the desired threshold 
        
        
            
          # Build column name
          col_label <- paste0("iter", i, "_ProbThresh_", thresh)
        
          # Rename performance column
          colnames(temp$Performance)[1] <- col_label
        
          # Rename confusion matrix list entry
          names(temp$ConfusionMat)[1] <- col_label
        
          # Collect 
          if(i == 1){
            
            build_conf <- temp
          
            } else {
              
            # collect performance 
            build_conf$Performance <- cbind(
              build_conf$Performance,
              temp$Performance)
              
                
            # Collect Matrix 
            
            build_conf$ConfusionMat[[col_label]] <- temp$ConfusionMat[[1]]
                
                
        
        
        
          }

        }
  
  return(build_conf)
  }


# Check threshold associated with lowest probability of positive classification -----------

check_pos_thresh<-function(df){
    
    temp<-df%>% 
  filter(response == 1) %>%
  arrange(desc(prob.1)) %>%
  tail(1)

 print(paste0(" Threshold lowest prob for positive class is:", temp$prob.1))
        
      

      }


```

# Desired Pred Thresh 
```{r}

desired_prob_thresh<-0.50

```

# Data Prep ------------------------------

## Create Training Data with Selected Features

## Define Features to Select
```{r}

      select_feats<-colnames(Master_MHG_corr_sig_train_500[4:ncol(Master_MHG_corr_sig_train_500)])

```

## Prep Training Data 
```{r}


drugstate_known_training_stripped<-prep_mlr(Master_MHG_corr_sig_train_500,
                                     select_feats , 
                                     "state")



    
```

# CV ------------------------------------

## Method Validation 

Purpose is to confirm the SVM and random search tuning procedures performs well and does not overfit. This is determined from the good performance metrics output immediately after this section. 

### Define Task, Learner, hyperparameter search, crossvalidation strategy 
```{r,  Define Task, Learner, hyperparameter search, crossvalidation strategy}

# Define task and learner ----------------------

# Supervised 
    
    #Task
    class_Task<-makeClassifTask(data = drugstate_known_training_stripped, 
                              target="state", 
                              positive = "1")                  
    #learner 
    svm_learner<-makeLearner("classif.svm",                         
                           predict.type="prob", 
                          predict.threshold = desired_prob_thresh
                          )    
    

# Define hyper parameter search space -------------------------------------
# Tuning the model 
                            
    
    kernels_choice<-c("polynomial", "radial", "sigmoid")          
    svm_ParamSpace<-makeParamSet(
                            makeDiscreteParam("kernel", values = kernels_choice),
                            makeIntegerParam("degree", lower = 1, upper = 3), # flexibility with hyperplane
                            makeNumericParam("cost", lower = 5, upper = 20),  # how much SVM should bend data to make smooth decision surface 
                            makeNumericParam("gamma", lower = 0, upper = 2) ) # distance of influence a training point has 
                            
    


# Define search procedure -------------------------------------------------
    
    # randomly select parameter combinations for tuning 
    randSearch_extended<-makeTuneControlRandom(maxit=60)          
    
    
    
# Define nested cross validation strategy ---------------------------------
# Nested CV mitigates over fitting common issue with k fold validation

    # Inner CV for hyperparameter tuning ------------    
      inner_cv<-makeResampleDesc("Holdout",                         
                                 split = 2/3,                    
                                 stratify.cols = "state", 
                                 predict = "both")                 

    # Outer CV for validation of hyperparamters ------------    
                                                                  
      outer_cv<-makeResampleDesc("CV", iters = 10, 
                                 stratify.cols = "state")     


# Define wrapper (learning SVM and tuning) --------------------
      
    svm_Wrapper<-makeTuneWrapper(
                            learner= svm_learner,
                            resampling = inner_cv,         
                            par.set=svm_ParamSpace,   
                            control = randSearch_extended  
                              )
      
    # output is learner object with hyperparameters defined
    


# Run CV with parameter tuning and record tested parameters -----------------
    
    svm_cv_method_val<-resample(
                              learner = svm_Wrapper, 
                              task = class_Task,
                              resampling = outer_cv,     
                              models = TRUE,             
                              extract = getTuneResult,   
                              measures = list(mmce,fpr, fnr, tpr, tnr, mlr::auc, timetrain))             
                                            


```

## Method Validation Summary

```{r}

# Selected Metrics to View 

print("Optimal hyperparameters from all iterations: ") 
cv_hyperparam_fold_table<-getNestedTuneResultsX(svm_cv_method_val) 
cv_hyperparam_fold_table                             

cv_hyperparam_fold_list<-svm_cv_method_val$extract  

```
# CV Performance ---------------------------

## Adjust Threshold for Metrics 
```{r}

# Set threshold to adjust predictions 
svm_cv_method_val$pred <- setThreshold(svm_cv_method_val$pred, desired_prob_thresh) # KEYSTONE


# Sanity Check ------------------- 
        
        temp<-svm_cv_method_val$pred$data
        temp<-temp%>%filter(prob.1 >= desired_prob_thresh)%>%
                    arrange(desc(prob.1))%>%
                    tail(n=1) # get last row 
                    
        
        if ( round(temp$prob.1, 2) >= desired_prob_thresh ){
          
          print(paste0("Lowest probability in predictions is ", temp$prob.1))
          
        }else{error("Issue with Desired threshold and threshold found in svm predictions. ")}
        


```


## Aggregate 

### *Sensitivity Point* - Calc Conf Matrix & Perf Met - Multi Thresh

```{r}
# Extract the Data -----------------------------

 all_call_CV<- as.data.frame(svm_cv_method_val$pred[["data"]])


# Execute --------------------------------



prob_thresh_vec<-c(seq(0, 1, by = 0.05))

cv_perf_confmat_allthresh<-calc_perf_multithresh(all_call_CV, prob_thresh_vec)


# Produced objects 
cv_perf_confmat_allthresh



```
### *Sensitivity Point* - Perf Across Prob Threshs

- on Aggregated/ All training data

Plotting the performance metrics across difference probability thresholds to define the positive class. 

```{r}

### Elongate --------------------------------------

# Extract the performance measures 
cv_perf_mat_allthresh<-cv_perf_confmat_allthresh$Performance

# Pivot and Filter for desired metrics 
cv_perf_mat_allthresh$Metric<-rownames(cv_perf_mat_allthresh)
cv_perf_mat_allthresh<-cv_perf_mat_allthresh%>%select(Metric, everything())

desired_metrics<-c("Precision", "Accuracy", "Recall", "Specificity")

enter<-tidyr::pivot_longer(cv_perf_mat_allthresh,
               cols=  ProbThresh_0:ProbThresh_1, 
               names_to = "ProbThresh", 
               values_to="value")%>%
  
        mutate(ProbThresh = gsub("ProbThresh_", "", ProbThresh))%>%
        mutate(Metric = factor(Metric, 
                           levels = desired_metrics))%>% # Make Metric a factor with this order 
        filter(Metric %in% desired_metrics)%>%
        mutate(value = as.numeric(value)) 


### Plot ----------------------------------------------
# Selections --------------------------

# Desired Thresholds for Prob Assessment 
selected_points<-seq(0,1, by = 0.1)

# Desired Performance Metrics to show 
select_metric<- c("Precision", 
                  #"Accuracy", 
                  "Recall" #, 
                  #"Specificity"
                  )

# colors 
gp_colors<- c( Precision= "#FFB000", 
               Accuracy = "#FE6100", 
               Recall =  "#785EF0", 
               Specificity = "#DC267F" )

# shapes 
gp_shapes <- c(
  Precision   = 21,
  Accuracy    = 22,
  Recall      = 23,
  Specificity = 24
)


# Plot CV Aggg -----------------------------

# Selected Performance Metrics 
plot_cv_agg_sensi<-enter%>%
        filter(Metric %in% all_of(select_metric), 
               ProbThresh %in% all_of(selected_points))  %>%
  ggplot(aes(x = ProbThresh, y = value, group = Metric, color = Metric, fill = Metric, shape=Metric)) +
  geom_line(size = 1) +                      
  geom_point( size = 3) + 
  scale_color_manual(values = gp_colors) +      
  scale_fill_manual(values = gp_colors) +    
  scale_shape_manual(values = gp_shapes) + 
  scale_y_continuous(limits= c(0,1), breaks = c(0.00, 0.20 ,0.40 ,0.60, 0.80 ,1.00) ) +             
  ggtitle("Sensitivity Analysis on Prediction Threshold") +
  ylab("Performance")+
  xlab("Probability Threshold for Metabolism")+
    labs(caption = "CV aggregated all folds")+
  theme(
    legend.title = element_blank(),
    plot.title = element_text(hjust = 0.5, size = 16)
  )




# All Performance Metrics 
plot_cv_agg_sensi_all<-enter%>%
        filter( 
               ProbThresh %in% all_of(selected_points))  %>%
  ggplot(aes(x = ProbThresh, y = value, group = Metric, color = Metric, fill = Metric, shape=Metric)) +
  geom_line(size = 1) +                      
  geom_point( size = 3) +    
  scale_color_manual(values = gp_colors) +      
  scale_fill_manual(values = gp_colors) +         
  scale_shape_manual(values = gp_shapes) + 
  scale_y_continuous(limits= c(0,1), breaks = c(0.00, 0.20 ,0.40 ,0.60, 0.80 ,1.00) ) +             
  ggtitle("Sensitivity Analysis on Prediction Threshold") +
  ylab("Performance")+
  xlab("Probability Threshold for Metabolism")+
  labs(caption = "CV aggregated all folds")+
  theme(
    legend.title = element_blank(),
    plot.title = element_text(hjust = 0.5, size = 16)
  )

```


### *Sensitivity Point* - Extract Threshold based on F1 and Neg Pred. Value 


```{r}

temp<-base::t(cv_perf_confmat_allthresh$Performance)%>%
  as.data.frame(.)%>%
  dplyr::select("F1", "Recall", "Neg Pred Value", "Specificity", "fnr", "Balanced Accuracy", "Kappa")



 # Highest Meta Threshold ---------------------------------------------

# Select Highest F1 value and associated threshold 

{ 
  
F1_high<-sort(u(temp$F1), decreasing=TRUE)[1]

# Start Group Code Block 
temp2<-temp%>%
  dplyr::filter(F1 == F1_high)

# If one threshold with highest F1 choose that threshold 
if(nrow(temp2)==1){
  
  thresh_sensi_top<-rownames(temp2)%>%sub(".*_", "", .)%>%as.numeric(.)
  
}else{
  
# If multiple thresholds with highest F1, Tie breaker is Highest Recall 
  
  # Collect highest recall 
  Recall_high<-sort(u(temp2$Recall), decreasing=TRUE)[1]

  
  
  #Filter for highest recall 
  temp3<-temp2%>%dplyr::filter(Recall == Recall_high)
    
# If Only only thresh with highest recall select it   
  if(nrow(temp3) ==1){
    
  thresh_sensi_top<-rownames(temp3)%>%sub(".*_", "", .)%>%as.numeric(.)

  
  }else{
    
    # pull the lowest threshold if ties between two perf metrics 
    thresh_sensi_top<-rownames(temp3)%>%
        sub(".*_", "", .)%>%
        as.numeric(.)%>%
        sort(., decreasing=FALSE)%>%
        .[1]%>%as.numeric(.)
    
    print("Tie Breaker enacted for Metabolizing Threshold")
  } 
  
  
} # end of nested if statements 
} # end of Grouped code block 



 # Bottom Nonmeta Threshold ---------------------------------------------

# Select Highest F1 value and associated threshold 

{
  
NPV_high<-sort(u(temp$`Neg Pred Value`), decreasing=TRUE)[1]  # Start Group Code Block 

temp2<-temp%>%
  dplyr::filter(`Neg Pred Value` == NPV_high)

# If one threshold with highest F1 choose that threshold 
if(nrow(temp2)==1){
  
  thresh_sensi_bot<-rownames(temp2)%>%sub(".*_", "", .)%>%as.numeric(.)

  
}else{
  
# If multiple thresholds with highest F1, Tie breaker is Highest Recall 
  
  # Collect highest recall 
 Spec_high<-sort(u(temp2$Specificity), decreasing=TRUE)[1]

  
  #Filter for highest recall 
  temp3<-temp2%>%dplyr::filter(Specificity == Spec_high)
    
# If Only only thresh with highest recall select it   
  if(nrow(temp3) ==1){
    
  thresh_sensi_bot<-rownames(temp3)%>%sub(".*_", "", .)%>%as.numeric(.)

  
  
  }else{
    
    # pull the highest threshold if ties between two perf metrics 
    thresh_sensi_bot<-rownames(temp3)%>%
        sub(".*_", "", .)%>%
        as.numeric(.)%>%
        sort(., decreasing=TRUE)%>%
        .[1]%>%as.numeric(.)
    
    print("Tie Breaker enacted for Nonmetabolizing Threshold")
  
  } 
  
  
} # end of nested if statements 
} # end of Grouped code block 




# Printed Summary 

print(paste0("Sensitivity Analysis on Classification threshold found top Meta. thresh: ", thresh_sensi_top))
print(paste0("Sensitivity Analysis on Classification threshold found botton non Meta. thresh: ", thresh_sensi_bot))
```

### Extract Perf. and ConfMat on Desired Thresh 

Choose matrix with prob threshold defined at the start labeled as desired_prob_thresh

```{r}

# name of Col with desired threshold
namedcol<-paste0("ProbThresh_", desired_prob_thresh)

# Performance from Aggregated Folds with desired threshold
cv_perf_agg<-cv_perf_confmat_allthresh$Performance%>%select(all_of(namedcol))

# Confusion Matrix from Aggregated Folds with desired Threshold 

cv_confmat_agg<- cv_perf_confmat_allthresh$ConfusionMat[[namedcol]]

# Obtained Objects 
print(paste0("Aggregated Crossvalidation Performance (Threshold of ", desired_prob_thresh, ")"))

cv_perf_agg

print(paste0("Aggregated Crossvalidation Confusion Matrix (Threshold of ", desired_prob_thresh, ")"))

cv_confmat_agg
```





### Performance curves

```{r}

# Collect Number of Cases per State for Plot 

n_pos_cv<-sum(drugstate_known_training_stripped$state == 1 )
n_neg_cv<-sum(drugstate_known_training_stripped$state == -1 )


samplecount_cv<-paste0("n: (+1) ", n_pos_cv,", (-1) ", n_neg_cv)


# Performance Curves - Aggregated ----------------------------------

thresh_vs_perf_agg<-generateThreshVsPerfData(obj = svm_cv_method_val$pred,
                                             measures = list(mmce,fpr, fnr, tpr, tnr, ppv),
                                             gridsize = 100L,
                                             aggregate = TRUE 
                                             )

# False Negative Rate vs True Negative Rate 

ft_neg_agg_cv<-plotROCCurves(obj = thresh_vs_perf_agg,
              measures = list(fnr, tnr) )+ 
              ggtitle(paste0("False Negative Rate vs True Negative Rate, CV Performance, ",samplecount_cv)) +
              theme(plot.title = element_text(size = 10))

# ROC - Sensitivity and Specificity curve 

ft_pos_agg_cv<-plotROCCurves(obj = thresh_vs_perf_agg,
              measures = list(fpr, tpr) )+      
               ggtitle(paste0("ROC - Sensitivity-Specifificty Curve, CV Performance, ",samplecount_cv))+
                 theme(plot.title = element_text(size = 10))
# Precision/Recall

prec_recall_agg_cv<-plotROCCurves(thresh_vs_perf_agg, measures = list(tpr, ppv), diagonal = FALSE)+      
                    ggtitle(paste0("Precision-Recall Curve, CV Performance, ",samplecount_cv))+
                    theme(plot.title = element_text(size = 10))


```



## Per Iteration
### Sanity Check 
```{r}

  temp<-all_call_CV%>% 
  filter(response == 1) %>%
  arrange(desc(prob.1)) %>%
  tail(1)
  
print(paste0("No Threshold Adjustment, lowest prob for positive class is:", temp$prob.1))
        
```

### Generate Per iteration conf mat at desired thresh 

Using Desired threshold calculate the performance per iteration 

```{r}

# Per iteration Confusion Matrix -------------

cv_iter_result_desirethresh<-calc_perf_multiiter(all_call_CV, desired_prob_thresh)

cv_iter_result_desirethresh

```



### Extract Perf. and ConfMat on Desired Thresh  

Choose matrix with prob threshold defined at the start labeled as desired_prob_thresh

```{r}

# name of Col with desired threshold
namedcol<-paste0("ProbThresh_", desired_prob_thresh)

# Performance per iteration with desired threshold
cv_perf_per_iter<-cv_iter_result_desirethresh$Performance

# Confusion Matrix fper iteration with desired Threshold 
cv_confmat_per_iter<- cv_iter_result_desirethresh$ConfusionMat


# Obtained Objects 
print(paste0("Per iteration Performance (Threshold of ", desired_prob_thresh, ")"))

cv_perf_per_iter

print(paste0("Per iteration Confusion Matrix (Threshold of ", desired_prob_thresh, ")"))

cv_confmat_per_iter

```



### Performance curves
```{r}


# ROC curve from predictions - Per iteration ----------------------------------

thresh_vs_perf<-generateThreshVsPerfData( obj = svm_cv_method_val$pred, 
                                              measures = list(mmce,fpr, fnr, tpr, tnr, ppv), 
                                              gridsize = 100L, 
                                              aggregate = FALSE # plot performance of individual iterations 
                                          )

# False Negative Rate vs True Negative Rate 


ft_neg_cv<-plotROCCurves(obj = thresh_vs_perf,
                          measures = list(fnr, tnr) )+      
  ggtitle(paste0("False Negative Rate vs True Negative Rate, CV Performance, ",samplecount_cv) )+
  theme(plot.title = element_text(size = 10))



# ROC - Sensitivity and Specificity 

ft_pos_cv<-plotROCCurves(obj = thresh_vs_perf,
                          measures = list(fpr, tpr) )+      
  ggtitle(paste0("ROC - Sensitivity-Specifificty Curve, Trained on:\n, CV Performance, ", samplecount_cv) )+
  theme(plot.title = element_text(size = 10))


# Precision/Recall

prec_recall_cv<-plotROCCurves(thresh_vs_perf, measures = list(tpr, ppv), diagonal = FALSE)+      
                    ggtitle(paste0("Precision-Recall Curve, Trained on:\n, CV Performance, ", samplecount_cv) )+
                    theme(plot.title = element_text(size = 10))

# Plot - Performance vs Threshold

ThreshvsPerf_plots_iter_cv<-plotThreshVsPerf(thresh_vs_perf)


```


## Results Agg and Iter Plots
```{r}

# Aggregated ---------

# Sensitivity Analysis - Performance across multiple thresholds 
plot_cv_agg_sensi

plot_cv_agg_sensi_all


# Aggregated performance plots (on desired thresh)
ft_neg_agg_cv

ft_pos_agg_cv

prec_recall_agg_cv


# Per Iteration ---------

# Aggregated performance plots (on desired thresh)

ft_neg_cv

ft_pos_cv

prec_recall_cv

ThreshvsPerf_plots_iter_cv

```



## Results Summary
```{r}

print(paste0("Sensivity point performance across multi thresholds on aggregated training data"))

cv_perf_confmat_allthresh$Performance


print(paste0("Confusion Matrix across multi thresholds on aggregated training data"))

cv_perf_confmat_allthresh$ConfusionMat

```

```{r}


# Obtained Objects 
print(paste0("Aggregated Crossvalidation Performance (Threshold of ", desired_prob_thresh, ")"))

cv_perf_agg

print(paste0("Aggregated Crossvalidation Confusion Matrix (Threshold of ", desired_prob_thresh, ")"))

cv_confmat_agg


```

```{r}


# Obtained Objects 
print(paste0("Per iteration Performance (Threshold of ", desired_prob_thresh, ")"))

cv_perf_per_iter

print(paste0("Per iteration Confusion Matrix (Threshold of ", desired_prob_thresh, ")"))

cv_confmat_per_iter
```



# Model Training --------------------------------

```{r}

# Run the tuning procedure and return best combo of parameters 
    tunedSvmPars<-tuneParams(learner= svm_learner,     
                              task= class_Task,
                              resampling = inner_cv,
                              par.set= svm_ParamSpace,   
                              control = randSearch_extended
                                )

    print("Determined Hyperparameters :")
    tunedSvmPars$x

  
# Apply the hyperparameters 
    tunedSvm_sethyper<-setHyperPars(svm_learner, 
                            par.vals = tunedSvmPars$x)   

# THE TRAINED MODEL
      tunedSvmModel<-mlr::train(tunedSvm_sethyper, class_Task) # Keystone 
                                                       
    
# The Trained Model Performance Metrics
    
    as.data.frame(tunedSvmPars$opt.path)

```
# Results 
```{r}

print( paste0("Determined Hyperparameters for Model Training: ") ) 
print(tunedSvmPars$x)


# Model 
print( paste0("Trained Model: " ) ) 
model_overview<-capture.output({tunedSvmModel})
print(model_overview)



```

# Learning Curves ----------------------
## Define Model and Learner 
```{r}
# Used and defined in the CV ------------------ 

# Define outer CV for Learning Curve 
    
          outer_cv_lc <- makeResampleDesc("CV", iters = 10, 
                                              stratify.cols = "state", predict = "both")
# Learner
    
          svm_learner_opthyper<-makeLearner("classif.svm",                         
                                              predict.type="prob", 
                                            predict.threshold = desired_prob_thresh,
                                              par.vals = tunedSvmPars$x )   # OPTIMAL HYPERPARAMTERS for model training                
 
          
```


## Generate 

```{r}

                                            
# Performance metrics Aggregated 
    
    # ACCURACY DF -----------------------------------------------

acc_agg<- generateLearningCurveData(
                            learners = svm_learner_opthyper, 
                            task = class_Task,
                            percs = seq(0.1, 1, by = 0.1), 
                            measures = list(acc, setAggregation(acc, train.mean)),
                            
                            resampling = outer_cv_lc,
                            show.info = FALSE)

acc_agg

    # MEAN MISCLASSIFICATION DF -----------------------------------------------


mmce_agg<- generateLearningCurveData(
                            learners = svm_learner_opthyper,     
                            task = class_Task,
                            percs = seq(0.1, 1, by = 0.1),      
                            measures = list(mmce, setAggregation(mmce, train.mean)),
                            
                            resampling = outer_cv_lc,
                            show.info = FALSE)

mmce_agg



    # FALSE POSITTIVE RATE DF -----------------------------------------------


fpr_agg<- generateLearningCurveData(
                            learners = svm_learner_opthyper,     
                            task = class_Task,
                            percs = seq(0.1, 1, by = 0.1),      
                            measures = list(fpr, setAggregation(fpr, train.mean)),
                            
                            resampling = outer_cv_lc,
                            show.info = FALSE)

fpr_agg



    # TRUE POSITTIVE RATE DF -----------------------------------------------


tpr_agg<- generateLearningCurveData(
                            learners = svm_learner_opthyper,     
                            task = class_Task,
                            percs = seq(0.1, 1, by = 0.1),      
                            measures = list(tpr, setAggregation(tpr, train.mean)),
                            
                            resampling = outer_cv_lc,
                            show.info = FALSE)

tpr_agg


    # False negative RATE DF -----------------------------------------------


fnr_agg<- generateLearningCurveData(
                            learners = svm_learner_opthyper,     
                            task = class_Task,
                            percs = seq(0.1, 1, by = 0.1),      
                            measures = list(fnr, setAggregation(fnr, train.mean)),
                            
                            resampling = outer_cv_lc,
                            show.info = FALSE)

fnr_agg



    # True negative RATE DF -----------------------------------------------


tnr_agg<- generateLearningCurveData(
                            learners = svm_learner_opthyper,     
                            task = class_Task,
                            percs = seq(0.1, 1, by = 0.1),      
                            measures = list(tnr, setAggregation(tnr, train.mean)),
                            
                            resampling = outer_cv_lc,
                            show.info = FALSE)

tnr_agg




```

## Graphs
```{r}
acc_agg_plot_withlegend<-plotLearningCurve(acc_agg, 
                  facet = "learner" 
                  ) 

mmce_agg_plot_withlegend<-plotLearningCurve(mmce_agg, 
                  facet = "learner"      
                  ) 


acc_agg_plot<-plotLearningCurve(acc_agg, 
                  facet = "learner"      
                  ) + theme(legend.position = "none")

mmce_agg_plot<-plotLearningCurve(mmce_agg, 
                  facet = "learner"      
                  ) + theme(legend.position = "none")

tpr_agg_plot<-plotLearningCurve(tpr_agg, 
                  facet = "learner"      
                  ) + theme(legend.position = "none")

fpr_agg_plot<-plotLearningCurve(fpr_agg, 
                  facet = "learner"      
                  ) + theme(legend.position = "none")

tnr_agg_plot<-plotLearningCurve(tnr_agg, 
                  facet = "learner"      
                  ) + theme(legend.position = "none")

fnr_agg_plot<-plotLearningCurve(fnr_agg, 
                  facet = "learner"      
                  ) + theme(legend.position = "none")



# Produced Objects ------------

acc_agg_plot
mmce_agg_plot
tpr_agg_plot
fpr_agg_plot
tnr_agg_plot
fnr_agg_plot


```

## Replot 
```{r}
acc_agg
mmce_agg

fpr_agg


tpr_agg

fnr_agg
tnr_agg


# Function to apply consistent labels and limits
standardize_plot <- function(plot_obj) {
    
  # Convert to long format
  df <- plot_obj$data%>%
    select(-learner)
  
  leadcol<-names(df)[2] # Measure name
  endcol<-names(df)[3] # Performance value 
  
  
   long<-df %>%
          rename(Performance=performance, 
                 Group=measure
                 )
          
  # Define consistent axis labels
  x_label <- "Percentage of Training Data"
  y_label <- "Performance"
  
  # Define consistent y-axis range
  y_limits <- c(0, 1)  # adjust as needed; e.g., 0-1 for proportions
  x_limits<- c(0,1)

  out<-ggplot(long, aes( x= percentage, y= Performance, color = Group))+
    geom_line(size=1)+
    geom_point(size=2)+ 
    theme_minimal() + theme(legend.position = "none")+
    labs(x = x_label, y = y_label) +
    coord_cartesian(ylim = y_limits, xlim = x_limits) 
}

# Apply to your plots
acc_agg_plot <- standardize_plot(acc_agg_plot)
mmce_agg_plot <- standardize_plot(mmce_agg_plot)
tpr_agg_plot <- standardize_plot(tpr_agg_plot)
fpr_agg_plot <- standardize_plot(fpr_agg_plot)
tnr_agg_plot <- standardize_plot(tnr_agg_plot)
fnr_agg_plot <- standardize_plot(fnr_agg_plot)


```



# Test Model -----------------------------------
## Prep Training Data 
```{r}
drugstate_known_test_stripped<-prep_mlr(Master_MHG_corr_sig_test_500,
                                     select_feats , 
                                     "state")



```

# Execute Test 
```{r}

testoutput <- predict(tunedSvmModel, newdata = drugstate_known_test_stripped)

check_pos_thresh(testoutput$data)
```



# Test Performance ------------------------------------------


### *Sensitivity Point* - Calc Conf Matrix & Perf Met - Multi Thresh

```{r}
# Extract the Data -----------------------------

 all_call_test<- as.data.frame(testoutput$data)


# Execute --------------------------------



prob_thresh_vec<-c(seq(0, 1, by = 0.05))

test_perf_confmat_allthresh<-calc_perf_multithresh(all_call_test, prob_thresh_vec)


# Produced objects 
test_perf_confmat_allthresh



```
### *Sensitivity Point* - Perf Across Prob Threshs

- on Aggregated/ All training data

Plotting the performance metrics across difference probability thresholds to define the positive class. 

```{r}

### Elongate --------------------------------------

# Extract the performance measures 
test_perf_mat_allthresh<-test_perf_confmat_allthresh$Performance

# Pivot and Filter for desired metrics 
test_perf_mat_allthresh$Metric<-rownames(test_perf_mat_allthresh)
test_perf_mat_allthresh<-test_perf_mat_allthresh%>%select(Metric, everything())

desired_metrics<-c("Precision", "Accuracy", "Recall", "Specificity")

enter<-tidyr::pivot_longer(test_perf_mat_allthresh,
               cols=  ProbThresh_0:ProbThresh_1, 
               names_to = "ProbThresh", 
               values_to="value")%>%
  
        mutate(ProbThresh = gsub("ProbThresh_", "", ProbThresh))%>%
        mutate(Metric = factor(Metric, 
                           levels = desired_metrics))%>%
        filter(Metric %in% desired_metrics)%>%
        mutate(value = as.numeric(value))  


### Plot ----------------------------------------------
# Selections --------------------------

# Desired Thresholds for Prob Assessment 
selected_points<-seq(0,1, by = 0.1)

# Desired Performance Metrics to show 
select_metric<- c("Precision", 
                  #"Accuracy", 
                  "Recall" #, 
                  #"Specificity"
                  )

# colors 
gp_colors<- c( Precision= "#FFB000", 
               Accuracy = "#FE6100", 
               Recall =  "#785EF0", 
               Specificity = "#DC267F" )

# shapes 
gp_shapes <- c(
  Precision   = 21,
  Accuracy    = 22,
  Recall      = 23,
  Specificity = 24
)


# Plot CV Aggg -----------------------------

# Selected Performance Metrics 
plot_test_sensi<-enter%>%
        filter(Metric %in% all_of(select_metric), 
               ProbThresh %in% all_of(selected_points))  %>%
  ggplot(aes(x = ProbThresh, y = value, group = Metric, color = Metric, fill = Metric, shape=Metric)) +
  geom_line(size = 1) +                    
  geom_point( size = 3) +    
  scale_color_manual(values = gp_colors) +  
  scale_fill_manual(values = gp_colors) +         
  scale_shape_manual(values = gp_shapes) + 
  scale_y_continuous(limits= c(0,1), breaks = c(0.00, 0.20 ,0.40 ,0.60, 0.80 ,1.00) ) +             
  ggtitle("Sensitivity Analysis on Prediction Threshold") +
  ylab("Performance")+
  xlab("Probability Threshold for Metabolism")+
    labs(caption = "Test data")+
  theme(
    legend.title = element_blank(),
    plot.title = element_text(hjust = 0.5, size = 16)
  )




# All Performance Metrics 
plot_test_sensi_all<-enter%>%
        filter( 
               ProbThresh %in% all_of(selected_points))  %>%
  ggplot(aes(x = ProbThresh, y = value, group = Metric, color = Metric, fill = Metric, shape=Metric)) +
  geom_line(size = 1) +                      
  geom_point( size = 3) +    
  scale_color_manual(values = gp_colors) +      
  scale_fill_manual(values = gp_colors) +         
  scale_shape_manual(values = gp_shapes) + 
  scale_y_continuous(limits= c(0,1), breaks = c(0.00, 0.20 ,0.40 ,0.60, 0.80 ,1.00) ) +             
  ggtitle("Sensitivity Analysis on Prediction Threshold") +
  ylab("Performance")+
  xlab("Probability Threshold for Metabolism")+
  labs(caption = "Test Data")+
  theme(
    legend.title = element_blank(),
    plot.title = element_text(hjust = 0.5, size = 16)
  )


# Produced Objects 

plot_test_sensi
plot_test_sensi_all

```



### Extract Perf. and ConfMat on Desired Thresh  

Choose matrix with prob threshold defined at the start labeled as desired_prob_thresh

```{r}

# name of Col with desired threshold
namedcol<-paste0("ProbThresh_", desired_prob_thresh)

# Performance from  with desired threshold
test_perf<-test_perf_confmat_allthresh$Performance%>%select(all_of(namedcol))

# Confusion Matrix from with desired Threshold 

test_confmat<- test_perf_confmat_allthresh$ConfusionMat[[namedcol]]






# Obtained Objects 
print(paste0("Test Performance (Threshold of ", desired_prob_thresh, ")"))

test_perf

print(paste0("Test Confusion Matrix (Threshold of ", desired_prob_thresh, ")"))

test_confmat



```





## MLR Plot method

```{r}


# Collect --------------------------------------------------------


n_pos_test<-sum(drugstate_known_test_stripped$TV_state == 1 )
n_neg_test<-sum(drugstate_known_test_stripped$TV_state == -1 )


samplecount_test<-paste0("n: (+1) ", n_pos_test,", (-1) ", n_neg_test)



# Performance Curves - Aggregated ----------------------------------


thresh_vs_perf_test<-generateThreshVsPerfData(obj = testoutput,
                                             measures = list(mlr::mmce, mlr::acc, mlr::fpr, mlr::fnr, mlr::tpr, mlr::tnr, mlr::auc, mlr::ppv),
                                             gridsize = 100L,
                                             aggregate = TRUE 
                                             )

# Plot -------------------------------------------------------------


# False Negative Rate vs True Negative Rate 

ft_neg_test<-plotROCCurves(obj = thresh_vs_perf_test,
              measures = list(fnr, tnr) )+      
              ggtitle(paste0("False Negative Rate vs True Negative Rate, Test Performance, ", samplecount_test))+
              theme(plot.title = element_text(size = 10))

# ROC - Sensitivity and Specificity curve 

ft_pos_test<-plotROCCurves(obj = thresh_vs_perf_test,
              measures = list(fpr, tpr) )+      
               ggtitle(paste0("ROC - Sensitivity-Specifificty Curve, Test Performance, ", samplecount_test))+
                 theme(plot.title = element_text(size = 10))
# Precision/Recall

prec_recall_test<-plotROCCurves(thresh_vs_perf_test, measures = list(tpr, ppv), diagonal = FALSE)+      
                    ggtitle(paste0("Precision-Recall Curve, Test Performance, ", samplecount_test))+
                    theme(plot.title = element_text(size = 10))


# Plots - Perf vs thresh --------------
ThreshvsPerf_plots_test<-plotThreshVsPerf(thresh_vs_perf_test)


# Produced Plots -------------------

ft_neg_test 

ft_pos_test 

prec_recall_test

ThreshvsPerf_plots_test

```



## Results PLots 
```{r}

# sensitivity 

plot_test_sensi
plot_test_sensi_all


# plots 
ft_neg_test
ft_pos_test


prec_recall_test
ThreshvsPerf_plots_test

```

## Results Summary 
```{r}
    
print(paste0("Sensivity point performance across multi thresholds on aggregated training data"))

test_perf_confmat_allthresh$Performance


print(paste0("Confusion Matrix across multi thresholds on aggregated training data"))

test_perf_confmat_allthresh$ConfusionMat



# Obtained Objects 
print(paste0("Test Performance (Threshold of ", desired_prob_thresh, ")"))

test_perf

print(paste0("Test Confusion Matrix (Threshold of ", desired_prob_thresh, ")"))

test_confmat


```

# Joint Summary 
```{r}


temp<-test_perf
colnames(temp)[1]<-paste0("Test_", colnames(test_perf)[1])


temp2<-cv_perf_agg
colnames(temp2)[1]<-paste0("CV_agg_", colnames(cv_perf_agg)[1])


temp3<-test_confmat
colnames(temp3)[3]<-paste0("Test_", colnames(test_perf)[1])

temp4<-cv_confmat_agg
colnames(temp4)[3]<-paste0("CV_agg_", colnames(cv_perf_agg)[1])



# Merge test and training performance metrics and desired threshold 
performance_summary_desiredthresh<-cbind(temp, temp2)


# Merge test and training performance metrics and desired threshold 
confmat_summary_desiredthresh<-full_join(temp3, temp4)




# Produced objects 
performance_summary_desiredthresh


confmat_summary_desiredthresh
```








# CLOSING ------------------
### Save Object Sizes ***Specify Objects***
```{r}



objects_created <- c( "tunedSvmPars", 
                               "tunedSvmModel", 
                               "svm_cv_method_val",
                               "thresh_sensi_top", # Based on F1 and/or Recall From Class. Seni. Analysis 
                               "thresh_sensi_bot")# Based on Negative Predictive Value and/or Specificity from Class seni analysis 


reccord_dim <- function(objects) {
  
  result <- list()
  
  for (obj_name in objects) {
    
    if (exists(obj_name)) {
      
      obj <- get(obj_name)
      
      if (is.data.frame(obj) || is.matrix(obj)) {
        
        rows <- nrow(obj)
        cols <- ncol(obj)
        result[[obj_name]] <- list(rows = rows, cols = cols)
        
      } else {
        
        warning(paste("Object labeled ", obj_name, "is not a data frame or a matrix. Skipping."))
      }
      
    } else {
      
      warning(paste("Object", obj_name, "does not exist. Skipping."))
      
    }
  }
  return(result)
}

objects_dim_list<-reccord_dim(objects_created)




#          Summary --------------------------------------------- 

print("Created Objects Summary:")
print(objects_dim_list)

```


### Exporting and Clean Up - Part 1/2
```{r}
#           Create Output File ------------------------------------------------------


current_output_folder<-paste0(script_name_base, "_", run_timestamp, ".Rmd")

dir.create(current_output_folder)

script_path_with_output_folder <- file.path(script_path_folder, 
                                            current_output_folder)

setwd(script_path_with_output_folder) # need to restate for each code chunk

#           Export Executed Code ----------------------------------------------------

copy_and_output_code <- function(script_path) {
  if (file.exists(script_path)) {
    
    rstudioapi::documentSave()
    
    script_content <- readLines(script_path)
    
    writeLines(script_content, current_output_folder)
  } else {
    message("Error: The specified script path does not exist.")
  }
}

# Call the function to copy and export the code
copy_and_output_code(script_path_current)

#           Export Run Info ---------------------------------------------------------

writeLines(capture.output(run_sessionInfo), "sessionInfo.txt")

```

### Exporting and Clean Up - Part 2/2 **Specify Objects**
```{r}

setwd(script_path_with_output_folder) # need to restate for each code chunk

#           Export Objects as .rda - **SPECIFY OBJECTS**----------------------------------------------------

objects_save<-c( objects_created, "objects_dim_list")

                            
save(list=objects_save,                   
     file = "env_obj.rda")

#           Export Tables/Genes Individually- **SPECIFY OBJECTS** ----------------------------------------

    write_lines(tunedSvmPars, "tunedSvmPars.txt" )
    write_lines(tunedSvmModel, "tunedSvmModel.txt")


# Sensitivity Analysis 

sensi_plot_names<-c("plot_cv_agg_sensi", 
                    "plot_cv_agg_sensi_all",
                    "plot_test_sensi",
                    "plot_test_sensi_all")

        dir.create("Results_Sensitivity", recursive = TRUE, showWarnings = FALSE)
        
        for (nm in sensi_plot_names) {
          ggsave(
            filename = file.path("Results_Sensitivity", paste0(nm, ".pdf")),
            plot = get(nm)
          )
        }

# CV Performance Curves
        
       cv_plot_names <- c( # Aggregated performance plots (on desired thresh)

                          "ft_neg_agg_cv",
                          "ft_pos_agg_cv",
                          "prec_recall_agg_cv",
                          
                          # Per Iteration performance plots (on desired thresh)
                          "ft_neg_cv",
                          "ft_pos_cv",
                          "prec_recall_cv"
                        )

        dir.create("Results_CV/Plots", recursive = TRUE, showWarnings = FALSE)
        
            
        ggsave(
            filename = file.path("Results_CV/Plots", "ThreshvsPerf_plots_iter_cv.pdf"),
            plot = ThreshvsPerf_plots_iter_cv, units = "in", width = 10, height = 8
          )
            
        for (nm in cv_plot_names) {
          ggsave(
            filename = file.path("Results_CV/Plots", paste0(nm, ".pdf")),
            plot = get(nm)
          )
        }

# Testing Performance Curves
        
                        
      test_plot_names<-c(
                        "ft_neg_test",
                        "ft_pos_test",
                        
                        
                        "prec_recall_test")

          dir.create("Results_Test/Plots", showWarnings = FALSE, recursive = TRUE)
        
            
        ggsave(
            filename = file.path("Results_Test/Plots", "ThreshvsPerf_plots_test.pdf"),
            plot = ThreshvsPerf_plots_test, units = "in", width = 10, height = 8
          )
        
        
        for (nm in test_plot_names) {
          ggsave(
            filename = file.path("Results_Test/Plots", paste0(nm, ".pdf")),
            plot = get(nm)
          )
        }
          
      

# Learning Curves
          

    learn_plot_names <- c("acc_agg_plot_withlegend", "mmce_agg_plot_withlegend",
                              "acc_agg_plot",
                              "mmce_agg_plot",
                              "tpr_agg_plot",
                              "fpr_agg_plot",
                              "tnr_agg_plot",
                              "fnr_agg_plot"
                            )

          dir.create("Results_Learning", showWarnings = FALSE, recursive = TRUE)
          
                  for (nm in learn_plot_names) {
                    ggsave(
                      filename = file.path("Results_Learning", paste0(nm, ".pdf")),
                      plot = get(nm), units = "in", width =3, height = 3
                    )
                  }
          
      

# Performance vs thresh 
    
    
    
# Export CSV
  

# Sensitivity Performance 
write.csv(cv_perf_confmat_allthresh$Performance, 
          file = file.path("Results_Sensitivity","cv_perf_confmat_allthresh_Performance.csv"), 
          row.names = TRUE)

write.csv(cv_perf_confmat_allthresh$ConfusionMat, 
          file = file.path("Results_Sensitivity","cv_perf_confmat_allthresh_ConfusionMat.csv"), 
          row.names = TRUE)


write.csv(test_perf_confmat_allthresh$Performance, 
          file = file.path("Results_Sensitivity", "test_perf_confmat_allthresh_Performance.csv"), 
          row.names = TRUE)

write.csv(test_perf_confmat_allthresh$ConfusionMat, 
          file = file.path("Results_Sensitivity","test_perf_confmat_allthresh_ConfusionMat.csv"), 
          row.names = TRUE)





# CV Performance Aggregated
write.csv(cv_perf_agg, 
          file = file.path("Results_CV", "cv_perf_agg.csv"),
          row.names = TRUE)
    
write.csv(cv_confmat_agg, 
          file = file.path("Results_CV", "cv_confmat_agg.csv"),
          row.names = TRUE)
    

# CV Performance Per Iteration
write.csv(cv_perf_per_iter, 
          file = file.path("Results_CV", "cv_perf_per_iter.csv"),
          row.names = TRUE)
    
write.csv(cv_confmat_per_iter, 
          file = file.path("Results_CV", "cv_confmat_per_iter.csv"),
          row.names = TRUE)
    


# Test Performance

write.csv(test_perf, 
          file = file.path("Results_Test", "test_perf.csv"), 
          row.names = TRUE)  # keeps the metric names as the first column

write.csv(test_confmat, 
          file = file.path("Results_Test", "test_confmat.csv"), 
          row.names = TRUE)  # keeps the metric names as the first column




# Joint SUmmary 

write.csv(performance_summary_desiredthresh, 
          file = "performance_summary_desiredthresh.csv", 
          row.names = TRUE)  # keeps the metric names as the first column

write.csv(confmat_summary_desiredthresh, 
          file =  "confmat_summary_desiredthresh.csv", 
          row.names = TRUE)  # keeps the metric names as the first column


# Read CSV files in folder
CSV_Files <- list.files(path = script_path_with_output_folder, pattern = ".csv$")

# Zip the files
zip::zip(zipfile = "exported_objects.zip", files = CSV_Files)

#Remove CSV files
file.remove(CSV_Files)


 
```


### Clear Env./Re-Add Generated Objects
```{r}
setwd(script_path_with_output_folder) # need to restate for each code chunk

#           Clear Environment/Re-Add Generated Objects  ------------------------------------------------------


#clear environment
rm(list = ls()) #USE VERY CAREFULLY ONLY ACTIVATE AT END OF PIPELINE
# rm(list = objects_save)

#readd the objects
#load("env_obj.rda")


```
