---
title: "2_correlations"
author: "Dali_Nemecio"
date: "`r Sys.Date()`"
output: html_document
---

This script will generate host-omic-microbe spearman correlations only. It does NOT use bootstrapping to generate these correlations, and therefore does NOT require the 10 DF generations for noise reduction as done in the original TV-SVM pipeline. 


# SET UP MAC ---------------------------------------------------------------------
## Library 
```{r, eval=TRUE}
# #           Load Library **SPECIFY**------------------------------------------------------------
 packages_needed<-c(
                    "rstudioapi", 
                    "tidyverse") 
  for (pkg in packages_needed){
 if ( !require(pkg, character.only = TRUE)){
   library(pkg, character.only = TRUE)
 } 
 }
```

## Script Info and Dir
```{r, eval=TRUE}
#           Collect Script Info and Change To Script Directory ---------------

# Script Directory
 script_path_current <- getSourceEditorContext()$path
 script_path_folder<-sub("/[^/]*$", "", script_path_current)
 script_name<-sub(".*/", "", script_path_current)
 script_name_base<-sub("\\..*$", "", script_name)

# Change directory in all code chunks to current script location
 knitr::opts_knit$set(root.dir = script_path_folder)

#           Collect Run Info------------------------------------------- 
 run_timestamp <- format(Sys.time(), "%Y_%m_%d_%H%M")
 
 run_sessionInfo<-sessionInfo()
# 
```

## Shortcuts
```{r, eval=TRUE}
source("/Users/dalinemecio/Documents/1_Rotations/Brubaker/R/x_smaller_folders/short_cuts/short_cuts.R")
```

## Load Data and Objects Required 
### Data Prev Folder 
```{r, eval=TRUE}

# Load Data - Collect .rda files ----------------------------------------

# Find Previous Code Folder -----------------------------

# Find the last slash
last_slash <- max(gregexpr("/", script_path_folder)[[1]])

# Extract the substring
substring_after_last_slash <- substr(script_path_folder, last_slash + 1, nchar(script_path_folder))

# Extract the first number
first_number <- regmatches(substring_after_last_slash, regexpr("[0-9]+", substring_after_last_slash))

# Convert the first number to an integer and subtract 1
new_number <- as.integer(first_number) - 1

# Construct the new path
new_path <- paste0(
  substr(script_path_folder, 1, last_slash),
  new_number,
  "_*"
)

# Function to find directory matching the pattern
find_directory <- function(path_with_wildcard) {
  
  # Extract directory path without wildcard
  directory_path <- dirname(path_with_wildcard)
  
  # List files matching the pattern
  matching_files <- list.files(directory_path, pattern = basename(path_with_wildcard))
  
  # Check if any matching directory exists
  matching_directories <- matching_files[dir.exists(file.path(directory_path, matching_files))]
  
  if (length(matching_directories) > 0) {
    
    return(file.path(directory_path, matching_directories[1]))
    
  } else {
    return(NULL)
  }
}

# Find the actual directory matching the wildcard
rda_directory <- find_directory(new_path)

# Load .rda files ---------------------------------

# Get list of all .rda files recursively
rda_files <- list.files(
  path = rda_directory,
  pattern = "\\.rda$",
  recursive = TRUE,
  full.names = TRUE
)

# *NEW* objects before loading .rda from previous folder
objects_beforeload <- ls()

# Load each .rda file
for (file in rda_files) {
  load(file)
}

# NEW* objects obtains from load

objects_afterload <- ls()

# Check Object dim by hand ---------------------------------
# A little redundant
loaded_obj <- setdiff(objects_afterload, objects_beforeload)
loaded_obj <- loaded_obj[!loaded_obj %in% c("file", "objects_beforeload")]

print("OBJECTS LOADED AND DIMENSIONS ")

for (obj_name in loaded_obj) {
  obj <- get(obj_name)  # get the actual object from its name
  dims <- if (!is.null(dim(obj))) dim(obj) else length(obj)
  print(paste0(obj_name, " Dim: ", paste(dims, collapse = " x ")))
}

# Collect starting Envr. ---------------------------------

objects_starting <- ls()
```


### Check Input Object Sizes 
```{r, Check Input Object Sizes - Previous File, eval=TRUE}
dim_check <- list()
has_mismatch <- FALSE

for (obj_name in objects_starting) {
  if (obj_name %in% names(objects_dim_list)) {
    correct_dimensions <- objects_dim_list[[obj_name]]
    actual_object <- get(obj_name)
    actual_dimensions <- list(rows = nrow(actual_object), cols = ncol(actual_object))
    
    if (identical(correct_dimensions, actual_dimensions)) {
      dim_check[[obj_name]] <- "Dimensions match"
    } else {
      mismatch_msg <- "Dimensions mismatch:"
      if (correct_dimensions$rows != actual_dimensions$rows) {
        mismatch_msg <- paste(mismatch_msg, "Expected rows is", correct_dimensions$rows,
                              "actual is", actual_dimensions$rows)
      }
      if (correct_dimensions$cols != actual_dimensions$cols) {
        mismatch_msg <- paste(mismatch_msg, "Expected columns is", correct_dimensions$cols,
                              "actual is", actual_dimensions$cols)
      }
      dim_check[[obj_name]] <- mismatch_msg
      has_mismatch <- TRUE
    }
  }
}

print(dim_check)

if (has_mismatch) {
  stop("There is at least one object with mismatched dimensions.")
} else {
  "No mismatch in loaded object sizes, continue code execution."
}

```

# Host-omic-microbe Correlations  ---------------------------------- 

```{r, corr}

# Define Input Data --------------------------------------------------------------

                    input1_RNA<-as.matrix(trans_data_share) 
                    input2_mbiocomp<-as.matrix(mbio_taxo_clean) 


# Spearman Correlation - GENERATE HOST-MICROBE OMIC CORR ---------------------------

                      microbes_vs_genes_corr_loop<-suppressWarnings(cor(input2_mbiocomp, input1_RNA, method = "spearman", use = "pairwise.complete.obs")) # KEYSTONE 
                      microbes_vs_genes_corr_loop<-as.data.frame(microbes_vs_genes_corr_loop) # to retain microbe names
                
                    
```

# Closing-------------------------------------
### Save Object Sizes ***Specify Objects***
```{r}


objects_created <- c("microbes_vs_genes_corr_loop")



reccord_dim <- function(objects) {
  
  result <- list()
  
  for (obj_name in objects) {
    
    if (exists(obj_name)) {
      
      obj <- get(obj_name)
    
        # If it's a list, check first element
    if (is.list(obj) && !is.data.frame(obj) && !is.matrix(obj)) {
      obj <- obj[[1]]
    }
    
    if (is.data.frame(obj) || is.matrix(obj)) {
      result[[obj_name]] <- list(
        rows = nrow(obj),
        cols = ncol(obj)
      )
    } else {
        
        warning(paste("Object labeled ", obj_name, "is not a data frame or a matrix, or a list, Skipping."))
      }
      
    } else {
      
      warning(paste("Object", obj_name, "does not exist. Skipping."))
      
    }
  }
  return(result)
}

objects_dim_list<-reccord_dim(objects_created)


print("CREATED OBJECT DIMENSIONS AS FOLLOWS :")
print(objects_dim_list)
      

```


### Exporting and Clean Up - Part 1/2
```{r}
#           Create Output File ------------------------------------------------------


current_output_folder<-paste0(script_name_base, "_", run_timestamp, ".Rmd")

dir.create(current_output_folder)

script_path_with_output_folder <- file.path(script_path_folder, 
                                          current_output_folder)


#           Export Run Info ---------------------------------------------------------

writeLines(capture.output(run_sessionInfo), file.path(script_path_with_output_folder, "sessionInfo.txt"))

```


### Exporting and Clean Up - Part 2/2 **Specify Objects**
```{r}

setwd(script_path_with_output_folder) # need to restate for each code chunk

#           Export Objects as .rda - **SPECIFY OBJECTS**----------------------------------------------------

objects_save<-c( objects_created, "objects_dim_list")

                            
save(list=objects_save,                   
     file = file.path(script_path_with_output_folder, "env_obj.rda")) 


 
```


# End ---------------------------------------------------------------------
