---
title: "lincs_multi"
author: "Dali_Nemecio"
date: "`r Sys.Date()`"
output: 
  html_document:
    code_folding: hide
---

T Test on the test data partitioned out. From the selected 500 features we will filter the test, train and to be predicted on data. 
 
## Start ---------------------------------------------------------------------

```{r , include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Library
```{r}
# Load Library **SPECIFY** -------------------------------------

  packages_needed<-c("tidyverse",
                     "tibble", 
                     "dplyr",
                     "rstudioapi") 
  
  for (pkg in packages_needed){
  if ( !require(pkg, character.only = TRUE)){
    library(pkg, character.only = TRUE)
  } 
  }

# Collect Script Info and Change To Script Directory ---------------


  #Script Directory
  script_path_current <- getSourceEditorContext()$path
  script_path_folder<-sub("/[^/]*$", "", script_path_current)
  script_name<-sub(".*/", "", script_path_current)
  script_name_base<-sub("\\..*$", "", script_name)
  
  #Change directory in all code chunks to current script location
  knitr::opts_knit$set(root.dir = script_path_folder)
   

# Collect Run Info ------------------------------------------- 
  
  run_timestamp <- format(Sys.time(), "%Y_%m_%d_%H%M")
  
  run_sessionInfo<-sessionInfo()

```

## Shortcuts
```{r}
source("/Users/dalinemecio/Documents/1_Rotations/Brubaker/R/x_smaller_folders/short_cuts/short_cuts.R")
```

## Load Data and Objects Required
```{r}
# Load Data - Collect .rda files ----------------------------------------

# Find Previous Code Folder -----------------------------
    
    # Find the last slash
    last_slash <- max(gregexpr("/", script_path_folder)[[1]])
    
    # Extract the substring
    substring_after_last_slash <- substr(script_path_folder, last_slash + 1, nchar(script_path_folder))
    
    # Extract the first number
    first_number <- regmatches(substring_after_last_slash, regexpr("[0-9]+", substring_after_last_slash))
    
    # Convert the first number to an integer and subtract 1
    new_number <- as.integer(first_number) - 1
    
    # Construct the new path
    new_path <- paste0(
      substr(script_path_folder, 1, last_slash),
      new_number,
      "_*"
    )
    
    # Function to find directory matching the pattern
    find_directory <- function(path_with_wildcard) {
            
            # Extract directory path without wildcard
            directory_path <- dirname(path_with_wildcard)
            
            # List files matching the pattern
            matching_files <- list.files(directory_path, pattern = basename(path_with_wildcard))
            
            # Check if any matching directory exists
            matching_directories <- matching_files[dir.exists(file.path(directory_path, matching_files))]
            
            if (length(matching_directories) > 0) {
              
              return(file.path(directory_path, matching_directories[1]))
              
            } else {
              return(NULL)
            }
    }
    
    # Find the actual directory matching the wildcard
    rda_directory <- find_directory(new_path)

# Load .rda files  ---------------------------------

# Get list of all .rda files recursively
    rda_files <- list.files(path = rda_directory, 
                        pattern = "\\.rda$",
                        recursive = TRUE,
                        full.names = TRUE)

# Load each .rda file
    for (file in rda_files) {
      load(file)
    }


# Collect starting Envr.  ---------------------------------

objects_starting<-ls()

```


## Check Input Object Sizes

```{r}

dim_check <- list()
has_mismatch <- FALSE  # Variable to track if there's a mismatch

for (obj_name in objects_starting) {
  if (obj_name %in% names(objects_dim_list)) {
    correct_dimensions <- objects_dim_list[[obj_name]]
    actual_object <- get(obj_name)
    actual_dimensions <- list(rows = nrow(actual_object), cols = ncol(actual_object))
    
    if (identical(correct_dimensions, actual_dimensions)) {
      dim_check[[obj_name]] <- "Dimensions match"
    } else {
      # Construct the mismatch message
      mismatch_msg <- "Dimensions mismatch:"
      if (correct_dimensions$rows != actual_dimensions$rows) {
        mismatch_msg <- paste(mismatch_msg, "Expected rows is", correct_dimensions$rows,
                              "actual is", actual_dimensions$rows)
      }
      if (correct_dimensions$cols != actual_dimensions$cols) {
        mismatch_msg <- paste(mismatch_msg, "Expected columns is", correct_dimensions$cols,
                              "actual is", actual_dimensions$cols)
      }
      # Store the mismatch message in dim_check
      dim_check[[obj_name]] <- mismatch_msg
      has_mismatch <- TRUE  # Set has_mismatch to TRUE if there's a mismatch
    }
  }
}

# Print the output
print(dim_check)

# Check if there's a mismatch and stop if true
if (has_mismatch) {
  stop("There is at least one object with mismatched dimensions.")
}  else {"No mismatch in loaded object sizes, continue code execution." }

```

# MAIN -------------
# Prep for T-test 
```{r}

# Input entering Data 

    enter_sig<-Master_MHG_corr_sig_train
    

# Filter for TV state = -1 or +1 ----------------------------------

    drug_known_ttest<- enter_sig%>%
                          filter(state== -1 |state== 1 )
            
# Define TRaining Data and Variables -----------------------------------

# Define Indexs
    gene_index_start <- which(colnames(drug_known_ttest) == "A1CF")
        
    gene_index_end <- which(colnames(drug_known_ttest) == "ZZZ3")
  
    select_set<-drug_known_ttest
    
            
             
# Define TV +1 rows 
    pos1<-select_set%>%
            filter(select_set$state == 1)
          
# Define TV -1 rows
    neg1<-select_set%>%
            filter(select_set$state == -1)
            

# Empty Data frame For T Test Results ---------------------------------------
      
    results_build <- data.frame(
                                  gene = character(0),
                                  p_value = numeric(0),
                                  neg1_group_mean = numeric(0),
                                  pos1_group_mean = numeric(0),
                                  conf_int_low = numeric(0),
                                  conf_int_high = numeric(0),
                                  t_value = numeric(0),
                                  degrees_of_freedom = numeric(0) )


```


# T test
```{r}
# Enter T test for loop -------------------------------------------

# Begin  Loop

  for (y in gene_index_start:gene_index_end){
         print(paste0("enter inner loop/iterate through columns y: ", y))
        if (y == gene_index_start) {
          print(paste0("enter inner loop/iterate through columns "))} 
    
    # Select Col Values         
    pos1_col<-pos1[,y]
    neg1_col<-neg1[,y]
    
    if( all(is.na(pos1_col)) && all(is.na(neg1_col))) {
      
      next
      
    }else{
      
      # Check is Col names are the same 
      if ( isTRUE( names(pos1)[y] == names(neg1)[y] )) {
        
        # Run Welches T test 
        results<-t.test(pos1_col, neg1_col, alternative = c("two.sided"), var.equal = FALSE) # KEYSTONE 
        
        # Add results to t_test results table
        results_loop<-data.frame(gene = names(pos1)[y],
                                 p_value = results$p.value,
                                 neg1_group_mean = mean(neg1_col),
                                 pos1_group_mean = mean(pos1_col),
                                 conf_int_low = results$conf.int[1],
                                 conf_int_high = results$conf.int[2],
                                 t_value = results$statistic,
                                 degrees_of_freedom = results$parameter)
        
        results_build <- rbind(results_build,results_loop)
        
        
      } else {
        print(paste("Column Index:", y,  "---Gene names do not match, will not run t test"))
        break
      }
      
      }
    
        if (names(select_set)[y] == gene_index_end){
      print(paste(" All colums cor. calc :)"))
    }
    
  } #end of t test looping through columns
  

# Rename results 
  ttest_results<-results_build

# Produced Objects --------------------------------------

paste0("Dimensions of ttestresults :", d(ttest_results)[1], " X ", d(ttest_results)[2])

```

## FDR
```{r}
# Temp Rename 
      result_df<-ttest_results
  
# Get adjusted values vector
      adj_p_value<-p.adjust(result_df$p_value, method = "BH")  # KEYSTONE
      
# Add to t test results 
      
      result_df$adj_p_value<-adj_p_value
      
      building<-result_df%>%
                    select(c(gene, adj_p_value, p_value,
                            neg1_group_mean, pos1_group_mean,
                            conf_int_low, conf_int_high,
                            t_value, degrees_of_freedom))
  
# Rename P val adjusted results
ttest_results<-building


```

# Results 
## Select Top 500 Genes  
```{r}

list_arr_fxn<- function(df){
  
  
           df<-as.data.frame(df)
            newdf_adj<-df %>%
                  arrange(adj_p_value)%>%
                  head(500)
            
            # If there are multiple unique adjusted p values in top 500 select top 500 based on adjusted p values
            if(l(u(newdf_adj$adj_p_value))>=2){
              
              
            print("Top 500 selected based on adjusted p values only.")
            return(newdf_adj)
              
            # If there is only one unique adjusted p values select top 500 based on standard p values
            }else{
              
              
            newdf_pval<-df %>%
                  arrange(p_value)%>%
                  head(500)
            
            print("Top 500 selected based on p values only.")
            return(newdf_pval)
            
            }
            
            
            

            
            
            
            }

top_500_summary<-list_arr_fxn(ttest_results)


```

# Filter Test, Train and To Predict data for 500 Features 

```{r}

Master_MHG_corr_sig_train_500<-Master_MHG_corr_sig_train%>%
                dplyr::select(microbe, drug, state, all_of(top_500_summary$gene))

Master_MHG_corr_sig_NA_500<-Master_MHG_corr_sig_NA%>%
                dplyr::select(microbe, drug, state, all_of(top_500_summary$gene))

Master_MHG_corr_sig_test_500<-Master_MHG_corr_sig_test%>%
                dplyr::select(microbe, drug, state, all_of(top_500_summary$gene))

```



# CLOSING ------------------
### Save Object Sizes ***Specify Objects***
```{r}


objects_created <- c( 
                      "top_500_summary",  # 500 8   of top 500 summary 
                      "Master_MHG_corr_sig_train_500", # contains select features 500
                      "Master_MHG_corr_sig_NA_500", 
                      "Master_MHG_corr_sig_test_500"
                       )

reccord_dim <- function(objects) {
  
  result <- list()
  
  for (obj_name in objects) {
    
    if (exists(obj_name)) {
      
      obj <- get(obj_name)
      
      if (is.data.frame(obj) || is.matrix(obj)) {
        
        rows <- nrow(obj)
        cols <- ncol(obj)
        result[[obj_name]] <- list(rows = rows, cols = cols)
        
      } else {
        
        warning(paste("Object labeled ", obj_name, "is not a data frame or a matrix. Skipping."))
      }
      
    } else {
      
      warning(paste("Object", obj_name, "does not exist. Skipping."))
      
    }
  }
  return(result)
}

objects_dim_list<-reccord_dim(objects_created)




#          Summary --------------------------------------------- 

print("Created Objects Summary:")
print(objects_dim_list)

```


### Exporting and Clean Up - Part 1/2
```{r}
#           Create Output File ------------------------------------------------------


current_output_folder<-paste0(script_name_base, "_", run_timestamp, ".Rmd")

dir.create(current_output_folder)

script_path_with_output_folder <- file.path(script_path_folder, 
                                            current_output_folder)

setwd(script_path_with_output_folder) # need to restate for each code chunk

#           Export Executed Code ----------------------------------------------------

copy_and_output_code <- function(script_path) {
  if (file.exists(script_path)) {
    
    rstudioapi::documentSave()
    
    script_content <- readLines(script_path)
    
    writeLines(script_content, current_output_folder)
  } else {
    message("Error: The specified script path does not exist.")
  }
}

# Call the function to copy and export the code
copy_and_output_code(script_path_current)

#           Export Run Info ---------------------------------------------------------

writeLines(capture.output(run_sessionInfo), "sessionInfo.txt")

```

### Exporting and Clean Up - Part 2/2 **Specify Objects**
```{r}

setwd(script_path_with_output_folder) # need to restate for each code chunk

#           Export Objects as .rda - **SPECIFY OBJECTS**----------------------------------------------------

objects_save<-c( objects_created, "objects_dim_list")

                            
save(list=objects_save,                   
     file = "env_obj.rda")
 
```


### Clear Env./Re-Add Generated Objects
```{r}
setwd(script_path_with_output_folder) # need to restate for each code chunk

#           Clear Environment/Re-Add Generated Objects  ------------------------------------------------------


#clear environment
rm(list = ls()) #USE VERY CAREFULLY ONLY ACTIVATE AT END OF PIPELINE
# rm(list = objects_save)

#readd the objects
load("env_obj.rda")


```
