---
title:  "prediction_GeneExpxMic-Gene.Rmd"
author: "Dali_Nemecio"
date: "`r Sys.Date()`"
output: 
  html_document:
    code_folding: hide
---

Pipeline Summary 

1. 15/20 patients were randomly selected to generate the training data. 5/20 patients were randomly selected to generate the testing data. Each patient set were used to bootstrapp microbe-gene correlations which were then multiplied by LINCS CD. This included non metabolic, metabolic, and unknown microbe-gene relationships (-1, +1, NA) 
2. The pre-training data is bootstrapped for 100 iterations, 10 times to generate a list of 10 dataframes. 
2. Each dataframe in the list undergoes a t-test for feature selection; top 500 features shared across all 10 dataframes are retained selected to define the MDH signature  
5. Using t-test identified features, we then train the model with the first dataframe from the training list of dataframes. 
6. Prediction with the generated model is done on all testing, training, and unknown data types. Both bootstrapped data and raw patient MDH values are predicted on here. The paper only contains the raw patient MDH predictions. 
  
# Set up 
## Library and Shortcuts 
```{r}
# Set Up - Section 1 -------------------------------------------------------
#           rmd set up----------------------------------------
knitr::opts_chunk$set(echo = TRUE)


#           Load Library **SPECIFY**------------------------------------------------------------
packages_needed<-c("knitr",
                   "tidyverse",
                   "tibble", 
                   "dplyr",
                   "rstudioapi", 
                   "mlr")  


for (pkg in packages_needed){
if ( !require(pkg, character.only = TRUE)){
  library(pkg, character.only = TRUE)
} 
     
}



#           Collect Script Info and Change To Script Directory ---------------


#Script Directory
script_path_current <- getSourceEditorContext()$path
script_path_folder<-sub("/[^/]*$", "", script_path_current)
script_name<-sub(".*/", "", script_path_current)
script_name_base<-sub("\\..*$", "", script_name)
#Change directory in all code chunks to current script location

knitr::opts_knit$set(root.dir = script_path_folder)
 

#           Collect Run Info------------------------------------------- 
run_timestamp <- format(Sys.time(), "%Y_%m_%d_%H%M")

run_sessionInfo<-sessionInfo()


#           Shortcut Custom functions --------------------------------------------------------


v <- function(data) {
  tab_name <- deparse(substitute(data))
  View(data, title = tab_name)
}

d<-function(data){
  dim(data)
}

l<-function(data){
  length(data)
}

u<-function(data){
  unique(data)
}

h<-function(data){
  head(data)
}

t<-function(data){
  tail(data)
}


# End Set up

```

## Load Data and Objects Required

```{r}
# Load Data - Collect .rda files ----------------------------------------

#       Find Previous Code Folder -----------------------------

# Find the last slash
last_slash <- max(gregexpr("/", script_path_folder)[[1]])

# Extract the substring
substring_after_last_slash <- substr(script_path_folder, last_slash + 1, nchar(script_path_folder))

# Extract the first number
first_number <- regmatches(substring_after_last_slash, regexpr("[0-9]+", substring_after_last_slash))

# Convert the first number to an integer and subtract 1
new_number <- as.integer(first_number) - 1

# Construct the new path
new_path <- paste0(
  substr(script_path_folder, 1, last_slash),
  new_number,
  "_*"
)

# Function to find directory matching the pattern
find_directory <- function(path_with_wildcard) {
  
  # Extract directory path without wildcard
  directory_path <- dirname(path_with_wildcard)
  
  # List files matching the pattern
  matching_files <- list.files(directory_path, pattern = basename(path_with_wildcard))
  
  # Check if any matching directory exists
  matching_directories <- matching_files[dir.exists(file.path(directory_path, matching_files))]
  
  if (length(matching_directories) > 0) {
    
    return(file.path(directory_path, matching_directories[1]))
    
  } else {
    return(NULL)
  }
}

# Find the actual directory matching the wildcard
rda_directory <- find_directory(new_path)



#       Load .rda files  ---------------------------------
         

# Get list of all .rda files recursively
rda_files <- list.files(path = rda_directory, 
                        pattern = "\\.rda$",
                        recursive = TRUE,
                        full.names = TRUE)

# Load each .rda file
for (file in rda_files) {
  load(file)
}

           
#       Collect starting Envr.  ---------------------------------

objects_starting<-ls()


```

## Check Input Object Sizes

```{r}

dim_check <- list()
has_mismatch <- FALSE  # Variable to track if there's a mismatch

for (obj_name in objects_starting) {
  if (obj_name %in% names(objects_dim_list)) {
    correct_dimensions <- objects_dim_list[[obj_name]]
    actual_object <- get(obj_name)
    actual_dimensions <- list(rows = nrow(actual_object), cols = ncol(actual_object))
    
    if (identical(correct_dimensions, actual_dimensions)) {
      dim_check[[obj_name]] <- "Dimensions match"
    } else {
      # Construct the mismatch message
      mismatch_msg <- "Dimensions mismatch:"
      if (correct_dimensions$rows != actual_dimensions$rows) {
        mismatch_msg <- paste(mismatch_msg, "Expected rows is", correct_dimensions$rows,
                              "actual is", actual_dimensions$rows)
      }
      if (correct_dimensions$cols != actual_dimensions$cols) {
        mismatch_msg <- paste(mismatch_msg, "Expected columns is", correct_dimensions$cols,
                              "actual is", actual_dimensions$cols)
      }
      # Store the mismatch message in dim_check
      dim_check[[obj_name]] <- mismatch_msg
      has_mismatch <- TRUE  # Set has_mismatch to TRUE if there's a mismatch
    }
  }
}

# Print the output
print(dim_check)

# Check if there's a mismatch and stop if true
if (has_mismatch) {
  stop("There is at least one object with mismatched dimensions.")
}  else {"No mismatch in loaded object sizes, continue code execution." }

```

## Obtain Objects from folder 1\_\*

```{r}
#       Find Object Code Folder 1_* -----------------------------------

        other_folder_number<-1

        # Construct the new path

        more_objects_path <- paste0(
          substr(script_path_folder, 1, last_slash),
          other_folder_number,
          "_*"
        )
        
        more_objects_path_defined<-find_directory(more_objects_path)
        
        
# Get objects from other 3_* folder 

rda_files<-list.files(path = more_objects_path_defined, 
                          pattern = "\\.rda$",
                          recursive = TRUE,
                          full.names = TRUE) 
   


# Load each .rda file in 3_* folder 
for (file in rda_files) {
  load(file)
}
        

#get downloaded objects 
objects_starting<-ls()

```



## Check Input Object Sizes

```{r}

dim_check <- list()
has_mismatch <- FALSE  # Variable to track if there's a mismatch

for (obj_name in objects_starting) {
  if (obj_name %in% names(objects_dim_list)) {
    correct_dimensions <- objects_dim_list[[obj_name]]
    actual_object <- get(obj_name)
    actual_dimensions <- list(rows = nrow(actual_object), cols = ncol(actual_object))
    
    if (identical(correct_dimensions, actual_dimensions)) {
      dim_check[[obj_name]] <- "Dimensions match"
    } else {
      # Construct the mismatch message
      mismatch_msg <- "Dimensions mismatch:"
      if (correct_dimensions$rows != actual_dimensions$rows) {
        mismatch_msg <- paste(mismatch_msg, "Expected rows is", correct_dimensions$rows,
                              "actual is", actual_dimensions$rows)
      }
      if (correct_dimensions$cols != actual_dimensions$cols) {
        mismatch_msg <- paste(mismatch_msg, "Expected columns is", correct_dimensions$cols,
                              "actual is", actual_dimensions$cols)
      }
      # Store the mismatch message in dim_check
      dim_check[[obj_name]] <- mismatch_msg
      has_mismatch <- TRUE  # Set has_mismatch to TRUE if there's a mismatch
    }
  }
}

# Print the output
print(dim_check)

# Check if there's a mismatch and stop if true
if (has_mismatch) {
  stop("There is at least one object with mismatched dimensions.")
}  else {"No mismatch in loaded object sizes, continue code execution." }

```
## Obtain Objects from folder 2\_\*

```{r}
#       Find Object Code Folder 2_* -----------------------------------

        other_folder_number<-2

        # Construct the new path

        more_objects_path <- paste0(
          substr(script_path_folder, 1, last_slash),
          other_folder_number,
          "_*"
        )
        
        more_objects_path_defined<-find_directory(more_objects_path)
        
        
# Get objects from other 2_* folder 

rda_files<-list.files(path = more_objects_path_defined, 
                          pattern = "\\.rda$",
                          recursive = TRUE,
                          full.names = TRUE) 
   


# Load each .rda file in 2_* folder 
for (file in rda_files) {
  load(file)
}
        

#get downloaded objects 
objects_starting<-ls()

```



## Check Input Object Sizes

```{r}

dim_check <- list()
has_mismatch <- FALSE  # Variable to track if there's a mismatch

for (obj_name in objects_starting) {
  if (obj_name %in% names(objects_dim_list)) {
    correct_dimensions <- objects_dim_list[[obj_name]]
    actual_object <- get(obj_name)
    actual_dimensions <- list(rows = nrow(actual_object), cols = ncol(actual_object))
    
    if (identical(correct_dimensions, actual_dimensions)) {
      dim_check[[obj_name]] <- "Dimensions match"
    } else {
      # Construct the mismatch message
      mismatch_msg <- "Dimensions mismatch:"
      if (correct_dimensions$rows != actual_dimensions$rows) {
        mismatch_msg <- paste(mismatch_msg, "Expected rows is", correct_dimensions$rows,
                              "actual is", actual_dimensions$rows)
      }
      if (correct_dimensions$cols != actual_dimensions$cols) {
        mismatch_msg <- paste(mismatch_msg, "Expected columns is", correct_dimensions$cols,
                              "actual is", actual_dimensions$cols)
      }
      # Store the mismatch message in dim_check
      dim_check[[obj_name]] <- mismatch_msg
      has_mismatch <- TRUE  # Set has_mismatch to TRUE if there's a mismatch
    }
  }
}

# Print the output
print(dim_check)

# Check if there's a mismatch and stop if true
if (has_mismatch) {
  stop("There is at least one object with mismatched dimensions.")
}  else {"No mismatch in loaded object sizes, continue code execution." }

```

## Obtain Objects from folder 3\_\*

```{r}
#       Find Object Code Folder 3_* -----------------------------------

        other_folder_number<-3

        # Construct the new path

        more_objects_path <- paste0(
          substr(script_path_folder, 1, last_slash),
          other_folder_number,
          "_*"
        )
        
        more_objects_path_defined<-find_directory(more_objects_path)
        
        
# Get objects from other 3_* folder 

rda_files<-list.files(path = more_objects_path_defined, 
                          pattern = "\\Test_List_Stacked.rda$",
                          recursive = TRUE,
                          full.names = TRUE) 
   


# Load each .rda file in 3_* folder 
for (file in rda_files) {
  load(file)
}
        
# Get objects from other 3_* folder 

rda_files<-list.files(path = more_objects_path_defined, 
                          pattern = "\\Train_List_Stacked.rda$",
                          recursive = TRUE,
                          full.names = TRUE) 
   


# Load each .rda file in 3_* folder 
for (file in rda_files) {
  load(file)
}


# Get objects from other 3_* folder 

rda_files<-list.files(path = more_objects_path_defined, 
                          pattern = "\\NA_list_stacked.rda$",
                          recursive = TRUE,
                          full.names = TRUE) 
   


# Load each .rda file in 3_* folder 
for (file in rda_files) {
  load(file)
}
     

     
#get downloaded objects 
objects_starting<-ls()

```

## Check Input Object Sizes

```{r}

dim_check <- list()
has_mismatch <- FALSE  # Variable to track if there's a mismatch

for (obj_name in objects_starting) {
  if (obj_name %in% names(objects_dim_list)) {
    correct_dimensions <- objects_dim_list[[obj_name]]
    actual_object <- get(obj_name)
    actual_dimensions <- list(rows = nrow(actual_object), cols = ncol(actual_object))
    
    if (identical(correct_dimensions, actual_dimensions)) {
      dim_check[[obj_name]] <- "Dimensions match"
    } else {
      # Construct the mismatch message
      mismatch_msg <- "Dimensions mismatch:"
      if (correct_dimensions$rows != actual_dimensions$rows) {
        mismatch_msg <- paste(mismatch_msg, "Expected rows is", correct_dimensions$rows,
                              "actual is", actual_dimensions$rows)
      }
      if (correct_dimensions$cols != actual_dimensions$cols) {
        mismatch_msg <- paste(mismatch_msg, "Expected columns is", correct_dimensions$cols,
                              "actual is", actual_dimensions$cols)
      }
      # Store the mismatch message in dim_check
      dim_check[[obj_name]] <- mismatch_msg
      has_mismatch <- TRUE  # Set has_mismatch to TRUE if there's a mismatch
    }
  }
}

# Print the output
print(dim_check)

# Check if there's a mismatch and stop if true
if (has_mismatch) {
  stop("There is at least one object with mismatched dimensions.")
}  else {"No mismatch in loaded object sizes, continue code execution." }

```

## Obtain Objects from folder 4\_\*

```{r}
#       Find Object Code Folder 4_* -----------------------------------

        other_folder_number<-4

        # Construct the new path

        more_objects_path <- paste0(
          substr(script_path_folder, 1, last_slash),
          other_folder_number,
          "_*"
        )
        
        more_objects_path_defined<-find_directory(more_objects_path)
        
        
# Get objects from other 3_* folder 

rda_files<-list.files(path = more_objects_path_defined, 
                          pattern = "\\.rda$",
                          recursive = TRUE,
                          full.names = TRUE) 
   


# Load each .rda file in 3_* folder 
for (file in rda_files) {
  load(file)
}
        

#get downloaded objects 
objects_starting<-ls()

```

## Check Input Object Sizes

```{r}

dim_check <- list()
has_mismatch <- FALSE  # Variable to track if there's a mismatch

for (obj_name in objects_starting) {
  if (obj_name %in% names(objects_dim_list)) {
    correct_dimensions <- objects_dim_list[[obj_name]]
    actual_object <- get(obj_name)
    actual_dimensions <- list(rows = nrow(actual_object), cols = ncol(actual_object))
    
    if (identical(correct_dimensions, actual_dimensions)) {
      dim_check[[obj_name]] <- "Dimensions match"
    } else {
      # Construct the mismatch message
      mismatch_msg <- "Dimensions mismatch:"
      if (correct_dimensions$rows != actual_dimensions$rows) {
        mismatch_msg <- paste(mismatch_msg, "Expected rows is", correct_dimensions$rows,
                              "actual is", actual_dimensions$rows)
      }
      if (correct_dimensions$cols != actual_dimensions$cols) {
        mismatch_msg <- paste(mismatch_msg, "Expected columns is", correct_dimensions$cols,
                              "actual is", actual_dimensions$cols)
      }
      # Store the mismatch message in dim_check
      dim_check[[obj_name]] <- mismatch_msg
      has_mismatch <- TRUE  # Set has_mismatch to TRUE if there's a mismatch
    }
  }
}

# Print the output
print(dim_check)

# Check if there's a mismatch and stop if true
if (has_mismatch) {
  stop("There is at least one object with mismatched dimensions.")
}  else {"No mismatch in loaded object sizes, continue code execution." }

```





# MAIN -------------------------------



# Prep
```{r}
# Prepare and strip data for MLR functions ----------

prep_mlr_pred<-function(df, featvec, statecol){
  
  
# col name consistency - gene col names in dataframe 
    names(df)<-gsub("\\-",".",names(df))
    

# col name consistency - Gene col names featvector
    featvec<-gsub("\\-",".",featvec)

    #desired col names in training data
    alongforride_colnames<-colnames(df[1:6])
    
    colnames_w_features<- c(alongforride_colnames, featvec)
   
  # Filter known classes using dynamic column name
  DF_known <- df %>%
    # dplyr::filter(.data[[statecol]] %in% c(-1, 1)) %>%
    dplyr::select(all_of(colnames_w_features))

  # Convert target to factor safely
  DF_known[[statecol]] <- factor(DF_known[[statecol]] #, levels = c( 1, -1)) 
                                    )
  
  # Strip down to target + features
  out_stripped <- DF_known %>%
    dplyr::select(all_of(c(statecol, featvec)))

  # Diagnostics
  print(paste0("Dimensions of entering df: ", dim(df)[1], " x ", dim(df)[2]))
  print(paste0("Dimensions of output df: ", dim(out_stripped)[1], " x ", dim(out_stripped)[2]))

  print("Count of drug metabolism state in out data:")
  print(table(out_stripped[[statecol]]))

  return(out_stripped)
  
}

```

## Assign name of model 
```{r}
nameofmodel<-"TV-SVM"
```


## Extract Data 
```{r}

MA_100_gene_exp_multi_list_test_1<-as.data.frame(MA_100_gene_exp_multi_list_test[[1]])

MA_100_gene_exp_multi_classbal_list_train_1<-as.data.frame(MA_100_gene_exp_multi_classbal_list_train[[1]])

MA_100_gene_exp_multi_classbal_list_NA_PT15_1<-as.data.frame(MA_100_gene_exp_multi_classbal_list_NA_PT15[[1]])

MA_100_gene_exp_multi_classbal_list_NA_PT5_1<-as.data.frame(MA_100_gene_exp_multi_classbal_list_NA_PT5[[1]])



# Combined 


temp1<-rbind(MA_100_gene_exp_multi_list_test_1, MA_100_gene_exp_multi_classbal_list_train_1)
temp2<-rbind(MA_100_gene_exp_multi_classbal_list_NA_PT15_1, MA_100_gene_exp_multi_classbal_list_NA_PT5_1)

TV_prediction_Boot_ALL<-rbind(temp1, temp2)

rm(MA_100_gene_exp_multi_list_test,
   MA_100_gene_exp_multi_classbal_list_train,
   MA_100_gene_exp_multi_classbal_list_NA_PT15, 
   MA_100_gene_exp_multi_classbal_list_NA_PT5 )


```




## PT Specific mRNA and MBIO data 
```{r}

# Select PT IDs for Testing and Training -----------

test_PT5<-unique(test_boot10_pt_ID_per_iteration[[1]]$pt_ID)

train_PT15<-unique(train_boot10_pt_ID_per_iteration[[1]]$pt_ID)

rm(test_boot10_pt_ID_per_iteration, train_boot10_pt_ID_per_iteration, train_boot10_MA_100, test_boot10_MA_100, test_boot10_Master_analysis, train_boot10_Master_analysis)

# RNA DATA -----------------------------------
 
# Training Pts (15)
rna_train_pts<-subset( df_hp1_rna_dat_select_tran, rownames(df_hp1_rna_dat_select_tran) %in% train_PT15)
rna_train_pts <- rna_train_pts[train_PT15, ]

# Testing PTs (5)
rna_test_pts<-subset( df_hp1_rna_dat_select_tran, rownames(df_hp1_rna_dat_select_tran) %in% test_PT5)
rna_test_pts <- rna_test_pts[test_PT5, ]


# MBio DATA -----------------------------------
 
# Training Pts (15)
mbio_train_pts<-subset( df_mbiocomp_dat_pres_pop_trans, rownames(df_mbiocomp_dat_pres_pop_trans) %in% train_PT15)
mbio_train_pts <- mbio_train_pts[train_PT15, ]

# Testing PTs (5)
mbio_test_pts<-subset( df_mbiocomp_dat_pres_pop_trans, rownames(df_mbiocomp_dat_pres_pop_trans) %in% test_PT5)
mbio_test_pts <- mbio_test_pts[test_PT5, ]



  
 
```
## Microbes in proteomic and mRNA pts 
```{r}

# Select Same Microbes as in PrEP Proteomics cohort ------------------


 raw_shared_microbes<- c("Prevotella",               "Fusobacterium nucleatum",  
                        "Gardnerella vaginalis"     ,"Mobiluncus mulieris"      ,
                        "Atopobium vaginae"         ,"Lactobacillus hamsteri"   ,
                        "Pseudomonas aeruginosa"    ,"Lactobacillus hominis"    ,
                        "Bifidobacterium"           ,"Lactobacillus gasseri"    ,
                       "Peptostreptococcus"        ,"undistinguishable"        ,
                       "Pseudomonas"               ,"Lactobacillus"            ,
                      "Pseudomonas fulva"         ,"Lactobacillus gallinarum" ,
                       "Lactobacillus ultunensis"  ,"Lactobacillus vaginalis"  ,
                       "Lactobacillus iners"       ,"Pseudomonas syringae"     ,
                       "Lactobacillus crispatus"   ,"Lactobacillus helveticus" ,
                       "Lactobacillus jensenii"    ,"Lactobacillus taiwanensis")
                      

```


## Define Fxn - Correlate mRNA ~ mBio x LINCS CD 
```{r}

 run_raw_corr_prediction <- function(
  mbiocomp_data,
  RNA_data,
  lincs_data,
  selected_features,
  svm_model
) {
  
  # ------------------------------------------------------------
  # Prep - Calculate Participant Correlation
  # ------------------------------------------------------------
  
  input2_loop_mbiocomp <- mbiocomp_data
  input1_loop_RNA <- RNA_data
  
  # Spearman correlation: Microbes x Host Genes
  microbes_vs_genes_corr_loop <- cor(
    input2_loop_mbiocomp,
    input1_loop_RNA,
    method = "spearman"
  )
  
  microbes_vs_genes_corr_loop <- as.data.frame(
    microbes_vs_genes_corr_loop
  )
  
  # Transpose and calculate Tenofovir correlation
  microbes_vs_genes_corr_loop_trans <- as.data.frame(
    base::t(microbes_vs_genes_corr_loop)
  )
  
  TV_microbe_gene_corr_loop <- cor(
    microbes_vs_genes_corr_loop_trans,
    y = lincs_data,
    method = "spearman"
  )
  
  TV_microbe_gene_corr_loop <- as.data.frame(
    TV_microbe_gene_corr_loop
  )
  
  # Create Master correlation dataframe
  Master_raw <- cbind(
    TV_microbe_gene_corr_loop,
    microbes_vs_genes_corr_loop
  )
  
  Master_raw_copy <- Master_raw
  
  # Retain gene columns
  col <- which(colnames(Master_raw) == "A2M")
  
  Master_raw_gene <- Master_raw[
    ,
    col:ncol(Master_raw)
  ]
  
  if (col == 2 & ncol(Master_raw) == 9452) {
    
    Master_raw_temp <- as.data.frame(
      Master_raw[, 1]
    )
    
    colnames(Master_raw_temp)[1] <- "tenofovir"
    
  } else {
    
    stop(
      "There be an issue with the col when making the Master_raw and which col is defined as A2M"
    )
  }
  
  # Add structural columns
  Master_raw_temp$Microbes <- rownames(Master_raw_gene)
  Master_raw_temp$TV_state <- rep(
    NA,
    nrow(Master_raw_temp)
  )
  Master_raw_temp$TV_Mic_iteration <- rep(
    "raw-corr",
    nrow(Master_raw_temp)
  )
  Master_raw_temp$MvG_iteration <- rep(
    "raw-corr",
    nrow(Master_raw_temp)
  )
  
  Master_raw_temp <- Master_raw_temp %>%
    dplyr::select(
      Microbes,
      TV_state,
      TV_Mic_iteration,
      tenofovir,
      MvG_iteration
    )
  
  # Rejoin and clear rownames
  Master_raw <- cbind(
    Master_raw_temp,
    Master_raw_gene
  )
  
  rownames(Master_raw) <- NULL
  
  
  # ------------------------------------------------------------
  # Multiply Gene Expression x Microbe-Gene Correlation
  # ------------------------------------------------------------
  
  lincs_data_matrix <- as.matrix(lincs_data)
  
  gene_col_index_start <- which(
    colnames(Master_raw) == "A2M"
  )
  
  gene_col_index_end <- which(
    colnames(Master_raw) == "ZZZ3"
  )
  
  # Select gene columns and transpose
  MA_raw_gene <- Master_raw[
    ,
    gene_col_index_start:gene_col_index_end
  ]
  
  MA_raw_gene <- as.matrix(MA_raw_gene)
  
  MA_raw_gene_trans <- base::t(
    MA_raw_gene
  )
  
  # Multiply LINCS gene expression by microbe-gene correlation
  MA_raw_gene_exp_multi_genesonly <- (
    lincs_data_matrix[, 1] *
      MA_raw_gene_trans
  )
  
  # Transpose back
  MA_raw_gene_exp_multi_genesonly <- base::t(
    MA_raw_gene_exp_multi_genesonly
  )
  
  # Add non-gene columns back
  MA_raw_gene_exp_multi_genesonly <- cbind(
    Master_raw[, 1:gene_col_index_start - 1],
    MA_raw_gene_exp_multi_genesonly
  )
  
  
  # ------------------------------------------------------------
  # Select Features
  # ------------------------------------------------------------
  
  # Make gene names consistent
  names(MA_raw_gene_exp_multi_genesonly) <- gsub(
    "\\-",
    ".",
    names(MA_raw_gene_exp_multi_genesonly)
  )
  
  selected_features <- gsub(
    "\\-",
    ".",
    selected_features
  )
  
  gene_index_start <- which(
    colnames(MA_raw_gene_exp_multi_genesonly) == "A2M"
  )
  
  # Columns retained for structural consistency
  alongforride_colnames <- colnames(
    MA_raw_gene_exp_multi_genesonly[
      1:gene_index_start - 1
    ]
  )
  
  colnames_w_features <- c(
    alongforride_colnames,
    selected_features
  )
  
  # Keep selected features
  TV_prediction <- MA_raw_gene_exp_multi_genesonly %>%
    dplyr::select(
      dplyr::all_of(colnames_w_features)
    )
  
  TV_prediction$TV_state <- factor(
    TV_prediction$TV_state
  )
  
  # Keep only TV_state and selected features for prediction
  TV_prediction_stripped <- TV_prediction %>%
    dplyr::select(
      TV_state,
      dplyr::all_of(selected_features)
    )
  
  
  # ------------------------------------------------------------
  # Identify Microbes That Can Be Predicted
  # ------------------------------------------------------------
  
  # A microbe can only be predicted if it has a value for
  # every selected feature.
  predictable_rows <- complete.cases(
    TV_prediction_stripped[, selected_features, drop = FALSE]
  )
  
  # Keep only microbes that have complete prediction data
  TV_prediction_dropped <- TV_prediction_stripped[
    predictable_rows,
    ,
    drop = FALSE
  ]
  
  # Keep corresponding microbe names
  predictable_microbes <- TV_prediction$Microbes[
    predictable_rows
  ]
  
  
  # ------------------------------------------------------------
  # Predict Only Predictable Microbes
  # ------------------------------------------------------------
  
  predictions <- predict(
    object = svm_model,
    newdata = TV_prediction_dropped
  )
  
  # Add microbe names
  predictions_labeled <- cbind(
    predictable_microbes,
    as.data.frame(predictions)
  )
  
  colnames(predictions_labeled)[1] <- "Microbes"
  
  predictions_labeled <- predictions_labeled %>%
    mutate(
      group = paste(
        Microbes,
        response,
        sep = "_"
      )
    )
  
  # Arrange by metabolizing probability
  predictions_labeled <- predictions_labeled %>%
    arrange(
      desc(prob.1)
    )
  
  # Insert known relationships used in training
  predictions_labeled <- within(
    predictions_labeled,
    truth[
      Microbes == "Gardnerella vaginalis" |
      Microbes == "Mobiluncus mulieris"
    ] <- 1
  )
  
  predictions_labeled <- within(
    predictions_labeled,
    truth[
      Microbes == "Lactobacillus iners" |
      Microbes == "Lactobacillus crispatus"
    ] <- -1
  )
  
  # Final prediction object
  pred_labeled_raw_corr_Thresh50 <- predictions_labeled
  
  
  # ------------------------------------------------------------
  # Return results
  # ------------------------------------------------------------
  
  return(
    list(
      TV_prediction = TV_prediction,
      TV_prediction_dropped = TV_prediction_dropped,
      predictions_labeled = predictions_labeled
    )
  )
} 
```

## Define Fxn - Plot Raw pred with modular thresholds 
```{r}
make_final_prediction_plot <- function(
  predictions_labeled,
  thresh_top,
  thresh_bot,
  model_name ,
  raw_shared_microbes = NULL,
  name = NULL
) {
  
  # ------------------------------------------------------------
  # Print thresholds
  # ------------------------------------------------------------
  
  print(
    paste0(
      "Top Classification Threshold for Meta calls: ",
      thresh_top
    )
  )
  
  print(
    paste0(
      "Bottom Classification Threshold for Meta calls: ",
      thresh_bot
    )
  )
  
  
  # ------------------------------------------------------------
  # Adjust Predictions
  # ------------------------------------------------------------
  
  pred_labeled_FINAL <- predictions_labeled %>%
    mutate(
      response = case_when(
        prob.1 >= thresh_top ~ 1,
        prob.1 <= thresh_bot ~ -1,
        TRUE ~ 0
      )
    ) %>%
    arrange(desc(prob.1))
  
  
  # ------------------------------------------------------------
  # Data Prep for Plot
  # ------------------------------------------------------------
  
  pred_lab_round <- pred_labeled_FINAL %>%
    dplyr::select(
      Microbes,
      prob.1,
      response
    )
  
  # Filter to shared microbes if provided
  if (!is.null(raw_shared_microbes)) {
    
    pred_lab_round <- pred_lab_round %>%
      filter(
        Microbes %in% raw_shared_microbes
      )
  }
  
  pred_lab_round <- pred_lab_round %>%
    mutate(
      response = as.factor(response)
    )
  
  
  # Define x-axis order
  level_order <- u(pred_lab_round$Microbes)
  
  
  # Specify colors
  group_colors <- c(
    "Nonmetabolize" = "#1e88e5",
    "Metabolize" = "#d81b60",
    "Indeterminate" = "grey"
  )
  
  
  # Label prediction classes
  pred_lab_round$response <- factor(
    pred_lab_round$response,
    levels = c(-1, 0, 1),
    labels = c(
      "Nonmetabolize",
      "Indeterminate",
      "Metabolize"
    )
  )
  
  
  # ------------------------------------------------------------
  # Plot
  # ------------------------------------------------------------
  
  pred_plot_FINAL <- ggplot(
    pred_lab_round,
    aes(
      x = factor(
        Microbes,
        level = level_order
      ),
      y = prob.1,
      color = response
    )
  ) +
    theme_bw() +
    ylim(-0.01, 1.01) +
    
    geom_jitter(
      alpha = 0.5,
      width = 0.2,
      size = 2
    ) +
    
    geom_hline(
      yintercept = thresh_top,
      linetype = "dashed",
      color = "darkgrey"
    ) +
    
    geom_hline(
      yintercept = thresh_bot,
      linetype = "dashed",
      color = "darkgrey"
    ) +
    
    scale_color_manual(
      values = group_colors,
      breaks = c(
        "Metabolize",
        "Indeterminate",
        "Nonmetabolize"
      ),
      name = "Predicted Classification"
    ) +
    
    theme(
      plot.title = element_text(
        hjust = 0.5,
        vjust = 4
      ),
      plot.subtitle = element_text(
        hjust = 0.5,
        vjust = 2
      ),
      axis.text.x = element_text(
        angle = 45,
        hjust = 1
      ),
      axis.title.x = element_text(
        vjust = -1
      ),
      axis.title.y = element_text(
        vjust = 5
      ),
      plot.margin = unit(
        c(1, 1, 1, 1),
        "cm"
      )
    ) +
    
    labs(
      title = "Predictions",
      subtitle = model_name
    ) +
    
    xlab("Microbes") +
    ylab("Probability of Metabolizing") +
    
    theme(
      plot.caption = element_text(
        hjust = 1,
        vjust = 0
      )
    )
  
  
  # ------------------------------------------------------------
  # Save Plot adn spreadsheet 
  # ------------------------------------------------------------
    
    ggplot2::ggsave(
      paste0("rawpt_plot_", "Thresh_Top",thresh_top,"_Bot", thresh_bot ,"_", name,".pdf"),
      pred_plot_FINAL,
      width = 7,
      height = 5
    )
    
    openxlsx::write.xlsx(
  pred_labeled_FINAL,
  file = paste0("rawpt_plot_", "Thresh_Top",thresh_top,"_Bot", thresh_bot ,"_", name,"predictions_labeled.xlsx"),
  rowNames = FALSE
)
    
    
    
  
  # ------------------------------------------------------------
  # Return
  # ------------------------------------------------------------


  return(
    list(
      predictions = pred_labeled_FINAL,
      plot = pred_plot_FINAL
    ))
}
```

### Clean env
```{r}
rm(predictions_labeled, predictions_sum, TV_prediction_stripped, pred_lab_round)
```

# **PREDICTION RAW PT DATA**

```{r}
out_pt_raw_all<-run_raw_corr_prediction(mbiocomp_data = df_mbiocomp_dat_pres_pop_trans,
                              RNA_data = df_hp1_rna_dat_select_tran,
                              lincs_data = df_lincs_gene_tv_sharedgenes,
                              selected_features = boot_10_shared_feat,
                              svm_model = tunedSvmModel_gene)
```

## plots

```{r}

plot_raw_all<-make_final_prediction_plot(
  predictions_labeled = out_pt_raw_all$predictions_labeled ,
  thresh_top= thresh_sensi_top,
  thresh_bot=thresh_sensi_bot,
  model_name= nameofmodel,
  raw_shared_microbes = raw_shared_microbes,
  name = "all"
)

```




# **CLOSING STEPS**

### Save Object Sizes ***Specify Objects***

```{r}

# Note- rather than saving all created objects I will specify the three dataframes we need for the next code section. 

objects_created <- c( "plot_raw_all"
                    
                      )

reccord_dim <- function(objects) {
  
  result <- list()
  
  for (obj_name in objects) {
    
    if (exists(obj_name)) {
      
      obj <- get(obj_name)
      
      if (is.data.frame(obj) || is.matrix(obj)) {
        
        rows <- nrow(obj)
        cols <- ncol(obj)
        result[[obj_name]] <- list(rows = rows, cols = cols)
        
      } else {
        
        warning(paste("Object labeled ", obj_name, "is not a data frame or a matrix. Skipping."))
      }
      
    } else {
      
      warning(paste("Object", obj_name, "does not exist. Skipping."))
      
    }
  }
  return(result)
}

objects_dim_list<-reccord_dim(objects_created)




#          Summary --------------------------------------------- 

print("Created Objects Summary:")
print(objects_dim_list)


```

### Exporting and Clean Up - Part 1/2

```{r}
#           Create Output File ------------------------------------------------------


current_output_folder<-paste0(script_name_base, "_", run_timestamp, ".Rmd")

dir.create(current_output_folder)

script_path_with_output_folder <- file.path(script_path_folder, 
                                            current_output_folder)

setwd(script_path_with_output_folder) # need to restate for each code chunk

#           Export Executed Code ----------------------------------------------------

copy_and_output_code <- function(script_path) {
  if (file.exists(script_path)) {
    
    
    if (rstudioapi::isAvailable()) {
      try(rstudioapi::documentSave(), silent = TRUE) # New
    }

    script_content <- readLines(script_path)
    
    writeLines(script_content, current_output_folder)
  } else {
    message("Error: The specified script path does not exist.")
  }
}

# Call the function to copy and export the code
copy_and_output_code(script_path_current)

#           Export Run Info ---------------------------------------------------------

writeLines(capture.output(run_sessionInfo), "sessionInfo.txt")


```

### Exporting and Clean Up - Part 2/2 **Specify Objects**

```{r}

setwd(script_path_with_output_folder) # need to restate for each code chunk

#           Export Objects as .rda - **SPECIFY OBJECTS**----------------------------------------------------

objects_save<-c( objects_created, "objects_dim_list")

                            
save(list=objects_save,                   
     file = "env_obj.rda")
 


 
```

### Clear Env./Re-Add Generated Objects

```{r}
setwd(script_path_with_output_folder) # need to restate for each code chunk

#           Clear Environment/Re-Add Generated Objects  ------------------------------------------------------


#clear environment
rm(list = ls()) #USE VERY CAREFULLY ONLY ACTIVATE AT END OF PIPELINE
# rm(list = objects_save)

#readd the objects
load("env_obj.rda")


  ## END ---------------------------------------------------------------------


```
